### 2022-03-25 Results.Rmd
project initialization

---
title: "Results"
author: "Andrew MacDonald"
date: "3/25/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Results

### 2022-03-25 Results.Rmd
Updated results into RMarkdown

@@
 ---
-title: "Results"
-author: "Andrew MacDonald"
-date: "3/25/2022"
-output: html_document
+title: "Connected or Disconnected?"
+subtitle: "An Examination of the Relationship between Social Media Use and Feelings of Isolation in China"
+author: 
+  - Jason Gainous^[Duke Kunshan University, jason.gainous@louisville.edu]
+  - Andrew W. MacDonald^[Duke Kunshan University, andrew.macdonald@dukekunshan.edu.cn]
+date: '`r format(Sys.time(), "%B %d, %Y")`'
+abstract: "The following brief paper is simply the preliminary results of our study.
+We seek to identify the relationship between social media use and feelings of isolationism in China.
+This study is based on original date.
+We conducted a nationwide survey of Chinese citizens conducted in 2015 measuring a range of concepts including those here.
+The preliminary results are promising.
+We develop an index of personal isolationism and model this as a function of social media use, connection to the outside digital world, and urbanicity, while controlling for a host of individual level factors.
+The results suggest the following: 1) Social media use does not have a generalized relationship with isolationism, 2) Those who use VPNs/proxy servers tend to feel less isolated than those who do not, 3) Those living in urban environments tend to feel more isolated, 3) There is a strong positive relationship between social media use and feelings of isolation for those who frequently use VPNs/proxy servers, and 4) The is a strong positive relationship between social media use and feelings of isolation for those living in rural China."
+keywords: 
+  - social isolation
+  - social media
+  - China
+output: bookdown::html_document2
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(warning = FALSE)
+knitr::opts_chunk$set(message = FALSE)
+
+library(tidyverse)
+library(sjPlot)
+library(ggpubr)
+library(grid)
+library(stargazer)
+library(scales)
+library(papeR)
+library(gridExtra)
+library(knitr)
+library(kableExtra)
+library(ggcorrplot)
+
+load("china_isolation_data.RData")
+
+china_isolation_data <- china_original_amanzhol
 ```
 
-# Results
+# Social Isolation in China
+
+## Introduction
+
+Research is quite mixed when it comes to identifying the relationship between social media use and feelings of isolationism.
+Early research suggested that the internet would build social capital, or an interconnectedness between people, and that social media platforms were the ultimate way to bring people together.
+Since then, research indicates that the effect may be the opposite for many.
+Social media may encourage social isolation, and ultimately, social media users may feel more disconnected from others than those who do not use social media.
+We know very little about this phenomenon in China.
+China presents an interesting case because the internet is bifurcated to some degree – there is the Chinese internet and the outside internet available via VPNs.
+Being connected to the outside world may lessen feelings of isolation, or it may increase these feelings because digital exposure to a world is much larger than that in people’s immediate environment without the ability to have in-person connection to may make one feel isolated.
+Interestingly, and somewhat ironically though, it may also matter, too, whether someone lives in a city.
+Research has suggested that urban living can actually lead to feelings of isolation.
+
+## Data
+
+Our data are based on a random Internet survey conducted by Qualtrics from November 25 to December 2, 2015.
+We designed the instrument, content and structure.
+After we designed the instrument in English and translated it into Chinese, we entered the questions into the graphical interface provided from our survey provider, Qualtrics.
+We were careful at this stage to make the formatting clear, and to distribute the questions across numerous pages to prevent overwhelming respondents with too many questions at once.
+This helped us achieve a high completion and response rate.
+Additionally, we were particularly attentive to the possibility of question order effects.
+Many of the questions are sensitive and could cue responses to subsequent questions.
+We grouped and placed questions strategically to limit any such potential for response bias.
+Once we settled on the design, Qualtrics administered the survey in November 2015.
+They recruit a large pool of respondents for various survey projects through online advertising on websites such as local portals, search engines, social networking services, and/or online shopping services.
+Panelists who update their profiles at least once every 6 months are randomly invited to participate in surveys for which they qualify.
+Online points are awarded to the corresponding panelists, which they may accumulate and exchange for cash or various other country-specific gifts to serve as an incentive for completion.
+This number of points is based on the length of the survey.
+Ours had over fifty questions, so respondents received a relatively high number of points.
+
+The data collection had two phases.
+For the first phase, Qualtrics collected and submitted to us a trial run of 286 cases.
+We were able to check the data for reliability and adjust the instrument before proceeding with the second phase, the final data collection.
+We only made three adjustments, all of which turned out to be important and central to our analysis.
+For the trial run, we only asked respondents about pro-government Internet posters and did not ask them about potential net-spy or hostile posters.
+We amended this oversight and it became central to the analysis that follows.
+In addition, much of our theory focuses on the impact of Chinese Internet users circumventing government filters on the Internet.
+We initially had a question about whether citizens had jumped the wall to read sensitive political information (see Appendix A – Q25), but decided to add whether they had done so for entertainment purposes as well (Q26 - to watch foreign movies, television shows, etc.).
+Finally, we also included an attention filter question as part of a battery of institutional trust questions where respondents were simply told to select the “None at all” response (Q13H).
+If they did not select this response, we could assume they were not paying attention to the questions, and the survey ended for these respondents and the data were not collected for them.
+In the end, the full sample included a total of 2292 respondents.
+This sample size provides for a roughly ±2 margin of error.
+
+While our sample was randomly selected, the sampling frame was based only on Internet users that Qualtrics can access.
+Qualtrics recruits their frame subjects through online advertising on websites such as local portals, search engines, social networking services, and/or online shopping services.
+We do not contend that our sample is representative of the Chinese population, as the method of obtaining respondents obviously greatly limits those citizens with little or no access to the Internet.
+That said, we are comfortable that our sample is generally representative of Chinese Internet users.
+Given that our research focus centers on Internet effects, it makes sense to have a large sample of Internet users.
+A sampling frame including the entire Chinese population did not make sense for this research.
+Half of the population do not regularly access the Internet according to World Bank and China Internet Network Information Center (CNNIC) data as of late 2015 when we conducted our survey.
+Using a sample of the entire population could potentially limit the degrees of freedom in our models and the marginals of nuanced measures of digital media use would likely become too small to have any value.
+Thus, the large sample of Internet users adds to our confidence in the inferences throughout the book.
+
+## Summary statistics
+
+### Summary stats table
+```{r summarystats}
+key.vars <- china_isolation_data %>% 
+  select(c(connected, gen_social_med, urbanicity, ses, female, CCP_member, age, jump_wall))
+
+kable(summarize(key.vars, type="numeric")) %>% 
+  kable_styling()
+```
+
+### Correlations
+
+```{r correlations}
+cors <- cor(key.vars, use="complete.obs")
+
+ggcorrplot(cors, title="Key variables associated with connectedness", lab=TRUE, type="lower")
+```
+
+## Models
+
+```{r models}
+mod1 <- lm(connected ~ gen_social_med + urbanicity + ses + female + CCP_member + age + jump_wall, data = china_isolation_data)
+
+mod2 <- lm(connected ~ gen_social_med*urbanicity + ses + female + CCP_member + age + jump_wall, data = china_isolation_data)
+
+mod3 <- lm(connected ~ gen_social_med*jump_wall + urbanicity + ses + female + CCP_member + age, data = china_isolation_data)
+
+tab_model(mod1, mod2, mod3, show.ci = FALSE)
+```
+
+## Margin plots
+
+```{r marginplots}
+a = plot_model(mod2, type = "pred", title = "", terms = c("gen_social_med", "urbanicity")
+               , legend.title = "Urbanicity") +
+  scale_color_discrete(labels = c("Village", "Small City", "Mid-sized City", "Suburb", "Big City")) +
+  ylab("Feelings of Isolation") +
+  xlab("Social Media Use")
+
+b = plot_model(mod3, type = "pred", title = "", terms = c("gen_social_med", "jump_wall")
+               , legend.title = "Globally Connected") +
+  scale_color_discrete(labels = c("Never", "", "", "A Moderate Amount", "", "", "Very Often")) +
+  ylab("Feelings of Isolation") +
+  xlab("Social Media Use")
+
+grid.arrange(a, b)
+```

### 2022-03-25 starting script/china_isolationism_script.R

@@ -1,0 +1,60 @@
+load("C:/Users/jbg43/Dropbox/Research/Internet Politics/China/Isolationism/china_isolation_data.RData")
+
+names(china_isolation_data)
+table(china_isolation_data$connected)
+cor.test(china_isolation_data$gen_social_med,china_isolation_data$connected)
+
+mod1 = lm(connected ~ gen_social_med + urbanicity + ses + female + CCP_member + age + jump_wall, data = china_isolation_data)
+summary(mod1)
+
+mod2 = lm(connected ~ gen_social_med*urbanicity + ses + female + CCP_member + age + jump_wall, data = china_isolation_data)
+summary(mod2)
+
+mod3 = lm(connected ~ gen_social_med*jump_wall + urbanicity + ses + female + CCP_member + age, data = china_isolation_data)
+summary(mod3)
+
+library(ggplot2)
+library(sjPlot)
+
+a = plot_model(mod2, type = "pred", title = "", terms = c("gen_social_med", "urbanicity")
+               , legend.title = "Urbanicity") +
+  scale_color_discrete(labels = c("Village", "Small City", "Mid-sized City", "Suburb", "Big City")) +
+  ylab("Feelings of Isolation") +
+  xlab("Social Media Use") 
+a
+
+b = plot_model(mod3, type = "pred", title = "", terms = c("gen_social_med", "jump_wall")
+               , legend.title = "Globally Connected") +
+  scale_color_discrete(labels = c("Never", "", "", "A Moderate Amount", "", "", "Very Often")) +
+  ylab("Feelings of Isolation") +
+  xlab("Social Media Use") 
+b
+
+library(ggpubr)
+library(grid)
+figure1 = ggarrange(a, b, ncol=2, nrow=1, common.legend = FALSE, legend="top")
+figure1 = annotate_figure(figure1, left = textGrob("Feelings of Isolation",  rot = 90, vjust = 1, gp = gpar(cex = 1.3)))
+figure1
+
+
+library(stargazer)
+stargazer(mod1, mod2, mod3,
+          digits = 2, 
+          dep.var.labels = c("Models"),
+          star.cutoffs = c(0.0549999),
+          omit.stat=c("LL","ser","f"), 
+          no.space =TRUE)
+
+#Invert Connected
+table(china_isolation_data$Q7_A)
+table(china_isolation_data$Q7_A_rc)
+
[…]

### 2022-11-18 Social Isolation in China.qmd
Move to Quarto

--- 2022-03-25 Results.Rmd
@@
 title: "Connected or Disconnected?"
-subtitle: "An Examination of the Relationship between Social Media Use and Feelings of Isolation in China"
 author: 
@@
   - China
-output: bookdown::html_document2
+format: pdf
+editor: visual
 ---
@@
 kable(summarize(key.vars, type="numeric")) %>% 
-  kable_styling()
+  kable_styling(latex_options="striped")
 ```
@@
 
-ggcorrplot(cors, title="Key variables associated with connectedness", lab=TRUE, type="lower")
+ggcorrplot(cors, title="Key variables associated with connectedness", 
+           lab=TRUE, type="lower", insig="blank")
 ```

### 2022-11-18 Social Isolation in China.qmd
Small update

@@
 We know very little about this phenomenon in China.
-China presents an interesting case because the internet is bifurcated to some degree – there is the Chinese internet and the outside internet available via VPNs.
-Being connected to the outside world may lessen feelings of isolation, or it may increase these feelings because digital exposure to a world is much larger than that in people’s immediate environment without the ability to have in-person connection to may make one feel isolated.
+China presents an interesting case because the internet is bifurcated to some degree -- there is the Chinese internet and the outside internet available via VPNs.
+Being connected to the outside world may lessen feelings of isolation, or it may increase these feelings because digital exposure to a world is much larger than that in people's immediate environment without the ability to have in-person connection to may make one feel isolated.
 Interestingly, and somewhat ironically though, it may also matter, too, whether someone lives in a city.
@@
 In addition, much of our theory focuses on the impact of Chinese Internet users circumventing government filters on the Internet.
-We initially had a question about whether citizens had jumped the wall to read sensitive political information (see Appendix A – Q25), but decided to add whether they had done so for entertainment purposes as well (Q26 - to watch foreign movies, television shows, etc.).
-Finally, we also included an attention filter question as part of a battery of institutional trust questions where respondents were simply told to select the “None at all” response (Q13H).
+We initially had a question about whether citizens had jumped the wall to read sensitive political information (see Appendix A -- Q25), but decided to add whether they had done so for entertainment purposes as well (Q26 - to watch foreign movies, television shows, etc.).
+Finally, we also included an attention filter question as part of a battery of institutional trust questions where respondents were simply told to select the "None at all" response (Q13H).
 If they did not select this response, we could assume they were not paying attention to the questions, and the survey ended for these respondents and the data were not collected for them.
@@
 ### Summary stats table
+
 ```{r summarystats}

### 2023-02-23 starting script/china_isolationism_script.R
ADDED

@@ -58,3 +58,5 @@ cor.test(china_isolation_data$xxx, china_isolation_data$connected)
 library(scales)
 china_isolation_data$urbanicity_cat = as.factor(rescale(china_isolation_data$urbanicity, to = c(1, 5)))
 table(china_isolation_data$urbanicity_cat)
+
+#FDGNJLKGSFDLKJSFDJLKFDSGLJ'D

### 2023-05-29 Social-Isolation-in-China.tex
update

--- 2022-11-18 Social Isolation in China.qmd
@@
----
-title: "Connected or Disconnected?"
-author: 
-  - Jason Gainous^[Duke Kunshan University, jason.gainous@louisville.edu]
-  - Andrew W. MacDonald^[Duke Kunshan University, andrew.macdonald@dukekunshan.edu.cn]
-date: '`r format(Sys.time(), "%B %d, %Y")`'
-abstract: "The following brief paper is simply the preliminary results of our study.
-We seek to identify the relationship between social media use and feelings of isolationism in China.
-This study is based on original date.
-We conducted a nationwide survey of Chinese citizens conducted in 2015 measuring a range of concepts including those here.
-The preliminary results are promising.
-We develop an index of personal isolationism and model this as a function of social media use, connection to the outside digital world, and urbanicity, while controlling for a host of individual level factors.
-The results suggest the following: 1) Social media use does not have a generalized relationship with isolationism, 2) Those who use VPNs/proxy servers tend to feel less isolated than those who do not, 3) Those living in urban environments tend to feel more isolated, 3) There is a strong positive relationship between social media use and feelings of isolation for those who frequently use VPNs/proxy servers, and 4) The is a strong positive relationship between social media use and feelings of isolation for those living in rural China."
-keywords: 
-  - social isolation
-  - social media
-  - China
-format: pdf
-editor: visual
----
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
+%
+\documentclass[
+  letterpaper,
+  DIV=11,
+  numbers=noendperiod]{scrartcl}
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
-knitr::opts_chunk$set(warning = FALSE)
-knitr::opts_chunk$set(message = FALSE)
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+% Make \paragraph and \subparagraph free-standing
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-library(tidyverse)
-library(sjPlot)
-library(ggpubr)
-library(grid)
-library(stargazer)
-library(scales)
-library(papeR)
-library(gridExtra)
-library(knitr)
-library(kableExtra)
-library(ggcorrplot)
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 
-load("china_isolation_data.RData")
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+\KOMAoption{captions}{tableheading}
+\makeatletter
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
+\fi
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
+\makeatletter
+\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
+\makeatother
+\makeatletter
+\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
+\makeatother
+\makeatletter
+\makeatother
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={The Spatial Relationship between Social Media, Digital Connectedness, and Social Isolation in China: Revisting Cyber-Optimism},
+  pdfauthor={Jason Gainous; Andrew W. MacDonald},
+  pdfkeywords={social isolation, social media, digital
+connectedness, China},
+  colorlinks=true,
+  linkcolor={blue},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
+  pdfcreator={LaTeX via pandoc}}
 
-china_isolation_data <- china_original_amanzhol
-```
+\title{The Spatial Relationship between Social Media, Digital
+Connectedness, and Social Isolation in China: Revisting Cyber-Optimism}
+\author{Jason Gainous\footnote{University of Louisville,
+  jason.gainous@louisville.edu} \and Andrew W. MacDonald\footnote{Duke
+  Kunshan University, andrew.macdonald@dukekunshan.edu.cn}}
+\date{3/5/23}
 
-# Social Isolation in China
+\begin{document}
+\maketitle
+\begin{abstract}
+Early research and populuar discourse on the promise of the internet was
+optimistic. Many believed it would promote social interconnectedness
+and, ultimately, be a positive force in people's lives. Since these
+early predictions, research has become much less positive, usually
+pointing to the negative aspects of social media. Here we argue that the
+digital environment can actually create a space that deters feelings of
+social isolationism especially for those living outside cities in
+restrictive information environments where citizens are often
+disconnected from the outside world. Using data from a nationwide survey
+of Chinese citizens we conducted in 2015, we find that the more citizens
+digitally connect with others, the more likely they are to move
+relationships from online to offliine, and the more they use social
+media the less personally isolated they feel. Futher, those living in
+urban environments tend to feel more isolated, and this spatial factor
+seems to moderate the aforementioned relationships. All three of those
+observed relationships are stronger for those in less urban
+environments.
+\end{abstract}
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, enhanced, frame hidden, interior hidden, boxrule=0pt, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
 
-## Introduction
+\hypertarget{social-isolation-in-china}{%
+\section{Social Isolation in China}\label{social-isolation-in-china}}
 
-Research is quite mixed when it comes to identifying the relationship between social media use and feelings of isolationism.
-Early research suggested that the internet would build social capital, or an interconnectedness between people, and that social media platforms were the ultimate way to bring people together.
-Since then, research indicates that the effect may be the opposite for many.
-Social media may encourage social isolation, and ultimately, social media users may feel more disconnected from others than those who do not use social media.
-We know very little about this phenomenon in China.
-China presents an interesting case because the internet is bifurcated to some degree -- there is the Chinese internet and the outside internet available via VPNs.
-Being connected to the outside world may lessen feelings of isolation, or it may increase these feelings because digital exposure to a world is much larger than that in people's immediate environment without the ability to have in-person connection to may make one feel isolated.
-Interestingly, and somewhat ironically though, it may also matter, too, whether someone lives in a city.
-Research has suggested that urban living can actually lead to feelings of isolation.
+\hypertarget{introduction}{%
+\subsection{Introduction}\label{introduction}}
 
-## Data
+Research is quite mixed when it comes to identifying the relationship
+between social media use and feelings of isolationism. Early research
+suggested that the internet would build social capital, or an
+interconnectedness between people, and that social media platforms were
+the ultimate way to bring people together. Since then, research
+indicates that the effect may be the opposite for many. Social media may
+encourage social isolation, and ultimately, social media users may feel
+more disconnected from others than those who do not use social media. We
+know very little about this phenomenon in China. China presents an
+interesting case because the internet is bifurcated to some degree --
+there is the Chinese internet and the outside internet available via
+VPNs. Being isolation to the outside world may lessen feelings of
+isolation, or it may increase these feelings because digital exposure to
+a world is much larger than that in people's immediate environment
+without the ability to have in-person connection to may make one feel
+isolated. Interestingly, and somewhat ironically though, it may also
+matter, too, whether someone lives in a city. Research has suggested
+that urban living can actually lead to feelings of isolation.
 
-Our data are based on a random Internet survey conducted by Qualtrics from November 25 to December 2, 2015.
-We designed the instrument, content and structure.
-After we designed the instrument in English and translated it into Chinese, we entered the questions into the graphical interface provided from our survey provider, Qualtrics.
-We were careful at this stage to make the formatting clear, and to distribute the questions across numerous pages to prevent overwhelming respondents with too many questions at once.
-This helped us achieve a high completion and response rate.
-Additionally, we were particularly attentive to the possibility of question order effects.
-Many of the questions are sensitive and could cue responses to subsequent questions.
-We grouped and placed questions strategically to limit any such potential for response bias.
-Once we settled on the design, Qualtrics administered the survey in November 2015.
-They recruit a large pool of respondents for various survey projects through online advertising on websites such as local portals, search engines, social networking services, and/or online shopping services.
-Panelists who update their profiles at least once every 6 months are randomly invited to participate in surveys for which they qualify.
-Online points are awarded to the corresponding panelists, which they may accumulate and exchange for cash or various other country-specific gifts to serve as an incentive for completion.
-This number of points is based on the length of the survey.
-Ours had over fifty questions, so respondents received a relatively high number of points.
+\hypertarget{introduction-1}{%
+\subsection{Introduction}\label{introduction-1}}
 
-The data collection had two phases.
-For the first phase, Qualtrics collected and submitted to us a trial run of 286 cases.
-We were able to check the data for reliability and adjust the instrument before proceeding with the second phase, the final data collection.
-We only made three adjustments, all of which turned out to be important and central to our analysis.
-For the trial run, we only asked respondents about pro-government Internet posters and did not ask them about potential net-spy or hostile posters.
-We amended this oversight and it became central to the analysis that follows.
-In addition, much of our theory focuses on the impact of Chinese Internet users circumventing government filters on the Internet.
-We initially had a question about whether citizens had jumped the wall to read sensitive political information (see Appendix A -- Q25), but decided to add whether they had done so for entertainment purposes as well (Q26 - to watch foreign movies, television shows, etc.).
-Finally, we also included an attention filter question as part of a battery of institutional trust questions where respondents were simply told to select the "None at all" response (Q13H).
-If they did not select this response, we could assume they were not paying attention to the questions, and the survey ended for these respondents and the data were not collected for them.
-In the end, the full sample included a total of 2292 respondents.
-This sample size provides for a roughly ±2 margin of error.
+Research is quite mixed when it comes to identifying the relationship
+between social media use and feelings of isolationism. Early research
+suggested that the internet would build social capital, or an
+interconnectedness between people, and that social media platforms were
+the ultimate way to bring people together. Since then, research
+indicates that the effect may be the opposite for many. Social media may
+encourage social isolation, and ultimately, social media users may feel
+more disconnected from others than those who do not use social media. We
+know very little about this phenomenon in China. China presents an
+interesting case because the internet is bifurcated to some degree --
+there is the Chinese internet and the outside internet available via
+VPNs. Being isolation to the outside world may lessen feelings of
+isolation, or it may increase these feelings because digital exposure to
+a world is much larger than that in people's immediate environment
+without the ability to have in-person connection to may make one feel
+isolated. Interestingly, and somewhat ironically though, it may also
+matter, too, whether someone lives in a city. Research has suggested
+that urban living can actually lead to feelings of isolation.
 
-While our sample was randomly selected, the sampling frame was based only on Internet users that Qualtrics can access.
-Qualtrics recruits their frame subjects through online advertising on websites such as local portals, search engines, social networking services, and/or online shopping services.
-We do not contend that our sample is representative of the Chinese population, as the method of obtaining respondents obviously greatly limits those citizens with little or no access to the Internet.
-That said, we are comfortable that our sample is generally representative of Chinese Internet users.
-Given that our research focus centers on Internet effects, it makes sense to have a large sample of Internet users.
-A sampling frame including the entire Chinese population did not make sense for this research.
-Half of the population do not regularly access the Internet according to World Bank and China Internet Network Information Center (CNNIC) data as of late 2015 when we conducted our survey.
-Using a sample of the entire population could potentially limit the degrees of freedom in our models and the marginals of nuanced measures of digital media use would likely become too small to have any value.
-Thus, the large sample of Internet users adds to our confidence in the inferences throughout the book.
+\hypertarget{data}{%
+\subsection{Data}\label{data}}
 
-## Summary statistics
+Our data are based on a random Internet survey conducted by Qualtrics
+from November 25 to December 2, 2015. We designed the instrument,
+content and structure. After we designed the instrument in English and
+translated it into Chinese, we entered the questions into the graphical
+interface provided from our survey provider, Qualtrics. We were careful
+at this stage to make the formatting clear, and to distribute the
+questions across numerous pages to prevent overwhelming respondents with
+too many questions at once. This helped us achieve a high completion and
+response rate. Additionally, we were particularly attentive to the
+possibility of question order effects. Many of the questions are
+sensitive and could cue responses to subsequent questions. We grouped
+and placed questions strategically to limit any such potential for
+response bias. Once we settled on the design, Qualtrics administered the
+survey in November 2015. They recruit a large pool of respondents for
+various survey projects through online advertising on websites such as
+local portals, search engines, social networking services, and/or online
+shopping services. Panelists who update their profiles at least once
+every 6 months are randomly invited to participate in surveys for which
+they qualify. Online points are awarded to the corresponding panelists,
+which they may accumulate and exchange for cash or various other
+country-specific gifts to serve as an incentive for completion. This
+number of points is based on the length of the survey. Ours had over
+fifty questions, so respondents received a relatively high number of
+points.
 
-### Summary stats table
+The data collection had two phases. For the first phase, Qualtrics
+collected and submitted to us a trial run of 286 cases. We were able to
+check the data for reliability and adjust the instrument before
+proceeding with the second phase, the final data collection. We only
+made three adjustments, all of which turned out to be important and
+central to our analysis. For the trial run, we only asked respondents
+about pro-government Internet posters and did not ask them about
+potential net-spy or hostile posters. We amended this oversight and it
+became central to the analysis that follows. In addition, much of our
+theory focuses on the impact of Chinese Internet users circumventing
+government filters on the Internet. We initially had a question about
+whether citizens had jumped the wall to read sensitive political
+information (see Appendix A -- Q25), but decided to add whether they had
+done so for entertainment purposes as well (Q26 - to watch foreign
+movies, television shows, etc.). Finally, we also included an attention
+filter question as part of a battery of institutional trust questions
+where respondents were simply told to select the ``None at all''
+response (Q13H). If they did not select this response, we could assume
+they were not paying attention to the questions, and the survey ended
+for these respondents and the data were not collected for them. In the
+end, the full sample included a total of 2292 respondents. This sample
+size provides for a roughly ±2 margin of error.
 
-```{r summarystats}
-key.vars <- china_isolation_data %>% 
-  select(c(connected, gen_social_med, urbanicity, ses, female, CCP_member, age, jump_wall))
+While our sample was randomly selected, the sampling frame was based
+only on Internet users that Qualtrics can access. Qualtrics recruits
+their frame subjects through online advertising on websites such as
+local portals, search engines, social networking services, and/or online
+shopping services. We do not contend that our sample is representative
+of the Chinese population, as the method of obtaining respondents
+obviously greatly limits those citizens with little or no access to the
+Internet. That said, we are comfortable that our sample is generally
+representative of Chinese Internet users. Given that our research focus
+centers on Internet effects, it makes sense to have a large sample of
+Internet users. A sampling frame including the entire Chinese population
+did not make sense for this research. Half of the population do not
+regularly access the Internet according to World Bank and China Internet
+Network Information Center (CNNIC) data as of late 2015 when we
+conducted our survey. Using a sample of the entire population could
+potentially limit the degrees of freedom in our models and the marginals
+of nuanced measures of digital media use would likely become too small
+to have any value. Thus, the large sample of Internet users adds to our
+confidence in the inferences throughout the book.
 
-kable(summarize(key.vars, type="numeric")) %>% 
-  kable_styling(latex_options="striped")
-```
-
-### Correlations
-
-```{r correlations}
-cors <- cor(key.vars, use="complete.obs")
-
-ggcorrplot(cors, title="Key variables associated with connectedness", 
-           lab=TRUE, type="lower", insig="blank")
-```
-
-## Models
-
-```{r models}
-mod1 <- lm(connected ~ gen_social_med + urbanicity + ses + female + CCP_member + age + jump_wall, data = china_isolation_data)
-
-mod2 <- lm(connected ~ gen_social_med*urbanicity + ses + female + CCP_member + age + jump_wall, data = china_isolation_data)
-
-mod3 <- lm(connected ~ gen_social_med*jump_wall + urbanicity + ses + female + CCP_member + age, data = china_isolation_data)
-
-tab_model(mod1, mod2, mod3, show.ci = FALSE)
-```
-
-## Margin plots
-
-```{r marginplots}
-a = plot_model(mod2, type = "pred", title = "", terms = c("gen_social_med", "urbanicity")
-               , legend.title = "Urbanicity") +
-  scale_color_discrete(labels = c("Village", "Small City", "Mid-sized City", "Suburb", "Big City")) +
-  ylab("Feelings of Isolation") +
-  xlab("Social Media Use")
-
-b = plot_model(mod3, type = "pred", title = "", terms = c("gen_social_med", "jump_wall")
-               , legend.title = "Globally Connected") +
-  scale_color_discrete(labels = c("Never", "", "", "A Moderate Amount", "", "", "Very Often")) +
-  ylab("Feelings of Isolation") +
-  xlab("Social Media Use")
-
-grid.arrange(a, b)
-```
+\end{document}

### 2023-05-29 starting script/china_isolationism_script.R

@@ -1,62 +1,280 @@
+<<<<<<< Updated upstream
 load("../china_isolation_data.RData")
+=======
+load("C:/Users/j0gain01/Dropbox/Research/Internet Politics/China/Isolationism/china_isolation_data.RData")
+>>>>>>> Stashed changes
 
 names(china_isolation_data)
-table(china_isolation_data$connected)
-cor.test(china_isolation_data$gen_social_med,china_isolation_data$connected)
 
-mod1 = lm(connected ~ gen_social_med + urbanicity + ses + female + CCP_member + age + jump_wall, data = china_isolation_data)
-summary(mod1)
+#Variable Coding################################################################################
+#Social Isolation
+china_isolation_data$isolation = (china_isolation_data$Q7_A_rc + china_isolation_data$Q7_B_rc + china_isolation_data$Q7_C_rc)
 
+<<<<<<< Updated upstream
 mod2 = lm(connected ~ gen_social_med*urbanicity + urbases + female + CCP_member + age + jump_wall, data = china_isolation_data)
 summary(mod2)
 
 mod3 = lm(connected ~ gen_social_med*jump_wall + urbanicity + ses + female + CCP_member + age + jump_wall, data = china_isolation_data)
 summary(mod3)
+=======
+library(psy)
+isolation.matrix = cbind(
+  china_isolation_data$Q7_A_rc,
+  china_isolation_data$Q7_B_rc,
+  china_isolation_data$Q7_C_rc
+)
+cronbach(isolation.matrix)
 
+library(scales)
+china_isolation_data$isolation = rescale(china_isolation_data$isolation, to = c(0, 1))
+summary(china_isolation_data$isolation)
+>>>>>>> Stashed changes
+
+#Digital Human Interaction
+table(china_isolation_data$Q8_1_rc)
+table(china_isolation_data$Q8_2_rc)
+table(china_isolation_data$Q8_3_rc)
+table(china_isolation_data$Q8_4_rc)
+table(china_isolation_data$Q8_5_rc)
+table(china_isolation_data$Q8_6_rc)
+
+library(scales)
+china_isolation_data$human_interaction = rescale((china_isolation_data$Q8_1_rc + china_isolation_data$Q8_2_rc + china_isolation_data$Q8_3_rc
+                                                 + china_isolation_data$Q8_4_rc + china_isolation_data$Q8_5_rc + china_isolation_data$Q8_6_rc),
+                                    t0 = c(0,1))
[…]

### 2023-06-02 Social Isolation in China old.qmd
backup file

---
title: "The Spatial Relationship between Social Media, Digital Connectedness, and Social Isolation in China: Revisting Cyber-Optimism"
author: 
  - Jason Gainous^[University of Louisville, jason.gainous@louisville.edu]
  - Andrew W. MacDonald^[Duke Kunshan University, andrew.macdonald@dukekunshan.edu.cn]
date: '`r format(Sys.time(), "%B %d, %Y")`'
abstract: "Early research and popular discourse on the promise of the internet was optimistic. Many believed it would promote social interconnectedness and, ultimately, be a positive force in people’s lives. Since these early predictions, research has become much less positive, usually pointing to the negative aspects of social media. Here we test whether the digital environment can actually create a space that deters feelings of social isolationism especially for those living outside cities in restrictive information environments where citizens are often disconnected from the outside world. Using data from a nationwide survey of Chinese citizens we conducted in 2015, we do find that the more citizens digitally connect with others, the less personally isolated they feel, but that this relationship is less pronounced for those in rural communities. Conversely, though, the more likely people are to move relationships from online to offline, and the more they use social media, the more personally isolated they feel. These counter-relationships are more pronounced for those in rural communities. Generally, those living in urban environments tend to feel more isolated, and digital connection does not seem to mediate this spatial factor. In fact, it exacerbates loneliness."
keywords: 
  - Social Isolation
  - Social Media
  - Digital Communication
  - China
format: pdf
execute: 
  echo: false
  warning: false
bibliography: references.bib
---

```{r}
# labeL: setup

library(tidyverse)
library(sjPlot)
library(ggpubr)
library(grid)
library(stargazer)
library(scales)
library(papeR)
library(gridExtra)
library(knitr)
library(kableExtra)
library(ggcorrplot)

load("china_isolation_data.RData")

china_isolation_data <- china_original_amanzhol
```

# Social Isolation in China

## Introduction

Research is quite mixed when it comes to identifying the relationship between social media use and feelings of isolationism. Early research suggested that the internet would build social capital, or an interconnectedness between people, and that social media platforms were the ultimate way to bring people together. Since then, research indicates that the effect may be the opposite for many. Social media may encourage social isolation, and ultimately, social media users may feel more disconnected from others than those who do not use social media. We know very little about this phenomenon in China. China presents an interesting case because the internet is bifurcated to some degree -- there is the Chinese internet and the outside internet available via VPNs. Being connected to the outside world may lessen feelings of isolation, or it may increase these feelings because digital exposure to a world is much larger than that in people's immediate environment without the ability to have in-person connection to may make one feel isolated. Interestingly, and somewhat ironically though, it may also matter, too, whether someone lives in a city. Research has suggested that urban living can actually lead to feelings of isolation.

## Introduction

Research is quite mixed when it comes to identifying the relationship between social media use and feelings of isolationism. Early research suggested that the internet would build social capital, or an interconnectedness between people, and that social media platforms were the ultimate way to bring people together. Since then, research indicates that the effect may be the opposite for many. Social media may encourage social isolation, and ultimately, social media users may feel more disconnected from others than those who do not use social media. We know very little about this phenomenon in China. China presents an interesting case because the internet is bifurcated to some degree -- there is the Chinese internet and the outside internet available via VPNs. Being connected to the outside world may lessen feelings of isolation, or it may increase these feelings because digital exposure to a world is much larger than that in people's immediate environment without the ability to have in-person connection to may make one feel isolated. Interestingly, and somewhat ironically though, it may also matter, too, whether someone lives in a city. Research has suggested that urban living can actually lead to feelings of isolation.

## Data, Measurement and Descriptives

The data from this study are original. We designed a survey instrument in English, and translated it into Chinese, to measure a range of concepts including social isolationism and various dimensions of social media and digital information consumption. We employed Qualtrics to collect the data. They randomly selected 2292 respondents from their existing panel[^1] from November 25 to December 2, 2015. This sample size on provides for a roughly ±2 margin of error.[^2]

[^1]: Qualtrics recruits a large pool of respondents for various survey projects through online advertising. Recruits who update their profiles at least once every 6 months are randomly invited to participate. These recruits are awarded online points that can be exchanged for cash or various other country-specific gifts. The number of points is based on the length of the survey, and since our survey had over fifty questions, respondents received a relatively high number of points.

[^2]: We were able to first collect a small sample (\$n\$=286) to check the reliability and adjust the instrument after before proceeding with the final data collection. We made three adjustments, none of which are related to the measures used in the current study.

Our dependent variable, **social isolationism**, is a three-item additive index. Respondents were given the following introduction: The next question is about how you feel about different aspects of your life. Could you tell me for each one if you feel that way always, almost always, some of the time, rarely or never? Then they were asked: A) How often do you feel that you lack companionship, B) How often do you feel isolated from others?, and C) How often do you feel left out? Response options were recoded so that higher responses equated to feeling more socially isolated, they were all three added together, and then rescaled to range from 0 through 1 maintaining the original intervals ($\alpha$ = 0.86). The distribution of that index is presented in Figure [isolation]{.smallcaps}. The distribution is relatively normal centered around the midpoint with a slight skew to the right. Most respondents appear to be on the low end, indicating the the majority of those in our sample do not feel particularly isolated. Conversely, the right skew in the distribution does suggest that a sizable chunk of folks feel quite socially isolated. Altogether, the spread out distribution indicates quite a bit of variance ($\mu$ = 0.41, sd = 0.20).

## Results

Given that the first two dependent variables (human interaction, online to offline to offline relationships) in our profile models are distributed ordinally, we initially estimate linear models of those outcomes and examine the residual behavior to determine if a linear model fits the data well or if an ordered outcome model is a better fit. The results were clear, a linear model is not a good fit for either outcome (see the figures in the Online Appendix), so we fit the models using ordered logit. Because our measure of general social media is based on an additive index, we treat it as continuous, and accordingly fit a linear model.

Our modeling strategy that follows is straightforward. We begin by modeling each of our internet communication independent variables as function of socio-economic status (SES), gender, Chinese Communist Party membership (CCP), and age to create an individual profile of each type of digital user (see the Online Appendix for the operationalization of these variables). This provides some context for the models that follow which are intended to test our primary hypotheses, that is that internet communication can deter social isolation and that this is particularly true for those who do not have the convenience of the high social interaction opportunity provided by urban living. For those we begin by fitting an additive model of our index of social isolationism as function of each of our primary independent variables while also controlling for the same variables included in our profile models. Finally, we refit three models with the same specification but introduce an interactive term between each of our internet communication indicators, respectively, with our measure of urbanicity. This allows us to test whether the observed additive effects are stronger for those living outside cities.

We have several primary independent variables including **human interaction**, **online to offline relationships**, **general social media use**, and **urbanicity**. We measured human interaction with a single item: Has the internet and phone applications increased your contact with the following groups of people (check yes to all that apply)? The response options were: 1) Family that lives nearby, 2) Family that lives far away, 3) Friends that live nearby, 4) Friends that live far away, 5) People you met on the internet that live nearby, and 6) People you met on the internet that live far away. We simply counted the number of selected responses so the item ranged from 0 to 6, and then for the models that come later, we rescaled it to range from 0 through 1 maintaining the original intervals. Online to offline relationships was also measured with a single item: Have you met someone offline that you initially met online? Response options were: 1) Yes, many times, 2) Yes, several times, 3) Yes, once, and 4) No, never. We inverted this scale so that higher values represented more offline relationships, and again, rescaled it to range from 0 through 1 for the models that follow.

The distributions of these ordinal independent variables are reflected in Figure [ivs]{.smallcaps}. Very few people claimed to never have increased their contact/connections with others through the internet. The modal number of increased connections respondents claimed to have made through the internet was 2, followed closely by 1, but a sizable proportion of the sample, about 48% claimed to have increased their number of personal connections by 3 or more through the internet. Perhaps not surprisingly, the modal response when asked whether one had met someone online and that relationship moved offline was "No, never". On the other hand, we were surprised that about 37% of those sampled claimed to have moved relationships offline several times, over 10% said they had done so many times, and about 13% did so once. Taken altogether, a large proportion of our respondents seem to using the internet to facilitate social relations.

We measured general social media use with an index based on the following three items: 1) About how many hours a day would you estimate you spend using only social media? Social media means applications like Weibo, QQ, Renren, Kaixin001, Douban, WeChat or other sites and services that allow users to interact with each other. (0-1, 1-2, 2-3, 3-4, 4-5, 5-6, 6-7, 7-8, 8-9, or More than 9), 2) Do you check email, read websites, and use social media (social media means applications like Weibo, QQ, Renren, Kaixin001, Douban, WeChat or other sites and services that allow users to interact with each other) more than you did five years ago? (Yes, No), and 3) How often do you read news stories about political events that have been posted on social media (social media means applications like Weibo, QQ, Renren, Kaixin001, Douban, WeChat or other sites and services that allow users to interact with each other)? (More than once a day, Everyday, Three-to-five days per week, One-to-two days per week, Less often, Never). Each was recoded so that higher values represented more social media use, rescaled to range from 0 through 1, added together, and then again, rescaled to range from 0 through 1 maintaining all original intervals. The distribution of this index is presented in Figure \ref{genSM}. The distribution is relatively normal and tightly centered around the mean 0.63 with a standard deviation of 0.17, but there is a left skew suggesting that a portion of the population is not that social media active, but clearly the bulk of the population are.

Our final primary independent variable, urbanicity, was measured using a single item: Which of these best describes the place in which you live? (Countryside/Village, Small City, Mid-Sized City, Suburban Area of a Big City, Big City). For the purpose of the models, we rescaled this item to range from 0 through 1 maintaining the original intervals. The distribution is reflected in Figure [urban]{.smallcaps}. Given the rural to urban Chinese migration since the founding of the People's Republic \citep{xia.2019}, it is not surprising to see that nearly 45% of those in our sample live in cities, 7% in suburbs, and about 27% in mid-sized cities. About 16% say they live in small cities and only about 5% say they live in villages.

Our modeling strategy that follows is straightforward. We begin by modeling each of our internet communication independent variables as function of socio-economic status (SES), gender, Chinese Communist Party membership (CCP), and age to create an individual profile of each type of digital user (see the Online Appendix for the operationalization of these variables). This provides some context for the models that follow which are intended to test our primary hypotheses, that is that internet communication can deter social isolation and that this is particularly true for those who do not have the convenience of the high social interaction opportunity provided by urban living. For those we begin by fitting an additive model of our index of social isolationism as function of each of our primary independent variables while also controlling for the same variables included in our profile models. Finally, we refit three models with the same specification but introduce an interactive term between each of our internet communication indicators, respectively, with our measure of urbanicity. This allows us to test whether the observed additive effects are stronger for those living outside cities.

## Results

Given that the first two dependent variables (human interaction, online to offline to offline relationships) in our profile models are distributed ordinally, we initially estimate linear models of those outcomes and examine the residual behavior to determine if a linear model fits the data well or if an ordered outcome model is a better fit. The results were clear, a linear model is not a good fit for either outcome (see the figures in the Online Appendix), so we fit the models using ordered logit. Because our measure of general social media is based on an additive index, we treat it as continuous, and accordingly fit a linear model.

The results of our profile models are presented in Table [profile]{.smallcaps}. When it comes to SES, the relationship across all three of our internet communication is consistent. As SES goes up so does digital human interaction, the move from online to offline relationships, and general social media use. That gender is only statistically significant in the model of the move from online to offline relationships where women are less likely to do so. Interestingly, being a CCP member has inverse relationships with human interaction and the move from online to offline, where members are less likely to increase digital human interaction but are more likely to move online relationships offline. Finally, the older respondents were the more likely they were to increase human interaction, and the less likely they were to move relationships offline and use social media. These profile results provide background context for the models that follow. The internet communication indicators are our primary independent variables, so these profile models give us a sense for whom they matter the most when it comes to deterring social isolation.

The results of our models of social isolation are presented in Table Figure [interact]{.smallcaps}. The additive estimates in model (1) provide mixed results regarding whether internet communication is a positive force in deterring social isolation. Not surprisingly, there is a negative relationship between the number of digital connections (human interaction) folks make and feelings of social isolation. On the other hand, though, both moving online relationships offline and general social media use are positively related to feelings of social isolation. The latter is consistent with much of the literature outlined above, but the former is not. Perhaps, this is context driven. The results also indicate that those living in more urban environments tend to feel less socially isolated.

%NOTE: Andrew, do you want to speculate here about why online to offline is positively related - desparate peole?.

Models (2) - (4) in Table [interact]{.smallcaps} include each of the interactions between our three internet communication measures and urbanicity. The consistent result across the interactions is that the relationships are dulled for those living in more rural areas. The interaction between digital human interaction and urbanicity is statistically significant (p \< 0.01), as is that between the move from online to offline relationships and urbanicity (p \< 0.001), and that between general social media use and urbanicity only slightly misses the arbitrary 0.05 threshold (p = 0.07). The interactions are most easily interpreted graphically (see Figure [intergraph]{.smallcaps}).

The model (2) results are graphed in the upper left hand figure. Here it is clear that the negative relationship between digital human interaction and feelings of social isolation is considerably stronger for those in cities. For that matter, notice that the relationship for those in villages is basically flat; the 95 percent confidence interval around the slight negative slope indicates that the relationship could be flat.

The results from the interaction between online to offline relationships and urbanicity are displayed in the graph in the upper right hand corner of Figure [intergraph]{.smallcaps}. Again, here, the main effects run in the opposite direction than those of digital human interaction. Those who are more likely to move relationships from online to offline tend to feel more isolated, and the interactive results presented here suggest that this relations is stronger for those living in less urban spaces. Likewise, the same is the case for those using social media more frequently. In fact, the relationship here for those living in the largest cities is completely non-existent.

## Conclusion

Cyberoptimists heralded the internet as means by which people could connect, build social capital, and some suggested this could deter social isolationism. Our results provide little evidence of this optimistic view of the internet and its ability to improve the quality of people's lives. We do find that some are more likely to interact with family and friends and that this does deter feelings of social isolation, but on the other hand, even though many move online relationships offline and connect through social media, doing so does not deter feelings of social isolation. Instead, such digital actively is actually associated with increased feelings of social isolation.

We also found no evidence that the internet could serve as bridge to build connections for those living outside of cities. The optimistic view here would be that the internet could lower the costs of making connections for those who have less social opportunity, those living in less populated areas, and as a result, help them to feel less isolated. We, in fact, found the opposite. Internet communication had either less positive effect or more negative effect on feelings of social isolation for those living in less urban spaces.

Our contribution here is that we look at some well-established theoretical arguments in a context outside that of where most of the research centered on these type questions has examined. By no means, have we offered a definitive answer to whether there are contextual differences. We have, though, offered a good starting point to further examine the relationship between internet communication and social isolationism outside Western contexts.

## References

::: {#refs}
:::

## Online Appendix

### Variable Operationalization

### Residual Analysis

### 2023-06-06 Social Isolation in China.qmd
added extra intro
Merge cleanup

--- 2022-11-18 Social Isolation in China.qmd
@@
 ---
-title: "Connected or Disconnected?"
+title: "The Spatial Relationship between Social Media, Digital Connectedness, and Social Isolation in China: Revisting Cyber-Optimism"
 author: 
-  - Jason Gainous^[Duke Kunshan University, jason.gainous@louisville.edu]
+  - Jason Gainous^[University of Louisville, jason.gainous@louisville.edu]
   - Andrew W. MacDonald^[Duke Kunshan University, andrew.macdonald@dukekunshan.edu.cn]
 date: '`r format(Sys.time(), "%B %d, %Y")`'
-abstract: "The following brief paper is simply the preliminary results of our study.
-We seek to identify the relationship between social media use and feelings of isolationism in China.
-This study is based on original date.
-We conducted a nationwide survey of Chinese citizens conducted in 2015 measuring a range of concepts including those here.
-The preliminary results are promising.
-We develop an index of personal isolationism and model this as a function of social media use, connection to the outside digital world, and urbanicity, while controlling for a host of individual level factors.
-The results suggest the following: 1) Social media use does not have a generalized relationship with isolationism, 2) Those who use VPNs/proxy servers tend to feel less isolated than those who do not, 3) Those living in urban environments tend to feel more isolated, 3) There is a strong positive relationship between social media use and feelings of isolation for those who frequently use VPNs/proxy servers, and 4) The is a strong positive relationship between social media use and feelings of isolation for those living in rural China."
+abstract: "Early research and popular discourse on the promise of the internet was optimistic.
+Many believed it would promote social interconnectedness and, ultimately, be a positive force in people’s lives.
+Since these early predictions, research has become much less positive, usually pointing to the negative aspects of social media.
+Here we test whether the digital environment can actually create a space that deters feelings of social isolationism especially for those living outside cities in restrictive information environments where citizens are often disconnected from the outside world.
+Using data from a nationwide survey of Chinese citizens we conducted in 2015, we do find that the more citizens digitally connect with others, the less personally isolated they feel, but that this relationship is less pronounced for those in rural communities.
+Conversely, though, the more likely people are to move relationships from online to offline, and the more they use social media, the more personally isolated they feel.
+These counter-relationships are more pronounced for those in rural communities.
+Generally, those living in urban environments tend to feel more isolated, and digital connection does not seem to mediate this spatial factor.
+In fact, it exacerbates loneliness."
 keywords: 
-  - social isolation
-  - social media
+  - Social Isolation
+  - Social Media
+  - Digital Communication
   - China
 format: pdf
-editor: visual
+execute: 
+  echo: false
+  warning: false
+bibliography: references.bib
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
-knitr::opts_chunk$set(warning = FALSE)
-knitr::opts_chunk$set(message = FALSE)
+```{r}
+#| label: setup
+#| include: false
 
@@
 load("china_isolation_data.RData")
-
-china_isolation_data <- china_original_amanzhol
 ```
 
-# Social Isolation in China
+#### Data, Measurement, and Descriptives
 
-## Introduction
+The data from this study are original.
+We designed a survey instrument in English, and translated it into Chinese, to measure a range of concepts including social isolationism and various dimensions of social media and digital information consumption.
+We employed Qualtrics to collect the data.
+They randomly selected 2292 respondents from their existing panel[^1] from November 25 to December 2, 2015.
+This sample size on provides for a roughly ±2 margin of error.[^2]
 
-Research is quite mixed when it comes to identifying the relationship between social media use and feelings of isolationism.
-Early research suggested that the internet would build social capital, or an interconnectedness between people, and that social media platforms were the ultimate way to bring people together.
-Since then, research indicates that the effect may be the opposite for many.
-Social media may encourage social isolation, and ultimately, social media users may feel more disconnected from others than those who do not use social media.
-We know very little about this phenomenon in China.
-China presents an interesting case because the internet is bifurcated to some degree – there is the Chinese internet and the outside internet available via VPNs.
-Being connected to the outside world may lessen feelings of isolation, or it may increase these feelings because digital exposure to a world is much larger than that in people’s immediate environment without the ability to have in-person connection to may make one feel isolated.
-Interestingly, and somewhat ironically though, it may also matter, too, whether someone lives in a city.
-Research has suggested that urban living can actually lead to feelings of isolation.
+[^1]: Qualtrics recruits a large pool of respondents for various survey projects through online advertising.
+Recruits who update their profiles at least once every 6 months are randomly invited to participate.
+These recruits are awarded online points that can be exchanged for cash or various other country-specific gifts.
+The number of points is based on the length of the survey, and since our survey had over fifty questions, respondents received a relatively high number of points.
 
-## Data
+[^2]: We were able to first collect a small sample (n = 286) to check the reliability and adjust the instrument after before proceeding with the final data collection.
+We made three adjustments, none of which are related to the measures used in the current study.
 
-Our data are based on a random Internet survey conducted by Qualtrics from November 25 to December 2, 2015.
-We designed the instrument, content and structure.
-After we designed the instrument in English and translated it into Chinese, we entered the questions into the graphical interface provided from our survey provider, Qualtrics.
-We were careful at this stage to make the formatting clear, and to distribute the questions across numerous pages to prevent overwhelming respondents with too many questions at once.
-This helped us achieve a high completion and response rate.
-Additionally, we were particularly attentive to the possibility of question order effects.
-Many of the questions are sensitive and could cue responses to subsequent questions.
-We grouped and placed questions strategically to limit any such potential for response bias.
-Once we settled on the design, Qualtrics administered the survey in November 2015.
-They recruit a large pool of respondents for various survey projects through online advertising on websites such as local portals, search engines, social networking services, and/or online shopping services.
-Panelists who update their profiles at least once every 6 months are randomly invited to participate in surveys for which they qualify.
-Online points are awarded to the corresponding panelists, which they may accumulate and exchange for cash or various other country-specific gifts to serve as an incentive for completion.
-This number of points is based on the length of the survey.
-Ours had over fifty questions, so respondents received a relatively high number of points.
+Our dependent variable, *social isolationism*, is a three-item additive index.
+Respondents were given the following introduction: The next question is about how you feel about different aspects of your life.
+Could
+you tell me for each one if you feel that way always, almost always, some of the time, rarely or never?
+Then they were asked: A) How often do you feel that you lack companionship, B) How often do you feel isolated from others?, and C) How often do you feel left out?
+Response options were recoded so that higher responses equated to feeling more socially isolated, they were all three added together, and then rescaled to range from 0 through 1 maintaining the original intervals (\\alpha = 0.86).
+The distribrution of that index is presented in
 
-The data collection had two phases.
-For the first phase, Qualtrics collected and submitted to us a trial run of 286 cases.
-We were able to check the data for reliability and adjust the instrument before proceeding with the second phase, the final data collection.
-We only made three adjustments, all of which turned out to be important and central to our analysis.
-For the trial run, we only asked respondents about pro-government Internet posters and did not ask them about potential net-spy or hostile posters.
-We amended this oversight and it became central to the analysis that follows.
-In addition, much of our theory focuses on the impact of Chinese Internet users circumventing government filters on the Internet.
-We initially had a question about whether citizens had jumped the wall to read sensitive political information (see Appendix A – Q25), but decided to add whether they had done so for entertainment purposes as well (Q26 - to watch foreign movies, television shows, etc.).
-Finally, we also included an attention filter question as part of a battery of institutional trust questions where respondents were simply told to select the “None at all” response (Q13H).
-If they did not select this response, we could assume they were not paying attention to the questions, and the survey ended for these respondents and the data were not collected for them.
-In the end, the full sample included a total of 2292 respondents.
-This sample size provides for a roughly ±2 margin of error.
+## Data, Measurement and Descriptives
 
-While our sample was randomly selected, the sampling frame was based only on Internet users that Qualtrics can access.
-Qualtrics recruits their frame subjects through online advertising on websites such as local portals, search engines, social networking services, and/or online shopping services.
-We do not contend that our sample is representative of the Chinese population, as the method of obtaining respondents obviously greatly limits those citizens with little or no access to the Internet.
-That said, we are comfortable that our sample is generally representative of Chinese Internet users.
-Given that our research focus centers on Internet effects, it makes sense to have a large sample of Internet users.
-A sampling frame including the entire Chinese population did not make sense for this research.
-Half of the population do not regularly access the Internet according to World Bank and China Internet Network Information Center (CNNIC) data as of late 2015 when we conducted our survey.
-Using a sample of the entire population could potentially limit the degrees of freedom in our models and the marginals of nuanced measures of digital media use would likely become too small to have any value.
-Thus, the large sample of Internet users adds to our confidence in the inferences throughout the book.
+The data from this study are original.
+We designed a survey instrument in English, and translated it into Chinese, to measure a range of concepts including social isolationism and various dimensions of social media and digital information consumption.
+We employed Qualtrics to collect the data.
+They randomly selected 2292 respondents from their existing panel[^1] from November 25 to December 2, 2015.
+This sample size on provides for a roughly ±2 margin of error.[^2]
 
-## Summary statistics
+[^1]: Qualtrics recruits a large pool of respondents for various survey projects through online advertising.
+Recruits who update their profiles at least once every 6 months are randomly invited to participate.
+These recruits are awarded online points that can be exchanged for cash or various other country-specific gifts.
+The number of points is based on the length of the survey, and since our survey had over fifty questions, respondents received a relatively high number of points.
 
-### Summary stats table
-```{r summarystats}
-key.vars <- china_isolation_data %>% 
-  select(c(connected, gen_social_med, urbanicity, ses, female, CCP_member, age, jump_wall))
+[^2]: We were able to first collect a small sample (\$n\$=286) to check the reliability and adjust the instrument after before proceeding with the final data collection.
+We made three adjustments, none of which are related to the measures used in the current study.
 
-kable(summarize(key.vars, type="numeric")) %>% 
-  kable_styling(latex_options="striped")
+Our dependent variable, **social isolationism**, is a three-item additive index.
+Respondents were given the following introduction: The next question is about how you feel about different aspects of your life.
+Could you tell me for each one if you feel that way always, almost always, some of the time, rarely or never?
+Then they were asked: A) How often do you feel that you lack companionship, B) How often do you feel isolated from others?, and C) How often do you feel left out?
+Response options were recoded so that higher responses equated to feeling more socially isolated, they were all three added together, and then rescaled to range from 0 through 1 maintaining the original intervals ($\alpha$ = 0.86).
+The distribution of that index is presented in Figure [isolation]{.smallcaps}.
+The distribution is relatively normal centered around the midpoint with a slight skew to the right.
+Most respondents appear to be on the low end, indicating the the majority of those in our sample do not feel particularly isolated.
+Conversely, the right skew in the distribution does suggest that a sizable chunk of folks feel quite socially isolated.
+Altogether, the spread out distribution indicates quite a bit of variance ($\mu$ = 0.41, sd = 0.20).
+
+## Results
+
+Given that the first two dependent variables (human interaction, online to offline to offline relationships) in our profile models are distributed ordinally, we initially estimate linear models of those outcomes and examine the residual behavior to determine if a linear model fits the data well or if an ordered outcome model is a better fit.
+The results were clear, a linear model is not a good fit for either outcome (see the figures in the Online Appendix), so we fit the models using ordered logit.
+Because our measure of general social media is based on an additive index, we treat it as continuous, and accordingly fit a linear model.
+
+Our modeling strategy that follows is straightforward.
+We begin by modeling each of our internet communication independent variables as function of socio-economic status (SES), gender, Chinese Communist Party membership (CCP), and age to create an individual profile of each type of digital user (see the Online Appendix for the operationalization of these variables).
+This provides some context for the models that follow which are intended to test our primary hypotheses, that is that internet communication can deter social isolation and that this is particularly true for those who do not have the convenience of the high social interaction opportunity provided by urban living.
+For those we begin by fitting an additive model of our index of social isolationism as function of each of our primary independent variables while also controlling for the same variables included in our profile models.
+Finally, we refit three models with the same specification but introduce an interactive term between each of our internet communication indicators, respectively, with our measure of urbanicity.
+This allows us to test whether the observed additive effects are stronger for those living outside cities.
+
+We have several primary independent variables including **human interaction**, **online to offline relationships**, **general social media use**, and **urbanicity**.
+We measured human interaction with a single item: Has the internet and phone applications increased your contact with the following groups of people (check yes to all that apply)?
+The response options were: 1) Family that lives nearby, 2) Family that lives far away, 3) Friends that live nearby, 4) Friends that live far away, 5) People you met on the internet that live nearby, and 6) People you met on the internet that live far away.
+We simply counted the number of selected responses so the item ranged from 0 to 6, and then for the models that come later, we rescaled it to range from 0 through 1 maintaining the original intervals.
+Online to offline relationships was also measured with a single item: Have you met someone offline that you initially met online?
+Response options were: 1) Yes, many times, 2) Yes, several times, 3) Yes, once, and 4) No, never.
+We inverted this scale so that higher values represented more offline relationships, and again, rescaled it to range from 0 through 1 for the models that follow.
+
+```{r}
+#| label: fig-ivs
+
 ```
 
-### Correlations
+The distributions of these ordinal independent variables are reflected in Figure [ivs]{.smallcaps}.
+Very few people claimed to never have increased their contact/connections with others through the internet.
+The modal number of increased connections respondents claimed to have made through the internet was 2, followed closely by 1, but a sizable proportion of the sample, about 48% claimed to have increased their number of personal connections by 3 or more through the internet.
+Perhaps not surprisingly, the modal response when asked whether one had met someone online and that relationship moved offline was "No, never".
+On the other hand, we were surprised that about 37% of those sampled claimed to have moved relationships offline several times, over 10% said they had done so many times, and about 13% did so once.
+Taken altogether, a large proportion of our respondents seem to using the internet to facilitate social relations.
 
-```{r correlations}
-cors <- cor(key.vars, use="complete.obs")
+We measured general social media use with an index based on the following three items: 1) About how many hours a day would you estimate you spend using only social media?
+Social media means applications like Weibo, QQ, Renren, Kaixin001, Douban, WeChat or other sites and services that allow users to interact with each other.
+(0-1, 1-2, 2-3, 3-4, 4-5, 5-6, 6-7, 7-8, 8-9, or More than 9), 2) Do you check email, read websites, and use social media (social media means applications like Weibo, QQ, Renren, Kaixin001, Douban, WeChat or other sites and services that allow users to interact with each other) more than you did five years ago?
+(Yes, No), and 3) How often do you read news stories about political events that have been posted on social media (social media means applications like Weibo, QQ, Renren, Kaixin001, Douban, WeChat or other sites and services that allow users to interact with each other)?
+(More than once a day, Everyday, Three-to-five days per week, One-to-two days per week, Less often, Never).
+Each was recoded so that higher values represented more social media use, rescaled to range from 0 through 1, added together, and then again, rescaled to range from 0 through 1 maintaining all original intervals.
+The distribution of this index is presented in Figure \ref{genSM}.
+The distribution is relatively normal and tightly centered around the mean 0.63 with a standard deviation of 0.17, but there is a left skew suggesting that a portion of the population is not that social media active, but clearly the bulk of the population are.
 
-ggcorrplot(cors, title="Key variables associated with connectedness", 
-           lab=TRUE, type="lower", insig="blank")
+```{r}
+#| label: fig-genSM
+
+figure1 = ggplot(china_isolation_data, aes(x=isolation)) + 
+  geom_histogram(aes(y=..density..), colour="black", fill="seashell", size=1)+
+  geom_density(alpha=.2, fill="#FF6666") +
+  xlab("Social Isolationism") +
+  ylab("Density") +
+  theme(panel.border = element_rect(color = "black",fill = NA, size = 1))
+figure1
 ```
 
-## Models
+Our final primary independent variable, urbanicity, was measured using a single item: Which of these best describes the place in which you live?
+(Countryside/Village, Small City, Mid-Sized City, Suburban Area of a Big City, Big City).
+For the purpose of the models, we rescaled this item to range from 0 through 1 maintaining the original intervals.
+The distribution is reflected in Figure [urban]{.smallcaps}.
+Given the rural to urban Chinese migration since the founding of the People's Republic \citep{xia.2019}, it is not surprising to see that nearly 45% of those in our sample live in cities, 7% in suburbs, and about 27% in mid-sized cities.
+About 16% say they live in small cities and only about 5% say they live in villages.
 
-```{r models}
-mod1 <- lm(connected ~ gen_social_med + urbanicity + ses + female + CCP_member + age + jump_wall, data = china_isolation_data)
+Our modeling strategy that follows is straightforward.
+We begin by modeling each of our internet communication independent variables as function of socio-economic status (SES), gender, Chinese Communist Party membership (CCP), and age to create an individual profile of each type of digital user (see the Online Appendix for the operationalization of these variables).
+This provides some context for the models that follow which are intended to test our primary hypotheses, that is that internet communication can deter social isolation and that this is particularly true for those who do not have the convenience of the high social interaction opportunity provided by urban living.
+For those we begin by fitting an additive model of our index of social isolationism as function of each of our primary independent variables while also controlling for the same variables included in our profile models.
+Finally, we refit three models with the same specification but introduce an interactive term between each of our internet communication indicators, respectively, with our measure of urbanicity.
+This allows us to test whether the observed additive effects are stronger for those living outside cities.
 
-mod2 <- lm(connected ~ gen_social_med*urbanicity + ses + female + CCP_member + age + jump_wall, data = china_isolation_data)
+## Results
 
-mod3 <- lm(connected ~ gen_social_med*jump_wall + urbanicity + ses + female + CCP_member + age, data = china_isolation_data)
+Given that the first two dependent variables (human interaction, online to offline to offline relationships) in our profile models are distributed ordinally, we initially estimate linear models of those outcomes and examine the residual behavior to determine if a linear model fits the data well or if an ordered outcome model is a better fit.
+The results were clear, a linear model is not a good fit for either outcome (see the figures in the Online Appendix), so we fit the models using ordered logit.
+Because our measure of general social media is based on an additive index, we treat it as continuous, and accordingly fit a linear model.
 
-tab_model(mod1, mod2, mod3, show.ci = FALSE)
-```
+The results of our profile models are presented in Table [profile]{.smallcaps}.
+When it comes to SES, the relationship across all three of our internet communication is consistent.
+As SES goes up so does digital human interaction, the move from online to offline relationships, and general social media use.
+That gender is only statistically significant in the model of the move from online to offline relationships where women are less likely to do so.
+Interestingly, being a CCP member has inverse relationships with human interaction and the move from online to offline, where members are less likely to increase digital human interaction but are more likely to move online relationships offline.
+Finally, the older respondents were the more likely they were to increase human interaction, and the less likely they were to move relationships offline and use social media.
+These profile results provide background context for the models that follow.
+The internet communication indicators are our primary independent variables, so these profile models give us a sense for whom they matter the most when it comes to deterring social isolation.
 
-## Margin plots
+The results of our models of social isolation are presented in Table Figure [interact]{.smallcaps}.
+The additive estimates in model (1) provide mixed results regarding whether internet communication is a positive force in deterring social isolation.
+Not surprisingly, there is a negative relationship between the number of digital connections (human interaction) folks make and feelings of social isolation.
+On the other hand, though, both moving online relationships offline and general social media use are positively related to feelings of social isolation.
+The latter is consistent with much of the literature outlined above, but the former is not.
+Perhaps, this is context driven.
+The results also indicate that those living in more urban environments tend to feel less socially isolated.
 
-```{r marginplots}
-a = plot_model(mod2, type = "pred", title = "", terms = c("gen_social_med", "urbanicity")
-               , legend.title = "Urbanicity") +
-  scale_color_discrete(labels = c("Village", "Small City", "Mid-sized City", "Suburb", "Big City")) +
-  ylab("Feelings of Isolation") +
-  xlab("Social Media Use")
+%NOTE: Andrew, do you want to speculate here about why online to offline is positively related - desparate peole?.
 
-b = plot_model(mod3, type = "pred", title = "", terms = c("gen_social_med", "jump_wall")
-               , legend.title = "Globally Connected") +
-  scale_color_discrete(labels = c("Never", "", "", "A Moderate Amount", "", "", "Very Often")) +
-  ylab("Feelings of Isolation") +
-  xlab("Social Media Use")
+Models (2) - (4) in Table [interact]{.smallcaps} include each of the interactions between our three internet communication measures and urbanicity.
+The consistent result across the interactions is that the relationships are dulled for those living in more rural areas.
+The interaction between digital human interaction and urbanicity is statistically significant (p \< 0.01), as is that between the move from online to offline relationships and urbanicity (p \< 0.001), and that between general social media use and urbanicity only slightly misses the arbitrary 0.05 threshold (p = 0.07).
+The interactions are most easily interpreted graphically (see Figure [intergraph]{.smallcaps}).
 
-grid.arrange(a, b)
-```
+The model (2) results are graphed in the upper left hand figure.
+Here it is clear that the negative relationship between digital human interaction and feelings of social isolation is considerably stronger for those in cities.
+For that matter, notice that the relationship for those in villages is basically flat; the 95 percent confidence interval around the slight negative slope indicates that the relationship could be flat.
+
+The results from the interaction between online to offline relationships and urbanicity are displayed in the graph in the upper right hand corner of Figure [intergraph]{.smallcaps}.
+Again, here, the main effects run in the opposite direction than those of digital human interaction.
+Those who are more likely to move relationships from online to offline tend to feel more isolated, and the interactive results presented here suggest that this relations is stronger for those living in less urban spaces.
+Likewise, the same is the case for those using social media more frequently.
+In fact, the relationship here for those living in the largest cities is completely non-existent.
+
+## Conclusion
+
+Cyberoptimists heralded the internet as means by which people could connect, build social capital, and some suggested this could deter social isolationism.
+Our results provide little evidence of this optimistic view of the internet and its ability to improve the quality of people's lives.
+We do find that some are more likely to interact with family and friends and that this does deter feelings of social isolation, but on the other hand, even though many move online relationships offline and connect through social media, doing so does not deter feelings of social isolation.
+Instead, such digital actively is actually associated with increased feelings of social isolation.
+
+We also found no evidence that the internet could serve as bridge to build connections for those living outside of cities.
+The optimistic view here would be that the internet could lower the costs of making connections for those who have less social opportunity, those living in less populated areas, and as a result, help them to feel less isolated.
+We, in fact, found the opposite.
+Internet communication had either less positive effect or more negative effect on feelings of social isolation for those living in less urban spaces.
+
+Our contribution here is that we look at some well-established theoretical arguments in a context outside that of where most of the research centered on these type questions has examined.
+By no means, have we offered a definitive answer to whether there are contextual differences.
+We have, though, offered a good starting point to further examine the relationship between internet communication and social isolationism outside Western contexts.
+
+## References
+
+::: {#refs}
+:::
+
+## Online Appendix
+
+### Variable Operationalization
+
+### Residual Analysis

### 2023-06-06 starting script/china_isolationism_script.R

@@ -1,22 +1,19 @@
-<<<<<<< Updated upstream
 load("../china_isolation_data.RData")
-=======
-load("C:/Users/j0gain01/Dropbox/Research/Internet Politics/China/Isolationism/china_isolation_data.RData")
->>>>>>> Stashed changes
 
 names(china_isolation_data)
 
-#Variable Coding################################################################################
+#Variable Coding
+
 #Social Isolation
+
 china_isolation_data$isolation = (china_isolation_data$Q7_A_rc + china_isolation_data$Q7_B_rc + china_isolation_data$Q7_C_rc)
 
-<<<<<<< Updated upstream
 mod2 = lm(connected ~ gen_social_med*urbanicity + urbases + female + CCP_member + age + jump_wall, data = china_isolation_data)
 summary(mod2)
 
 mod3 = lm(connected ~ gen_social_med*jump_wall + urbanicity + ses + female + CCP_member + age + jump_wall, data = china_isolation_data)
 summary(mod3)
-=======
+
 library(psy)
 isolation.matrix = cbind(
   china_isolation_data$Q7_A_rc,
@@ -28,7 +25,7 @@ cronbach(isolation.matrix)
 library(scales)
 china_isolation_data$isolation = rescale(china_isolation_data$isolation, to = c(0, 1))
 summary(china_isolation_data$isolation)
->>>>>>> Stashed changes
+
 
 #Digital Human Interaction
 table(china_isolation_data$Q8_1_rc)

### 2023-06-15 Social Isolation in China.qmd
Full replication of Jason paper

@@
 library(tidyverse)
-library(sjPlot)
-library(ggpubr)
 library(grid)
-library(stargazer)
+library(modelsummary)
 library(scales)
@@
 library(kableExtra)
-library(ggcorrplot)
+library(ggthemes)
+library(MASS)
+library(sjPlot)
+
+theme_set(theme_tufte())
 
@@
 
-#### Data, Measurement, and Descriptives
+# Social Isolation in China
 
-The data from this study are original.
-We designed a survey instrument in English, and translated it into Chinese, to measure a range of concepts including social isolationism and various dimensions of social media and digital information consumption.
-We employed Qualtrics to collect the data.
-They randomly selected 2292 respondents from their existing panel[^1] from November 25 to December 2, 2015.
-This sample size on provides for a roughly ±2 margin of error.[^2]
+"For example, when social media is used to facilitate offline relationships, to communicate, or to make new friends, it reduces feelings of loneliness \[140, 141\].
+In contrast, when social media is used to compensate for poor social skills by replacing offline interactions with online interactions, it significantly increases loneliness \[142,143,144\]." [@lim2020]
 
-[^1]: Qualtrics recruits a large pool of respondents for various survey projects through online advertising.
-Recruits who update their profiles at least once every 6 months are randomly invited to participate.
-These recruits are awarded online points that can be exchanged for cash or various other country-specific gifts.
-The number of points is based on the length of the survey, and since our survey had over fifty questions, respondents received a relatively high number of points.
+## Introduction
 
-[^2]: We were able to first collect a small sample (n = 286) to check the reliability and adjust the instrument after before proceeding with the final data collection.
-We made three adjustments, none of which are related to the measures used in the current study.
-
-Our dependent variable, *social isolationism*, is a three-item additive index.
-Respondents were given the following introduction: The next question is about how you feel about different aspects of your life.
-Could
-you tell me for each one if you feel that way always, almost always, some of the time, rarely or never?
-Then they were asked: A) How often do you feel that you lack companionship, B) How often do you feel isolated from others?, and C) How often do you feel left out?
-Response options were recoded so that higher responses equated to feeling more socially isolated, they were all three added together, and then rescaled to range from 0 through 1 maintaining the original intervals (\\alpha = 0.86).
-The distribrution of that index is presented in
+Research is quite mixed when it comes to identifying the relationship between social media use and feelings of isolationism.
+Early research suggested that the internet would build social capital, or an interconnectedness between people, and that social media platforms were the ultimate way to bring people together.
+Since then, research indicates that the effect may be the opposite for many.
+Social media may encourage social isolation, and ultimately, social media users may feel more disconnected from others than those who do not use social media.
+We know very little about this phenomenon in China.
+China presents an interesting case because the internet is bifurcated to some degree -- there is the Chinese internet and the outside internet available via VPNs.
+Being connected to the outside world may lessen feelings of isolation, or it may increase these feelings because digital exposure to a world is much larger than that in people's immediate environment without the ability to have in-person connection to may make one feel isolated.
+Interestingly, and somewhat ironically though, it may also matter, too, whether someone lives in a city.
+Research has suggested that urban living can actually lead to feelings of isolation.
 
@@
 They randomly selected 2292 respondents from their existing panel[^1] from November 25 to December 2, 2015.
-This sample size on provides for a roughly ±2 margin of error.[^2]
+This sample size on provides for a roughly $\pm2$ margin of error.[^2]
 
@@
 
-[^2]: We were able to first collect a small sample (\$n\$=286) to check the reliability and adjust the instrument after before proceeding with the final data collection.
+[^2]: We were able to first collect a small sample ($n=286$) to check the reliability and adjust the instrument after before proceeding with the final data collection.
 We made three adjustments, none of which are related to the measures used in the current study.
 
-Our dependent variable, **social isolationism**, is a three-item additive index.
+Our dependent variable, *social isolationism*, is a three-item additive index.
 Respondents were given the following introduction: The next question is about how you feel about different aspects of your life.
@@
 Then they were asked: A) How often do you feel that you lack companionship, B) How often do you feel isolated from others?, and C) How often do you feel left out?
-Response options were recoded so that higher responses equated to feeling more socially isolated, they were all three added together, and then rescaled to range from 0 through 1 maintaining the original intervals ($\alpha$ = 0.86).
-The distribution of that index is presented in Figure [isolation]{.smallcaps}.
+Response options were recoded so that higher responses equated to feeling more socially isolated, they were all three added together, and then rescaled to range from 0 through 1 maintaining the original intervals ($\alpha = 0.86$).
+The distribution of that index is presented in @fig-social-iso-dist.
 The distribution is relatively normal centered around the midpoint with a slight skew to the right.
@@
 Conversely, the right skew in the distribution does suggest that a sizable chunk of folks feel quite socially isolated.
-Altogether, the spread out distribution indicates quite a bit of variance ($\mu$ = 0.41, sd = 0.20).
+Altogether, the spread out distribution indicates quite a bit of variance ($\mu = 0.41$, $sd = 0.20$).
 
-## Results
+```{r}
+#| label: fig-social-iso-dist
+#| fig-cap: "Distribution of Social Isolationism Index"
 
-Given that the first two dependent variables (human interaction, online to offline to offline relationships) in our profile models are distributed ordinally, we initially estimate linear models of those outcomes and examine the residual behavior to determine if a linear model fits the data well or if an ordered outcome model is a better fit.
-The results were clear, a linear model is not a good fit for either outcome (see the figures in the Online Appendix), so we fit the models using ordered logit.
-Because our measure of general social media is based on an additive index, we treat it as continuous, and accordingly fit a linear model.
+figure1 = ggplot(china_isolation_data, aes(x=isolation)) + 
+  geom_histogram(aes(y=..density..), colour="black", fill="seashell")+
+  geom_density(alpha=.2, fill="#FF6666") +
+  xlab("Social Isolationism") +
+  ylab("Density") +
+  theme(panel.border = element_rect(color = "black",fill = NA))
+figure1
+```
 
-Our modeling strategy that follows is straightforward.
-We begin by modeling each of our internet communication independent variables as function of socio-economic status (SES), gender, Chinese Communist Party membership (CCP), and age to create an individual profile of each type of digital user (see the Online Appendix for the operationalization of these variables).
-This provides some context for the models that follow which are intended to test our primary hypotheses, that is that internet communication can deter social isolation and that this is particularly true for those who do not have the convenience of the high social interaction opportunity provided by urban living.
-For those we begin by fitting an additive model of our index of social isolationism as function of each of our primary independent variables while also controlling for the same variables included in our profile models.
-Finally, we refit three models with the same specification but introduce an interactive term between each of our internet communication indicators, respectively, with our measure of urbanicity.
-This allows us to test whether the observed additive effects are stronger for those living outside cities.
-
-We have several primary independent variables including **human interaction**, **online to offline relationships**, **general social media use**, and **urbanicity**.
-We measured human interaction with a single item: Has the internet and phone applications increased your contact with the following groups of people (check yes to all that apply)?
-The response options were: 1) Family that lives nearby, 2) Family that lives far away, 3) Friends that live nearby, 4) Friends that live far away, 5) People you met on the internet that live nearby, and 6) People you met on the internet that live far away.
+We have several primary independent variables including human interaction, online to offline relationships, general social media use, and urbanicity.
+We measured human interaction with a single item: "Has the internet and phone applications increased your contact with the following groups of people (check yes to all that apply)?" The response options were: 1) Family that lives nearby, 2) Family that lives far away, 3) Friends that live nearby, 4) Friends that live far away, 5) People you met on the internet that live nearby, and 6) People you met on the internet that live far away.
 We simply counted the number of selected responses so the item ranged from 0 to 6, and then for the models that come later, we rescaled it to range from 0 through 1 maintaining the original intervals.
@@
 
-```{r}
-#| label: fig-ivs
-
-```
-
-The distributions of these ordinal independent variables are reflected in Figure [ivs]{.smallcaps}.
+The distributions of these ordinal independent variables are reflected in @fig-var-dist.
 Very few people claimed to never have increased their contact/connections with others through the internet.
@@
 Taken altogether, a large proportion of our respondents seem to using the internet to facilitate social relations.
+
+```{r}
+#| label: fig-var-dist
+#| fig-cap: "Primary Independent Variables Distributions"
+
+figure2a = ggplot(data = subset(china_isolation_data, !is.na(human_interaction_cat)), aes(x = human_interaction_cat)) +
+  geom_bar(aes(y = (..count..)/sum(..count..))) +
+  scale_y_continuous(labels=scales::percent) +
+  labs(x = "Human Interaction", y = "Percent") +
+  coord_flip() +
+  theme(panel.border = element_rect(color = "black",fill = NA, size = 1))
+
+figure2b = ggplot(data = subset(china_isolation_data, !is.na(online_offline_cat)), aes(x = online_offline_cat)) +
+  geom_bar(aes(y = (..count..)/sum(..count..))) +
+  scale_y_continuous(labels=scales::percent) +
+  labs(x = "Online to Offline Relationships", y = "Percent") +
+  coord_flip() +
+  theme(panel.border = element_rect(color = "black",fill = NA, size = 1))
+
+grid.arrange(figure2a, figure2b)
+```
 
@@
 Each was recoded so that higher values represented more social media use, rescaled to range from 0 through 1, added together, and then again, rescaled to range from 0 through 1 maintaining all original intervals.
-The distribution of this index is presented in Figure \ref{genSM}.
+The distribution of this index is presented in @fig-sm-use-dist.
 The distribution is relatively normal and tightly centered around the mean 0.63 with a standard deviation of 0.17, but there is a left skew suggesting that a portion of the population is not that social media active, but clearly the bulk of the population are.
@@
 ```{r}
-#| label: fig-genSM
+#| label: fig-sm-use-dist
+#| fig-cap: General Social Media Use Distribution
 
-figure1 = ggplot(china_isolation_data, aes(x=isolation)) + 
-  geom_histogram(aes(y=..density..), colour="black", fill="seashell", size=1)+
+figure3 = ggplot(data = subset(china_isolation_data, !is.na(gen_social_med)), aes(x=gen_social_med)) + 
+  geom_histogram(aes(y=..density..), colour="black", fill="seashell") +
   geom_density(alpha=.2, fill="#FF6666") +   
-  xlab("Social Isolationism") +
+  xlab("Social Media Use") +
   ylab("Density")  +
-  theme(panel.border = element_rect(color = "black",fill = NA, size = 1))
-figure1
+  theme(panel.border = element_rect(color = "black",fill = NA))
+figure3
 ```
@@
 For the purpose of the models, we rescaled this item to range from 0 through 1 maintaining the original intervals.
-The distribution is reflected in Figure [urban]{.smallcaps}.
-Given the rural to urban Chinese migration since the founding of the People's Republic \citep{xia.2019}, it is not surprising to see that nearly 45% of those in our sample live in cities, 7% in suburbs, and about 27% in mid-sized cities.
+The distribution is reflected in @fig-urban-dist.
+Given the rural to urban Chinese migration since the founding of the People's Republic [@xia1995], it is not surprising to see that nearly 45% of those in our sample live in cities, 7% in suburbs, and about 27% in mid-sized cities.
 About 16% say they live in small cities and only about 5% say they live in villages.
+
+```{r}
+#| label: fig-urban-dist
+#| fig-cap: "Urbanicity Distribution"
+
+figure4 = ggplot(data = subset(china_isolation_data, !is.na(urbanicity_cat)), aes(x = urbanicity_cat)) +
+  geom_bar(aes(y = (..count..)/sum(..count..))) +
+  scale_y_continuous(labels=scales::percent) +
+  labs(x = "Urbanicity", y = "Percent") +
+  coord_flip() +
+  theme(panel.border = element_rect(color = "black",fill = NA, size = 1))
+
+figure4
+```
 
@@
 
-The results of our profile models are presented in Table [profile]{.smallcaps}.
+```{r}
+#| label: tbl-profile-models
+#| tbl-cap: "Modeling Profiles of Digital Communication"
+
+mod1_ord = polr(human_interaction_cat ~ ses + female + CCP_member + age, data = china_isolation_data)
+mod2_ord = polr(online_offline_cat ~ ses + female + CCP_member + age, data = china_isolation_data)
+mod3 = lm(gen_social_med ~ ses + female + CCP_member + age, data = china_isolation_data)
+
+models <- list(
+  "Human Interaction" = mod1_ord,
+  "Online/Offline Interaction" = mod2_ord,
+  "General Social Media" = mod3
+)
+
+gof.included <- list(
+  list("raw" = "nobs", "clean" = "N", "fmt" = "%i"),
+  list("raw" = "r2.nagelkerke", "clean" = "Pseudo R2", "fmt" = "%.2f"),
+  list("raw" = "r.squared", "clean" = "R2", "fmt" = "%.2f"))
+
+n <- "Human Interaction and Offline/Online Relationships estimates are derived from ordered logit and General Social Media from ordinary least squares."
+
+modelsummary(models, 
+             coef_omit = ".*Connect|.*Intercept|.*No|.*Yes",
+             coef_rename = c("ses" = "SES",
+                             "female" = "Female",
+                             "CCP_member" = "CCP Member",
+                             "age" = "Age"),
+             fmt=2,
+             stars=c("*" = 0.05),
+             output="kableExtra",
+             gof_map = gof.included) %>% 
+  footnote(general = n, threeparttable = TRUE)
+
+#gof_omit = "R2 Adj|AIC|BIC|Log.Lik.|RMSE" 
+```
+
+The results of our profile models are presented in @tbl-profile-models.
 When it comes to SES, the relationship across all three of our internet communication is consistent.
@@
 
-The results of our models of social isolation are presented in Table Figure [interact]{.smallcaps}.
+```{r}
+#| label: tbl-social-isolation-models
+#| tbl-cap: "Modeling Social Isolation"
+
+mod4 = lm(isolation ~ human_interaction + online_offline + gen_social_med + urbanicity + ses + female + CCP_member + age, data = china_isolation_data)
+
+mod5 = lm(isolation ~ human_interaction*urbanicity + online_offline + gen_social_med + ses + female + CCP_member + age, data = china_isolation_data)
+
+mod6 = lm(isolation ~ online_offline*urbanicity + human_interaction + gen_social_med + ses + female + CCP_member + age, data = china_isolation_data)
+
+mod7 = lm(isolation ~ gen_social_med*urbanicity + human_interaction + online_offline + ses + female + CCP_member + age, data = china_isolation_data)
+
+n <- "Estimates are derived using ordinary least squares"
+
+mods <- list(mod4, mod5, mod6, mod7)
+
+modelsummary(mods, 
+             coef_omit = ".*Connect|.*Intercept|.*No|.*Yes",
+             coef_rename = c("ses" = "SES",
+                             "female" = "Female",
+                             "CCP_member" = "CCP Member",
+                             "age" = "Age",
+                             "urbanicity" = "Urbanicity",
+                             "online_offline" = "Online-Offline",
+                             "human_interaction" = "Human Interaction",
+                             "gen_social_med" = "Social Media",
+                             "human_interaction:urbanicity" = 
+                               "Human Interaction*Urbanicity",
+                             "online_offline:urbanicity" =
+                               "Online-Offline*Urbanicity",
+                             "gen_social_med:urbanicity" = 
+                               "Social Media*Urbanicity"),
+             fmt=2,
+             stars=c("*" = 0.05),
+             output="kableExtra",
+             gof_map = gof.included) %>% 
+  footnote(general = n, threeparttable = TRUE)
+```
+
+The results of our models of social isolation are presented in @tbl-social-isolation-models.
 The additive estimates in model (1) provide mixed results regarding whether internet communication is a positive force in deterring social isolation.
@@
 
-%NOTE: Andrew, do you want to speculate here about why online to offline is positively related - desparate peole?.
+Models (2) - (4) in Table 2 include each of the interactions between our three internet communication measures and urbanicity.
+The consistent result across the interactions is that the relationships are dulled for those living in more rural areas.
+The interaction between digital humna interaction and urbanicity is statistically significant ($p < 0.01$), as is that between the move from online to offline relationships and urbanicity ($p < 0.001$), and that between general social media use and urbanicity only slightly misses the arbitrary $0.05$ threshold ($p = 0.07$).
+The interactions are most easily interpreted graphically (see @fig-social-isolation-interactions).
 
-Models (2) - (4) in Table [interact]{.smallcaps} include each of the interactions between our three internet communication measures and urbanicity.
-The consistent result across the interactions is that the relationships are dulled for those living in more rural areas.
-The interaction between digital human interaction and urbanicity is statistically significant (p \< 0.01), as is that between the move from online to offline relationships and urbanicity (p \< 0.001), and that between general social media use and urbanicity only slightly misses the arbitrary 0.05 threshold (p = 0.07).
-The interactions are most easily interpreted graphically (see Figure [intergraph]{.smallcaps}).
+```{r}
+#| label: fig-social-isolation-interactions
+#| fig-cap: "Modeling Social Isolation: Interaction Results"
+#| fig-width: 8
+
+a <- plot_model(mod5, type = "pred", title = "", terms = c("human_interaction", "urbanicity")
+               , legend.title = "Urbanicity") +
+  scale_color_discrete(labels = c("Village", "Small City", "Mid-sized City", "Suburb", "Big City")) +
+  ylab("") +
+  xlab("Digital Human Interaction") +
+  theme(panel.border = element_rect(color = "black",fill = NA, size = 1))
+
+b <- plot_model(mod6, type = "pred", title = "", terms = c("online_offline", "urbanicity")
+               , legend.title = "Urbanicity") +
+  scale_color_discrete(labels = c("Village", "Small City", "Mid-sized City", "Suburb", "Big City")) +
+  ylab("") +
+  xlab("Online to Offline Relationships") +
+  theme(panel.border = element_rect(color = "black",fill = NA, size = 1))
+
+c <- plot_model(mod7, type = "pred", title = "", terms = c("gen_social_med", "urbanicity")
+               , legend.title = "Urbanicity") +
+  scale_color_discrete(labels = c("Village", "Small City", "Mid-sized City", "Suburb", "Big City")) +
+  ylab("") +
+  xlab("Social Media Use") +
+  theme(panel.border = element_rect(color = "black",fill = NA, size = 1))
+
+grobs <- list(a, b, c)
+
+grid.arrange(grobs=grobs, ncol=2, left="Feelings of social isolation")
+```
 
@@
 
-The results from the interaction between online to offline relationships and urbanicity are displayed in the graph in the upper right hand corner of Figure [intergraph]{.smallcaps}.
+The results from the interaction between online to offline relationships and urbanicity are displayed in the graph in the upper right hand corner of Figure 5.
 Again, here, the main effects run in the opposite direction than those of digital human interaction.

### 2023-06-19 Social Isolation in China.qmd
Wrote a bunch

@@
 
-"For example, when social media is used to facilitate offline relationships, to communicate, or to make new friends, it reduces feelings of loneliness \[140, 141\].
-In contrast, when social media is used to compensate for poor social skills by replacing offline interactions with online interactions, it significantly increases loneliness \[142,143,144\]." [@lim2020]
-
 ## Introduction
@@
 Research has suggested that urban living can actually lead to feelings of isolation.
+
+## Literature Review and Theory
+
+The literature on the relationship between social media usage and attitudes about the self
+
+Most of the literature finds a negative relationship between
+
+Initially
+
+More recently, there has been a great deal of attention paid to the idea that there is some sort of connection between well-being and social media use, with most critics and significant scholarly research
+
+While the current Different studies have come to different conclusions regarding which direction the causal relationship flows; whether higher social media use causes more social isolation or whether the relationship is reversed.
+Martilla et al.
+propose a more complex causal model in that social media usage predicts loneliness, which then influences measures of social well-being [@marttila2021].
+A meta-review of
+
+At a more intermediate level, and perhaps one of the reasons for some of the empirical disagreement between authors, is that social media can have two possible effects.
+As Lim puts it, "...when social media is used to facilitate offline relationships, to communicate, or to make new friends, it reduces feelings of loneliness.
+In contrast, when social media is used to compensate for poor social skills by replacing offline interactions with online interactions, it significantly increases loneliness" [@lim2020].
+While
+
+Importantly, the proposed mechanisms f
+
+Almost all of the existing research on the subject takes U.S.
+citizens as its object of study, with an additional few studies on other Western developed countries.
+It seems quite likely that the cultural context can matter for social isolation.
+Studies have demonstrated that measures of social isolation can vary significantly across countries.
+Different starting points of social isolation seem reasonably likely to lead to differential effects of increased social media use.
+Additionally, while the basic mechanics of social media (sharing and consuming content of others), likely the internet environment .
+
+This study aims to understand how these complex dynamics interact in the non-Western setting of China. China is known for high/low level of social isolation.
+
+In our view, there are three key differences between the Chinese social media environment and that of the West that may influence the linkage between social media use and feelings of isolation - the government attempts to control the internet, the space for online subcultures, and the popularity of Chinese social media influencers.
+Many people are aware that the Chinese government censors politically sensitive content on online platforms.
+However, fewer are aware that the Chinese government spends as much if not more effort to clean up non-political but negative or distressing content on the Chinese internet, such as scams, instances of cyber bullying, disturbing videos, and vulgar content.
+This control impulse also extends content the government views as spiritually polluting, such as pornography, scantily dressed women, and other escapist content.
+
+Secondly, due to the government's perceived need to control online content, the number of available spaces online where users can freely interact is significantly more limited than on the Western internet.
+Due to this limitation, there are also fewer opportunities for niche subcultures to form.
+Most of the existing social media channels are either ones in which the user may connect directly people they know in real life (WeChat) or ones in which they view content of other, anonymous, users in which they rarely form a stable, ongoing relationship with (Xiaohongshu and TikTok).
+China does feature a program similar to Twitter (Weibo) that does lead to some unique subculture formation but has no analogous space to Reddit or other such spaces that are organized primarily according to user interest.
+
+Finally, China also has a highly robust online influencer culture.
+While social media influencers are a global phenomena, China has perhaps the most commercialized version of influencing.
+Social media influencers are developed by large agencies and work in an almost assembly-line fashion to promote products on livestreams or pitch sponsor products.
+In this influencer culture, less attention is paid to authenticity and personality and relatively more emphasis is placed on consumerism, brand promotion, and image [@tam2019; @wei2023].
+
+From a theoretical perspective, these three differences may lead to divergent findings regarding the relationship as compared to the West.
 

### 2023-06-21 Social Isolation in China.qmd
More text updated

--- 2023-06-15 Social Isolation in China.qmd
@@
 Research has suggested that urban living can actually lead to feelings of isolation.
+
+## Literature Review and Theory
+
+The existing literature on social isolation and social media use generally finds a negative relationship between the two.
+However, there are some remaining questions regarding whether this relationship remains significant in different cultural and regulatory environments.
+Based on the existing literature, we then develop some testable hypotheses regarding how the relationship between usage and isolation may vary in the context of China.
+The result of these hypotheses tests help to better understand the mechanism that links the two concepts.
+
+Initially, scholars imagined that social media would create more opportunities for users to create unique and fulfilling social relationships.
+The early theorizing about the possible benefits of social media hypothesized three important mechanisms by which social media could decrease loneliness.
+1) creating more opportunities for online to offline meetups and 2) helping to alleviate feelings of isolation for those who have difficulty making in-person social connections via joining an online communities, and 3) facilitating keeping in touch with family and friends [@ellison2007; @steinfield2008; @subrahmanyam2008].
+
+More recent studies on the subject have been significantly more critical of the impact of social media on feelings of isolation. In particular, many authors have linked problematic social media use to
+
+While most of the studies agree that the causal direction flows from social media use to feelings of isolation (though see xxx), there is disagreement among authors about the specific mechanisms and causal pathways through which this relationship exists.
+Martilla et al.
+propose a more complex causal model in that social media usage predicts loneliness, which then influences measures of social well-being [@marttila2021].
+Twenge et al.
+suggest that that while individual-level studies may not show a strong relationship between social media use and feelings of isolation, the technology may be supressing overall mean societal levels of social isolation via a generalized decrease in person to person meetups [@twenge2021].
+
+There have been a number of
+
+Most of the existing research on the subject focuses on Western highly developed societies, and this focus may limit variation on key independent variables given the similar social and institutional context in which users are embedded.
+
+To address this problem, this study aims to understand how these complex dynamics interact in the non-Western setting of China.
+Relatively little is known about China's level of social isolation, though anecdotal evidence suggests that it is on the rise.
+Twenge et al.'s study found that adolescent feelings of loneliness have generally been on the rise in comparable East Asian countries [@twenge2021].
+News reports have highlighted the increasing number of people who consider themselves to be online outcasts or losers (*diaosi*) [@nan2013; @szablewicz2014; @chinas2016].
+These feelings of social isolation and loneliness have developed in the context of one of the most rapid periods of urbanization in human history.
+Hundreds of millions of people have shifted from rural subsistence farming to participating in an urban market economy.
+The existing literature finds that urbanicity is an important factor in levels and mechanisms for social isolation; many studies of Western societies have found that rural residents, while having stronger familial bonds, also can more easily experience social isolation without those bonds [@kaye2017; @koning2017; @henning-smith2018].
+
+Interacting with these societal trends is a social media space that is highly controlled.
+Many people are aware that the Chinese government heavily censors politically sensitive content on online platforms.
+However, fewer are aware that the Chinese government spends as much if not more effort to clean up non-political but negative or distressing content on the Chinese internet, such as scams, instances of cyber bullying, disturbing videos, and vulgar content [@wang2020].
+This control impulse also extends content the government views as spiritually polluting, such as pornography, scantily dressed women, and other escapist content.
+While the Chinese government and online platforms are limited in their ability to completely stamp out such content, the default is that such content is actively restricted, while US platforms tent to take a more pro-speech regulatory position [@liu2022].
+If one of the main mechanisms through which social media promotes social isolation occurs is exposure to negative content, then this online environment should lead to a weaker relationship between social media use and isolation.
+
+On the other hand, China also has a highly robust online influencer culture.
+While social media influencers are a global phenomena, China has perhaps the most commercialized version of influencing.
+Social media influencers are developed by large agencies and work in an almost assembly-line fashion to promote products on livestreams or pitch sponsor products.
+In this influencer culture, less attention is paid to authenticity and personality and relatively more emphasis is placed on consumerism, brand promotion, and image \[\@tam2019; \@wei2023\].
+Given that previous research has suggested one of the main channels through which social media creates feelings of isolation is negative personal comparisons with online content (so-called "FOMO" - fear of missing out), heavy social media use may increase the strength of the relationship between social media use and
 
@@
 ### Residual Analysis
+
+```{r}
+#| label: extra-text
+#| include: false
+
+#Secondly, due to the government's perceived need to control online content, the number of available spaces online where users can freely interact is significantly more limited than on the Western internet.
+Due to this limitation, there are also fewer opportunities for niche subcultures to form.
+Most of the existing social media channels are either ones in which the user may connect directly people they know in real life (WeChat) or ones in which they view content of other, anonymous, users in which they rarely form a stable, ongoing relationship with (Xiaohongshu and TikTok).
+China does feature a program similar to Twitter (Weibo) that does lead to some unique subculture formation but has no analogous space to Reddit or other such spaces that are organized primarily according to user interest.
+
+#Finally, China also has a highly robust online influencer culture.
+While social media influencers are a global phenomena, China has perhaps the most commercialized version of influencing.
+Social media influencers are developed by large agencies and work in an almost assembly-line fashion to promote products on livestreams or pitch sponsor products.
+In this influencer culture, less attention is paid to authenticity and personality and relatively more emphasis is placed on consumerism, brand promotion, and image [@tam2019; @wei2023].
+```

### 2023-06-21 Social Isolation in China.qmd
More updated text

@@
 
-More recent studies on the subject have been significantly more critical of the impact of social media on feelings of isolation. In particular, many authors have linked problematic social media use to
+More recent studies on the subject have been significantly more mixed regarding the impact of social media on feelings of isolation.
+In particular, many authors have linked problematic social media use to
+
+Primack et al. found a negative relationship between social media use and social isolation in youth in a representative sample [@primack2017].
+
+Somewhat contrary to the previous findings, Hajek and König find that the relationship between social media and social isolation is reversed for their sample of those over 40 in Germany, suggesting the impact of social media may be influenced by age [@hajek2019].
 
@@
 
-There have been a number of
+More recent research has begun to investigate what is the primary mechanism by which social media influences feelings of social isolation.
 
 Most of the existing research on the subject focuses on Western highly developed societies, and this focus may limit variation on key independent variables given the similar social and institutional context in which users are embedded.
-
 To address this problem, this study aims to understand how these complex dynamics interact in the non-Western setting of China.
@@
 News reports have highlighted the increasing number of people who consider themselves to be online outcasts or losers (*diaosi*) [@nan2013; @szablewicz2014; @chinas2016].
-These feelings of social isolation and loneliness have developed in the context of one of the most rapid periods of urbanization in human history.
-Hundreds of millions of people have shifted from rural subsistence farming to participating in an urban market economy.
-The existing literature finds that urbanicity is an important factor in levels and mechanisms for social isolation; many studies of Western societies have found that rural residents, while having stronger familial bonds, also can more easily experience social isolation without those bonds [@kaye2017; @koning2017; @henning-smith2018].
+We do not aim to make a direct comparison between China and Western countries but rather highlight the way in which China's unique context helps highlight how important contextual factors are in the key variable relationships.
 
-Interacting with these societal trends is a social media space that is highly controlled.
+The most important contextual factor in China is that social media space that is highly controlled online environment.
 Many people are aware that the Chinese government heavily censors politically sensitive content on online platforms.
@@
 Social media influencers are developed by large agencies and work in an almost assembly-line fashion to promote products on livestreams or pitch sponsor products.
-In this influencer culture, less attention is paid to authenticity and personality and relatively more emphasis is placed on consumerism, brand promotion, and image \[\@tam2019; \@wei2023\].
-Given that previous research has suggested one of the main channels through which social media creates feelings of isolation is negative personal comparisons with online content (so-called "FOMO" - fear of missing out), heavy social media use may increase the strength of the relationship between social media use and
+In this influencer culture, less attention is paid to authenticity and personality and relatively more emphasis is placed on consumerism, brand promotion, and image [@tam2019; @wei2023].
+Given that previous research has suggested one of the main channels through which social media creates feelings of isolation is negative personal comparisons with online content (so-called "FOMO" - fear of missing out), heavy social media use may increase the strength of the relationship between social media use and social isolation.
+
+The nexus of social isolation and social media use has developed in the context of one of the most rapid periods of urbanization in human history.
+Hundreds of millions of people have shifted from rural subsistence farming to participating in an urban market economy.
+The existing literature finds that urbanicity is an important factor in levels and mechanisms for social isolation; many studies of Western societies have found that rural residents, while having stronger familial bonds, also can more easily experience social isolation without those bonds [@kaye2017; @koning2017; @henning-smith2018].
+In China, less is known about the differential effects of the urban rural divide on feelings of social isolation but the research that does exist suggests that urban environments can be especially isolating, particularly for rural to urban migrants particularly due to lack of access to traditional support systems and familial connections [@li2017].
+
+Given the existing literature and the context of China, this leads to a series of testable hypotheses.
+
+-   **H1a:** social media use should have a weak connection to social isolation due to strengthened government control over online content
+
+-   **H1b:** social media use should have a strong connection to social isolation due to the dominance of influencer culture in China
+
+-   **H2:** those who are able to use social media to
+
+-   **H3:** the urban/rural divide will produce differential impacts in the above hypotheses on the relationship between social media use and social isolation
 

### 2023-06-22 Social Isolation in China.qmd
conference draft done

@@
 We know very little about this phenomenon in China.
-China presents an interesting case because the internet is bifurcated to some degree -- there is the Chinese internet and the outside internet available via VPNs.
-Being connected to the outside world may lessen feelings of isolation, or it may increase these feelings because digital exposure to a world is much larger than that in people's immediate environment without the ability to have in-person connection to may make one feel isolated.
-Interestingly, and somewhat ironically though, it may also matter, too, whether someone lives in a city.
-Research has suggested that urban living can actually lead to feelings of isolation.
+China presents an interesting case because the institutional structures, level of development and the cultural context are all quite different than the areas studied in most existing studies.
+This allows us to test whether such features moderate or exacerbate the relationship between social media use and social isolation.
+To fully test this theory, we employ a large survey of Chinese internet users and test a variety of regression specifications.
+The main result is that social media use is robustly negatively related to social isolation, though the nature of this relationship changes depending on the urbanicity of the respondent - being in a rural area amplifies this relationship.
 
@@
 Based on the existing literature, we then develop some testable hypotheses regarding how the relationship between usage and isolation may vary in the context of China.
-The result of these hypotheses tests help to better understand the mechanism that links the two concepts.
+The result of these hypotheses tests will help to better understand the mechanism that links the two variables.
 
@@
 
-More recent studies on the subject have been significantly more mixed regarding the impact of social media on feelings of isolation.
-In particular, many authors have linked problematic social media use to
+More recent studies on the subject have found significantly more mixed and often negative evidence regarding the impact of social media on feelings of isolation.
+Primack et al.
+found a negative relationship between social media use and social isolation in youth in a representative sample [@primack2017].
+A meta-review of the literature on adolescent social media usage notes that while the effect size is often small the relationship in most studies is negative [@valkenburg2022].
+There are relatively fewer studies that consider all ages.
+However, those that have been conducted also generally find a negative (if modest) relationship [@appel2020].
+More recent research has suggested that the effect of social media on measures like social isolation may be highly heterogeneous across individuals, a finding that would help reconcile some of the discrepancies in the literature [@beyens2020; @ostic2021].
 
-Primack et al. found a negative relationship between social media use and social isolation in youth in a representative sample [@primack2017].
-
-Somewhat contrary to the previous findings, Hajek and König find that the relationship between social media and social isolation is reversed for their sample of those over 40 in Germany, suggesting the impact of social media may be influenced by age [@hajek2019].
-
-While most of the studies agree that the causal direction flows from social media use to feelings of isolation (though see xxx), there is disagreement among authors about the specific mechanisms and causal pathways through which this relationship exists.
-Martilla et al.
-propose a more complex causal model in that social media usage predicts loneliness, which then influences measures of social well-being [@marttila2021].
-Twenge et al.
-suggest that that while individual-level studies may not show a strong relationship between social media use and feelings of isolation, the technology may be supressing overall mean societal levels of social isolation via a generalized decrease in person to person meetups [@twenge2021].
-
-More recent research has begun to investigate what is the primary mechanism by which social media influences feelings of social isolation.
+While most of the studies agree that the causal direction flows from social media use to feelings of isolation (though see [@nowland2018; @kim2017]), there is disagreement among authors about the specific mechanisms and causal pathways through which this relationship exists.
+One set of mechanisms find that the social media itself that is the problem.
+Cyberbullying, or more generally, repeated and aggressive online attacks against users has been systematically linked to feelings of social isolation [@ademiluyi2022].
+Upward comparisons of others and the weak nature of online connections has been found to generate social anxiety and social isolation [@alabri2022; @büttner2022].
+Another set of mechanisms primarily concern themselves with the physical changes that social media causes.
+Social media use has been shown to displace face to face activity, which leads to greater social isolation [@larson2018].
+Heavy social media use also decreases hours of sleep, leading to greater feelings of anxiety and more social isolation [@twenge2017].
+The current research suggests that which of these mechanisms is dominant depends on the age/demographic group in question and the societal context [@twenge2019].
 
@@
 To address this problem, this study aims to understand how these complex dynamics interact in the non-Western setting of China.
-Relatively little is known about China's level of social isolation, though anecdotal evidence suggests that it is on the rise.
+Relatively little is known about China's level of social isolation, though what evidence that does exist suggests that it is on the rise.
 Twenge et al.'s study found that adolescent feelings of loneliness have generally been on the rise in comparable East Asian countries [@twenge2021].
 News reports have highlighted the increasing number of people who consider themselves to be online outcasts or losers (*diaosi*) [@nan2013; @szablewicz2014; @chinas2016].
-We do not aim to make a direct comparison between China and Western countries but rather highlight the way in which China's unique context helps highlight how important contextual factors are in the key variable relationships.
+We do not aim to make a direct comparison between China and Western countries but rather highlight the way in which China's unique context helps shed light on which contextual factors matter in understanding the linkage between the two variables.
 
-The most important contextual factor in China is that social media space that is highly controlled online environment.
+The most important of these contextual factor in China is that social media space that is highly controlled online environment.
 Many people are aware that the Chinese government heavily censors politically sensitive content on online platforms.
@@
 This control impulse also extends content the government views as spiritually polluting, such as pornography, scantily dressed women, and other escapist content.
-While the Chinese government and online platforms are limited in their ability to completely stamp out such content, the default is that such content is actively restricted, while US platforms tent to take a more pro-speech regulatory position [@liu2022].
+While the Chinese government and online platforms are not 100 per cent effective in their ability to completely stamp out such content, the default is that such content is actively restricted, while US platforms tent to take a more pro-speech regulatory position [@liu2022].
 If one of the main mechanisms through which social media promotes social isolation occurs is exposure to negative content, then this online environment should lead to a weaker relationship between social media use and isolation.
+Suggestive of this is a a study by Liu and Liu that finds those who consumed more commercialized and sensationalized media reported more trauma during the first COVID-19 in China than those who followed government sources [@liu2020].
 
@@
 
-The nexus of social isolation and social media use has developed in the context of one of the most rapid periods of urbanization in human history.
+Aditionally, China's social media environment is relatively unique in that the dominant messaging platform is also the largest social media app (WeChat).
+Users can use it simply to chat with family and friends, they can use it to post photos and other content about their life in a feed that works similarly to Facebook, or they can browse videos of others in a method similar to Tiktok.
+Previous research has indicated that while, on the whole, social media increases social isolation, for users that primarily use it to contact friends and family, its use can counteract the negative effects [@hajek2019; @lim2020].
+Given the ubiquity of WeChat in China, we expect to find similar results.
+
+Finally, the nexus of social isolation and social media use in China has played out in the context of one of the most rapid periods of urbanization in human history.
 Hundreds of millions of people have shifted from rural subsistence farming to participating in an urban market economy.
@@
 
--   **H1a:** social media use should have a weak connection to social isolation due to strengthened government control over online content
+-   **H1a:** social media use should have a weak or possibly positive connection to social isolation due to strengthened government control over online content
 
--   **H1b:** social media use should have a strong connection to social isolation due to the dominance of influencer culture in China
+-   **H1b:** social media use should have a negative connection to social isolation due to the dominance of influencer culture in China
 
--   **H2:** those who are able to use social media to
+-   **H2:** those who are able to use social media to make new friends will have lower social isolation scores than those who do not
 
@@
 
+In terms of our original hypotheses, we find support for the idea that China's social media environment is not particularly unique with respect to generating feelings of social isolation (**H1b**).
+Whether or not this is due to the influencer culture or other factors, we cannot say with our data but it at least does suggest that greater content regulation is not likely to moderate the amount of isolation that social media produces.
+We also find, as has been found in other studies, that users who use the internet to create new connections are less likely to feel isolated (**H2**).
+However, this does not seem to extend to those that use the internet to facilitate offline meetups.
+Finally, we find that the impact of the internet and social media vary significantly according to the level of urbanicity (**H3**).
+These findings are generally in line with previous research on the subject, suggesting that the mechanisms that generate feelings of social isolation are universal and not so sensitive to different social and governing contexts.
+
 ## Conclusion
@@
 Our contribution here is that we look at some well-established theoretical arguments in a context outside that of where most of the research centered on these type questions has examined.
-By no means, have we offered a definitive answer to whether there are contextual differences.
-We have, though, offered a good starting point to further examine the relationship between internet communication and social isolationism outside Western contexts.
+While our study is far from the last word on the subject, these results suggest that the mechanisms that link social media use and social isolation are relatively context-insensitive.
 

### 2023-06-27 presentations/Responsible Citizens presentation/Responsible Citizens 2023 Presentation.Rmd
Final presentation update

---
title: "Connected or Disconnected? Social Media and Social Isolationism in China"
author: "Jason Gainous and Andrew W. MacDonald"
date: "June 27th, 2023"
output: 
  learnr::tutorial:
    toc_depth: 3
bibliography: www/references.bib
nocite: '@*'
csl: www/apsa.csl
runtime: shiny_prerendered
---

```{r setup, include=FALSE, context="setup"}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)

library(ggplot2)
library(broom)
library(dplyr)
library(modelsummary)
library(gridExtra)
library(knitr)
library(kableExtra)
library(ggthemes)
library(ggdag)
library(dagitty)
library(sjPlot)
library(learnr)
library(MASS)
library(DescTools)
library(gt)

theme_set(theme_light())

gof.included.short <- list()

gof.included.full <- list(
  list("raw" = "nobs", "clean" = "N", "fmt" = "%i"),
  list("raw" = "r2.nagelkerke", "clean" = "Pseudo R2", "fmt" = "%.2f"),
  list("raw" = "r.squared", "clean" = "R2", "fmt" = "%.2f"))

replace_estimates <- function(mod_list) {

  for(model in 1:length(mod_list)) {
    for(obs in 1:nrow(mod_list[[model]]$tidy)) {
      mod_list[[model]]$tidy$estimate[obs] <- case_when(mod_list[[model]]$tidy$p.value[obs] > 0.05 ~ "—",
                                mod_list[[model]]$tidy$estimate[obs] >= 0 ~ "▲",
                                mod_list[[model]]$tidy$estimate[obs] < 0 ~ "▼")
    }
  }

  return(mod_list)
}

load("www/china_isolation_data.RData")
```

## Where to find this research

```{r qrcodeintro, out.width = "300px", fig.cap="QR code for this presentation"}
knitr::include_graphics("www/qrcode.png")
```

Presentation website: [bit.ly/rc2023presentation](https://bit.ly/rc2023presentation)

Conference paper: [bit.ly/rc2023paper](https://bit.ly/rc2023paper)

Github repository: [bit.ly/rc2023github](https://bit.ly/rc2023github)

## Why this project?

```{r prop1, out.width = "100%", fig.cap="Increase in social isolation^[Image credit: https://www.mdedge.com/psychiatry/article/133020/practice-management/social-media-may-be-isolating-young-adults]"}
knitr::include_graphics("www/socialisolationinc.png")
```

### Main problem(s) with this literature

**1. What is the direction of the relationship?**

```{r direction1, out.width = "100%", fig.cap="Plausible relationship"}
standard_dag <- dagify(Iso ~ SM,
  SM ~ a + b,
  exposure = "SM",
  outcome = "Iso"
)

standard_dag %>%
  node_parents("SM") %>%
  ggplot(aes(x = x, y = y, 
             xend = xend, yend = yend, color = parent)) +
  geom_dag_point(size=20) +
  geom_dag_text(col = "white") +
  geom_dag_edges_arc() +
  theme_dag(legend.position = "none") +
  scale_color_hue(breaks = c("parent", "child")) #  ignores NA in legend
```

**2. What is the causal direction?**

```{r causal, out.width = "100%", fig.cap="Reversed causation"}
reverse_dag <- dagify(SM ~ Iso,
  Iso ~ a + b,
  exposure = "Iso",
  outcome = "SM"
)

reverse_dag %>%
  node_parents("Iso") %>%
  ggplot(aes(x = x, y = y, 
             xend = xend, yend = yend, color = parent)) +
  geom_dag_point(size=20) +
  geom_dag_text(col = "white") +
  geom_dag_edges_arc() +
  theme_dag(legend.position = "none") +
  scale_color_hue(breaks = c("parent", "child")) #  ignores NA in legend
```

**3. What are the mechanisms?**

```{r mechanisms, out.width = "100%", fig.cap="Mechanism confusion"}
alt_dag <- dagify(Iso ~ a + SM,
  a ~ b + SM,
  exposure = "SM",
  outcome = "Iso"
)

alt_dag %>%
  node_parents("SM") %>%
  ggplot(aes(x = x, y = y, 
             xend = xend, yend = yend, color = parent)) +
  geom_dag_point(size=20) +
  geom_dag_text(col = "white") +
  geom_dag_edges() +
  theme_dag(legend.position = "none") +
  scale_color_hue(breaks = c("parent", "child")) #  ignores NA in legen
```

```{r mechanismlist}
dt_lb <- data.frame(
  col1 = c("<b>Direct</b>", 
           "&emsp;&emsp;&emsp;&emsp;Cyberbullying",
           "&emsp;&emsp;&emsp;&emsp;Upward comparisons (\"FOMO\")",
           "&emsp;&emsp;&emsp;&emsp;Opportunity to build social capital",
           "<b>Indirect</b>", 
           "&emsp;&emsp;&emsp;&emsp;Less sleep", 
           "&emsp;&emsp;&emsp;&emsp;More bluelight", 
           "&emsp;&emsp;&emsp;&emsp;Replaces in-person interaction", 
           "<b>Reverse</b>", 
           "&emsp;&emsp;&emsp;&emsp;Attention seeking", 
           "&emsp;&emsp;&emsp;&emsp;Compensation by making friends"))

dt_lb %>%
  kbl(booktabs=T, 
      caption="<span style='font-size:16px;color:black'><b>Mechanism list</b></span>", 
      col.names=NULL, 
      escape=FALSE) %>% 
  kable_styling(position="center", )
```

### How can the case of China help solve this problem?

**New context!**

**1. Government control**

```{r china1a, out.width = "100%", fig.cap="Banned content example A^[Image credit: https://edition.cnn.com/2016/08/31/asia/china-banned-on-tv-censorship/index.html]"}

knitr::include_graphics("www/banned1.webp")
```

```{r china1b, out.width = "100%", fig.cap="Banned content example B^[Image credit: https://edition.cnn.com/2016/08/31/asia/china-banned-on-tv-censorship/index.html]"}
knitr::include_graphics("www/banned2.webp")
```

```{r china1c, out.width = "100%", fig.cap="Banned content example C^[Image credit: https://edition.cnn.com/2016/08/31/asia/china-banned-on-tv-censorship/index.html]"}
knitr::include_graphics("www/banned3.webp")
```

```{r china1d, out.width = "100%", fig.cap="Banned content example D^[Image credit: https://edition.cnn.com/2016/08/31/asia/china-banned-on-tv-censorship/index.html]"}
knitr::include_graphics("www/banned4.webp")
```

```{r china1e, out.width = "100%", fig.cap="Banned content example E^[Image credit: https://www.theguardian.com/news/2021/jul/15/china-video-game-censorship-tencent-netease-blizzard]"}

knitr::include_graphics("www/banned5.webp")
```

**2. Influencer culture**

```{r china2a, out.width = "100%", fig.cap="Rise of influencer culture^[Image credit: https://www.statista.com/chart/27133/influencer-marketing-reach-by-country/]"}

knitr::include_graphics("www/influencerchart.jpeg")
```

```{r china2b, out.width = "100%", fig.cap="Influencer factory^[Image credit: https://www.goldthread2.com/culture/inside-chinese-social-media-influencer-factory/article/3000868]"}

knitr::include_graphics("www/influencer.webp")
```

**3. WeChat**

```{r china3, out.width = "100%", fig.cap="Wechat functions^[Image credit: https://www.fdichina.com/services/wechat-business-account/]"}

knitr::include_graphics("www/wechat.jpeg")
```

**4. Urban/rural divide**

```{r china4a, out.width = "100%", fig.cap="Urban-rural divide^[Image credit: http://realchinacharts.com]"}

knitr::include_graphics("www/urbanrural.png")
```

```{r china4b, out.width = "100%", fig.cap="Rural poverty^[Image credit: https://www.scmp.com/news/china/society/article/2089654/china-rural-rich-get-richer-and-poor-get-poorer?module=perpetual_scroll_0&pgtype=article&campaign=2089654]"}

knitr::include_graphics("www/rural.png")
```

### Hypotheses

- $\mathbf{H1_a}: social\:media \rightarrow social\:isolation\downarrow$
  + *Reason*: Government control of internet
- $\mathbf{H1_b}: social\:media \rightarrow social\:isolation\uparrow$
  + *Reason*: Influencer culture
- $\mathbf{H2}: social\:media\:to\:make\:friends \rightarrow social\:isolation\downarrow$
  + *Reason*: integration of social media and messaging in China
- $\mathbf{H3}: urbanicity \rightarrow interactive\:effect$ 
  + *Reason*: Radically different social settings in China

## Data and descriptives

```{r keyvars}
dt_lb <- data.frame(
  col1 = c("<b>Response variable</b>", 
           "&emsp;&emsp;&emsp;&emsp;Social isolation", 
           "<b>Predictor variables</b>", 
           "&emsp;&emsp;&emsp;&emsp;Human interaction", 
           "&emsp;&emsp;&emsp;&emsp;Online-offline interaction", 
           "&emsp;&emsp;&emsp;&emsp;Social media use", 
           "&emsp;&emsp;&emsp;&emsp;Urbanicity", 
           "<b>Control variables</b>", 
           "&emsp;&emsp;&emsp;&emsp;SES", 
           "&emsp;&emsp;&emsp;&emsp;Female", 
           "&emsp;&emsp;&emsp;&emsp;CCP member", 
           "&emsp;&emsp;&emsp;&emsp;Age"))

dt_lb %>%
  kbl(booktabs=T, 
      caption="<span style='font-size:16px;color:black'><b>Key variables</b></span>", 
      col.names=NULL, 
      escape=FALSE) %>% 
  kable_styling(position="center")
```

### Social islation

```{r socialisolationdist, out.width = "100%"}
figure1 = ggplot(china_isolation_data, aes(x=isolation)) + 
  geom_histogram(aes(y=..density..), colour="black", fill="seashell")+
  geom_density(alpha=.2, fill="#FF6666") +
  xlab("Social Isolationism") +
  ylab("Density") +
  theme(panel.border = element_rect(color = "black",fill = NA))
figure1
```

### Human interaction

```{r humaninteractiondist, out.width = "100%"}
figure2a = ggplot(data = subset(china_isolation_data, !is.na(human_interaction_cat)), aes(x = human_interaction_cat)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill="blue4") +
  scale_y_continuous(labels=scales::percent) +
  labs(x=NULL, y = "Percent") 
figure2a
```

### Online-offline relationships

```{r onlineofflinedist, out.width = "100%"}
figure2b = ggplot(data = subset(china_isolation_data, !is.na(online_offline_cat)), aes(x = online_offline_cat)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill="blue4") +
  scale_y_continuous(labels=scales::percent) +
  labs(x=NULL, y = "Percent") 
figure2b
```

### Social media use

```{r socialmediausedist, out.width = "100%"}
figure3 = ggplot(data = subset(china_isolation_data, !is.na(gen_social_med)), aes(x=gen_social_med)) + 
  geom_histogram(aes(y=..density..), colour="black", fill="seashell") +
  geom_density(alpha=.2, fill="#FF6666") +   
  xlab("Social Media Use") +
  ylab("Density")  +
  theme(panel.border = element_rect(color = "black",fill = NA))
figure3
```

### Urbanicity

```{r urbanicitydist, out.width = "100%"}
figure4 = ggplot(data = subset(china_isolation_data, !is.na(urbanicity_cat)), aes(x = urbanicity_cat)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill="blue4") +
  scale_y_continuous(labels=scales::percent) +
  labs(x=NULL, y = "Percent")
figure4
```

## Model test

### Profile of users

```{r profileusersshort, out.width = "100%"}
selectInput(
  'model1', label = 'Model:',
  choices = c("Default", "Human interaction", "Online-offline", "Social media"), 
  selected = "Default"
)

uiOutput("profile")
```

```{r profileusersshortstart, context="setup"}
mod1_ord <- polr(data=china_isolation_data, human_interaction_cat ~ ses + 
                   female + CCP_member + age, Hess=TRUE)
mod2_ord <- polr(online_offline_cat ~ ses + female + CCP_member + age, 
                 data=china_isolation_data, Hess=TRUE)
mod3 <- lm(gen_social_med ~ ses + female + CCP_member + age,
           data=china_isolation_data)

n <- "▲, ▼ indicates p>0.05"

models <- list(
  "Human Interaction" = mod1_ord,
  "Online/Offline Interaction" = mod2_ord,
  "General Social Media" = mod3
)

# Remove the number estimates
mod_list <- modelsummary(models, output = "modelsummary_list")
mod_list <- replace_estimates(mod_list)

profile.table <- modelsummary(mod_list, 
             coef_omit = ".*Connect|.*Intercept|.*No|.*Yes",
             coef_rename = c("ses" = "SES",
                           "female" = "Female",
                             "CCP_member" = "CCP Member",
                             "age" = "Age"),
             fmt=2,
             output="gt",
             gof_map = gof.included.short,
             statistic=NULL) %>% 
  tab_footnote(footnote = n) 
```

```{r profiledef, context="server"}
output$profile <- renderUI({

  if(input$model1=="Default") {
    profile.table
  }
  else if(input$model1=="Human interaction") {
    profile.table %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 2,
            rows = c(2,3)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right", "top"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 2,
            rows = c(1)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right", "bottom"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 2,
            rows = c(4)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_text(weight = "bold",
                    color = "blue")
          ),
        locations = cells_body(
          columns = 2,
          rows = c(1:4)
          )
        )
  } else if(input$model1=="Online-offline") {
    profile.table %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 3,
            rows = c(2,3)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right", "top"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 3,
            rows = c(1)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right", "bottom"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 3,
            rows = c(4)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_text(weight = "bold",
                    color = "blue")
          ),
        locations = cells_body(
          columns = 3,
          rows = c(1:4)
          )
        ) 
  } else {
    profile.table %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 4,
            rows = c(2,3)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right", "top"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 4,
            rows = c(1)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right", "bottom"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 4,
            rows = c(4)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_text(weight = "bold",
                    color = "blue")
          ),
        locations = cells_body(
          columns = 4,
          rows = c(1:4)
          )
        )
  }

})
```

### Modeling social isolation

```{r socialisolationshort, out.width = "100%"}
selectInput(
  'model2', label = 'Model:',
  choices = c("Default", "Model 1", "Model 2", "Model 3", "Model 4"), 
  selected = "Default"
)

uiOutput("sociso")
```

```{r socialisolationshortstart, context="setup"}
mod4 = lm(isolation ~ human_interaction + online_offline + gen_social_med + urbanicity + ses + female + CCP_member + age, data = china_isolation_data)

mod5 = lm(isolation ~ human_interaction*urbanicity + online_offline + gen_social_med + ses + female + CCP_member + age, data = china_isolation_data)

mod6 = lm(isolation ~ online_offline*urbanicity + human_interaction + gen_social_med + ses + female + CCP_member + age, data = china_isolation_data)

mod7 = lm(isolation ~ gen_social_med*urbanicity + human_interaction + online_offline + ses + female + CCP_member + age, data = china_isolation_data)

n <- "▲, ▼ indicates p>0.05"

mods <- list(mod4, mod5, mod6, mod7)

# Remove the number estimates
mod_list <- modelsummary(mods, output = "modelsummary_list")
mod_list <- replace_estimates(mod_list)

socisotable <- modelsummary(mod_list, 
             coef_omit = ".*Connect|.*Intercept|.*No|.*Yes",
             coef_rename = c("ses" = "SES",
                             "female" = "Female",
                             "CCP_member" = "CCP Member",
                             "age" = "Age",
                             "urbanicity" = "Urbanicity",
                             "online_offline" = "Online-Offline",
                             "human_interaction" = "Human Interaction",
                             "gen_social_med" = "Social Media",
                             "human_interaction:urbanicity" = 
                               "Human Interaction*Urbanicity",
                             "online_offline:urbanicity" =
                               "Online-Offline*Urbanicity",
                             "gen_social_med:urbanicity" = 
                               "Social Media*Urbanicity"),
             fmt=2,
             output="gt",
             gof_map = gof.included.short,
             statistic = NULL) %>% 
  tab_footnote(footnote = n) %>% 
  tab_header("Response variable: social isolation")
```

```{r socialisolationdef, context="server"}
output$sociso <- renderUI({

  if(input$model2=="Default") {
    socisotable
  }
  else if(input$model2=="Model 1") {
    socisotable %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 2,
            rows = c(2:10)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right", "top"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 2,
            rows = c(1)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right", "bottom"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 2,
            rows = c(11)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_text(weight = "bold",
                    color = "blue")
          ),
        locations = cells_body(
          columns = 2,
          rows = c(1:11)
          )
        )
  } else if(input$model2=="Model 2") {
    socisotable %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 3,
            rows = c(2:10)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right", "top"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 3,
            rows = c(1)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right", "bottom"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 3,
            rows = c(11)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_text(weight = "bold",
                    color = "blue")
          ),
        locations = cells_body(
          columns = 3,
          rows = c(1:11)
          )
        )
  } else if(input$model2=="Model 3") {
    socisotable %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 4,
            rows = c(2:10)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right", "top"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 4,
            rows = c(1)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right", "bottom"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 4,
            rows = c(11)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_text(weight = "bold",
                    color = "blue")
          ),
        locations = cells_body(
          columns = 4,
          rows = c(1:11)
          )
        )
  } else {
    socisotable %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 5,
            rows = c(2:10)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right", "top"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 5,
            rows = c(1)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_borders(
            sides = c("left", "right", "bottom"),
            color = "#FF0000",
            weight = px(3)
          )
        ),
        locations = list(
          cells_body(
            columns = 5,
            rows = c(11)
          )
        )
      ) %>% 
      tab_style(
        style = list(
          cell_text(weight = "bold",
                    color = "blue")
          ),
        locations = cells_body(
          columns = 5,
          rows = c(1:11)
          )
        )
  }

})
```

### Marginal effects

```{r marginaleffects, out.width = "100%"}

selectInput(
  'model', label = 'Model:',
  choices = c("Human interaction", "Online-offline", "Social media"), 
  selected = "Human interaction"
)

plotOutput("margins")
```

```{r marginsetup, context="server-start"}
  mod5 = lm(isolation ~ human_interaction*urbanicity + online_offline 
            + gen_social_med + ses + female + CCP_member + age, 
            data = china_isolation_data)

  mod6 = lm(isolation ~ online_offline*urbanicity + human_interaction 
            + gen_social_med + ses + female + CCP_member + age, 
            data = china_isolation_data)

  mod7 = lm(isolation ~ gen_social_med*urbanicity + human_interaction 
            + online_offline + ses + female + CCP_member + age, 
            data = china_isolation_data)

  a <- plot_model(mod5, type = "pred", title = "",
                  terms = c("human_interaction", "urbanicity"), 
                  legend.title = "Urbanicity") +
    scale_color_discrete(labels = c("Village", "Small City", 
                                    "Mid-sized City", "Suburb", "Big City")) +
    ylab("") +
    xlab("Digital Human Interaction") +
    theme(panel.border = element_rect(color = "black",fill = NA, size = 1))

  b <- plot_model(mod6, type = "pred", title = "", 
                  terms = c("online_offline", "urbanicity"), 
                  legend.title = "Urbanicity") +
    scale_color_discrete(labels = c("Village", "Small City", 
                                    "Mid-sized City", "Suburb", "Big City")) +
    ylab("") +
    xlab("Online to Offline Relationships") +
    theme(panel.border = element_rect(color = "black",fill = NA, size = 1))

  c <- plot_model(mod7, type = "pred", title = "", 
                  terms = c("gen_social_med", "urbanicity"), 
                  legend.title = "Urbanicity") +
    scale_color_discrete(labels = c("Village", "Small City", 
                                    "Mid-sized City", "Suburb", "Big City")) + 
    ylab("") +
    xlab("Social Media Use") +
    theme(panel.border = element_rect(color = "black",fill = NA, size = 1))  
```

```{r margindef, context="server"}
output$margins <- renderPlot({

  if(input$model=="Human interaction") {
    a
  } else if(input$model=="Online-offline") {
    b
  } else {
    c
  }

})
```

## Conclusion and links to resources

* China context not so different?
* Government regulation not likely to be helpful?
* More research?
* Help us out!

```{r qrcodeconclusion, out.width = "300px", fig.cap="QR code for this presentation"}
knitr::include_graphics("www/qrcode.png")
```

Presentation website: [bit.ly/rc2023presentation](https://bit.ly/rc2023presentation)

Conference paper: [bit.ly/rc2023paper](https://bit.ly/rc2023paper)

Github repository: [bit.ly/rc2023github](https://bit.ly/rc2023github)

## Appendix

### Full model results

*Profile of users full results*

```{r profileusersfull, exercise=TRUE}
mod1_ordfull = polr(human_interaction_cat ~ ses + female + CCP_member + age, data = china_isolation_data, Hess=TRUE)
mod2_ordfull = polr(online_offline_cat ~ ses + female + CCP_member + age, data = china_isolation_data, Hess=TRUE)
mod3full = lm(gen_social_med ~ ses + female + CCP_member + age, data = china_isolation_data)

modelsfull <- list(
  "Human Interaction" = mod1_ordfull,
  "Online/Offline Interaction" = mod2_ordfull,
  "General Social Media" = mod3full
)

gof.included <- list(
  list("raw" = "nobs", "clean" = "N", "fmt" = "%i"),
  list("raw" = "r2.nagelkerke", "clean" = "Pseudo R2", "fmt" = "%.2f"),
  list("raw" = "r.squared", "clean" = "R2", "fmt" = "%.2f"))

n <- "Human Interaction and Offline/Online Relationships estimates are derived from ordered logit and General Social Media from ordinary least squares."

modelsummary(modelsfull, 
             coef_omit = ".*Connect|.*Intercept|.*No|.*Yes",
             coef_rename = c("ses" = "SES",
                             "female" = "Female",
                             "CCP_member" = "CCP Member",
                             "age" = "Age"),
             fmt=2,
             stars=c("*" = 0.05),
             output="kableExtra",
             gof_map = gof.included.full) %>% 
  footnote(general = n, threeparttable = TRUE)
```

*Modeling social isolation*

```{r socialisolationfull, exercise=TRUE}
mod4full = lm(isolation ~ human_interaction + online_offline + gen_social_med + urbanicity + ses + female + CCP_member + age, data = china_isolation_data)

mod5full = lm(isolation ~ human_interaction*urbanicity + online_offline + gen_social_med + ses + female + CCP_member + age, data = china_isolation_data)

mod6full = lm(isolation ~ online_offline*urbanicity + human_interaction + gen_social_med + ses + female + CCP_member + age, data = china_isolation_data)

mod7full = lm(isolation ~ gen_social_med*urbanicity + human_interaction + online_offline + ses + female + CCP_member + age, data = china_isolation_data)

n <- "Estimates are derived using ordinary least squares"

modsfull <- list(mod4full, mod5full, mod6full, mod7full)

modelsummary(modsfull, 
             coef_omit = ".*Connect|.*Intercept|.*No|.*Yes",
             coef_rename = c("ses" = "SES",
                             "female" = "Female",
                             "CCP_member" = "CCP Member",
                             "age" = "Age",
                             "urbanicity" = "Urbanicity",
                             "online_offline" = "Online-Offline",
                             "human_interaction" = "Human Interaction",
                             "gen_social_med" = "Social Media",
                             "human_interaction:urbanicity" = 
                               "Human Interaction*Urbanicity",
                             "online_offline:urbanicity" =
                               "Online-Offline*Urbanicity",
                             "gen_social_med:urbanicity" = 
                               "Social Media*Urbanicity"),
             fmt=2,
             stars=c("*" = 0.05),
             output="kableExtra",
             gof_map = gof.included.full) %>% 
  footnote(general = n, threeparttable = TRUE)
```

### Variable definitions

```{r socisoqs}
table.text <- list()

table.text[[1]] <- c("Header", "The next question is about how you feel about different aspects of your life. Could you tell me for each one if you feel that way always, almost always, some of the time, rarely or never?")
table.text[[2]] <- c("Q1", "How often do you feel that you lack companionship")
table.text[[3]] <- c("Q2", "How often do you feel isolated from others?")
table.text[[4]] <- c("Q3", "How often do you feel left out?")

sociso.text <- data.frame()

for(line in table.text) {
  sociso.text <- rbind(sociso.text, line)
}

kbl(sociso.text, col.names = NULL, caption="Social isolation variable construction") %>% 
  kable_styling()
```

```{r humintqs}
table.text <- list()

table.text[[1]] <- c("Q", "Has the internet and phone applications increased your contact with the following groups of people (check yes to all that apply)?")
table.text[[2]] <- c("R1", "Family that lives nearby")
table.text[[3]] <- c("R2", "Family that lives far away")
table.text[[4]] <- c("R3", "Friends that live nearby")
table.text[[5]] <- c("R4", "Friends that live far away")
table.text[[6]] <- c("R5", "People you met on the internet that live nearby")
table.text[[7]] <- c("R6", "People you met on the internet that live far away")

humint.text <- data.frame()

for(line in table.text) {
  humint.text <- rbind(humint.text, line)
}

kbl(humint.text, col.names = NULL, caption="Human interaction variable construction") %>% 
  kable_styling()
```

```{r onloffqs}
table.text <- list()

table.text[[1]] <- c("Q", "Have you met someone offline that you initially met online?")
table.text[[2]] <- c("R1", "Yes, many times")
table.text[[3]] <- c("R2", "Yes, several times")
table.text[[4]] <- c("R3", "Yes, once")
table.text[[5]] <- c("R4", "No, never")

onloff.text <- data.frame()

for(line in table.text) {
  onloff.text <- rbind(onloff.text, line)
}

kbl(onloff.text, col.names = NULL, caption="Online-offline variable construction") %>% 
  kable_styling()
```

```{r socmedqs}
table.text <- list()

table.text[[1]] <- c("Q1", "About how many hours a day would you estimate you spend using only social media? Social media means applications like Weibo, QQ, Renren, Kaixin001, Douban, WeChat or other sites and services that allow users to interact with each other.")
table.text[[2]] <- c("RC", "0-1, 1-2, 2-3, 3-4, 4-5, 5-6, 6-7, 7-8, 8-9, or More than 9")
table.text[[3]] <- c("Q2", "Do you check email, read websites, and use social media (social media means applications like Weibo, QQ, Renren, Kaixin001, Douban, WeChat or other sites and services that allow users to interact with each other) more than you did five years ago?")
table.text[[4]] <- c("RC", "Yes, No")
table.text[[5]] <- c("Q3", "How often do you read news stories about political events that have been posted on social media (social media means applications like Weibo, QQ, Renren, Kaixin001, Douban, WeChat or other sites and services that allow users to interact with each other)?")
table.text[[6]] <- c("RC", "More than once a day, Everyday, Three-to-five days per week, One-to-two days per week, Less often, Never")

socmed.text <- data.frame()

for(line in table.text) {
  socmed.text <- rbind(socmed.text, line)
}

kbl(socmed.text, col.names = NULL, caption="Social media variable construction") %>% 
  kable_styling()
```

```{r urbqs}
table.text <- list()

table.text[[1]] <- c("Q", "Which of these best describes the place in which you live?")
table.text[[2]] <- c("R1", "Countryside/Village")
table.text[[3]] <- c("R2", "Small City")
table.text[[4]] <- c("R3", "Mid-Sized City")
table.text[[5]] <- c("R4", "Suburban Area of a Big City")
table.text[[6]] <- c("R5", "Big City")

urb.text <- data.frame()

for(line in table.text) {
  urb.text <- rbind(urb.text, line)
}

kbl(urb.text, col.names = NULL, caption="Urbanicity variable construction") %>% 
  kable_styling()
```

### Additional reading

<div id="refs"></div>

### 2023-07-06 presentations/Responsible Citizens presentation/Responsible Citizens 2023 Presentation.Rmd
Final presentation files

@@
   learnr::tutorial:
-    toc_depth: 3
+    toc_depth: 2
 bibliography: www/references.bib
@@
 
+replace_estimates <- function(mod_list_func) {
+
+  working <- mod_list_func
+
+  for(model in 1:length(working)) {
+    for(obs in 1:nrow(working[[model]]$tidy)) {
+      working[[model]]$tidy$estimate[obs] <- case_when(working[[model]]$tidy$p.value[obs] > 0.05 ~ "—",
+                                working[[model]]$tidy$estimate[obs] >= 0 ~ "▲",
+                                working[[model]]$tidy$estimate[obs] < 0 ~ "▼")
+    }
+  }
+
+  return(working)
+}
+
 gof.included.short <- list()
@@
   list("raw" = "r.squared", "clean" = "R2", "fmt" = "%.2f"))
-
-replace_estimates <- function(mod_list) {
-
-  for(model in 1:length(mod_list)) {
-    for(obs in 1:nrow(mod_list[[model]]$tidy)) {
-      mod_list[[model]]$tidy$estimate[obs] <- case_when(mod_list[[model]]$tidy$p.value[obs] > 0.05 ~ "—",
-                                mod_list[[model]]$tidy$estimate[obs] >= 0 ~ "▲",
-                                mod_list[[model]]$tidy$estimate[obs] < 0 ~ "▼")
-    }
-  }
-
-  return(mod_list)
-}
 
@@
 
-```{r profileusersshortstart, context="setup"}
-mod1_ord <- polr(data=china_isolation_data, human_interaction_cat ~ ses + 
+```{r profileusersshortstart, context="data"}
+mod1_ord_short <- polr(data=china_isolation_data, human_interaction_cat ~ ses + 
                    female + CCP_member + age, Hess=TRUE)
-mod2_ord <- polr(online_offline_cat ~ ses + female + CCP_member + age, 
+mod2_ord_short <- polr(online_offline_cat ~ ses + female + CCP_member + age, 
                  data=china_isolation_data, Hess=TRUE)
-mod3 <- lm(gen_social_med ~ ses + female + CCP_member + age,
+mod3_short <- lm(gen_social_med ~ ses + female + CCP_member + age,
            data=china_isolation_data)
@@
 
-models <- list(
-  "Human Interaction" = mod1_ord,
-  "Online/Offline Interaction" = mod2_ord,
-  "General Social Media" = mod3
+mods_prof <- list(
+  "Human Interaction" = mod1_ord_short,
+  "Online/Offline Interaction" = mod2_ord_short,
+  "General Social Media" = mod3_short
 )
@@
 # Remove the number estimates
-mod_list <- modelsummary(models, output = "modelsummary_list")
-mod_list <- replace_estimates(mod_list)
-
-profile.table <- modelsummary(mod_list, 
+mod_list_prof <- modelsummary(mods_prof, output = "modelsummary_list")
+mod_list_prof_update <- as.list(mod_list_prof)
+mod_list_prof_update <- replace_estimates(mod_list_prof_update)
+
+profile.table <- modelsummary(mod_list_prof_update, 
              coef_omit = ".*Connect|.*Intercept|.*No|.*Yes",
@@
 
-```{r socialisolationshortstart, context="setup"}
-mod4 = lm(isolation ~ human_interaction + online_offline + gen_social_med + urbanicity + ses + female + CCP_member + age, data = china_isolation_data)
-
-mod5 = lm(isolation ~ human_interaction*urbanicity + online_offline + gen_social_med + ses + female + CCP_member + age, data = china_isolation_data)
-
-mod6 = lm(isolation ~ online_offline*urbanicity + human_interaction + gen_social_med + ses + female + CCP_member + age, data = china_isolation_data)
-
-mod7 = lm(isolation ~ gen_social_med*urbanicity + human_interaction + online_offline + ses + female + CCP_member + age, data = china_isolation_data)
+```{r socialisolationshortstart, context="data"}
+mod4short = lm(isolation ~ human_interaction + online_offline + gen_social_med + urbanicity + ses + female + CCP_member + age, data = china_isolation_data)
+
+mod5short = lm(isolation ~ human_interaction*urbanicity + online_offline + gen_social_med + ses + female + CCP_member + age, data = china_isolation_data)
+
+mod6short = lm(isolation ~ online_offline*urbanicity + human_interaction + gen_social_med + ses + female + CCP_member + age, data = china_isolation_data)
+
+mod7short = lm(isolation ~ gen_social_med*urbanicity + human_interaction + online_offline + ses + female + CCP_member + age, data = china_isolation_data)
 
@@
 
-mods <- list(mod4, mod5, mod6, mod7)
+mods_soc <- list(mod4short, mod5short, mod6short, mod7short)
 
 # Remove the number estimates
-mod_list <- modelsummary(mods, output = "modelsummary_list")
-mod_list <- replace_estimates(mod_list)
-
-socisotable <- modelsummary(mod_list, 
+mod_list_soc <- modelsummary(mods_soc, output = "modelsummary_list")
+mod_list_soc_update <- as.list(mod_list_soc)
+mod_list_soc_update <- replace_estimates(mod_list_soc_update)
+
+socisotable <- modelsummary(mod_list_soc_update, 
              coef_omit = ".*Connect|.*Intercept|.*No|.*Yes",
@@
 ```{r marginsetup, context="server-start"}
-  mod5 = lm(isolation ~ human_interaction*urbanicity + online_offline 
+  mod5margin = lm(isolation ~ human_interaction*urbanicity + online_offline 
             + gen_social_med + ses + female + CCP_member + age, 
@@
 
-  mod6 = lm(isolation ~ online_offline*urbanicity + human_interaction 
+  mod6margin = lm(isolation ~ online_offline*urbanicity + human_interaction 
             + gen_social_med + ses + female + CCP_member + age, 
@@
 
-  mod7 = lm(isolation ~ gen_social_med*urbanicity + human_interaction 
+  mod7margin = lm(isolation ~ gen_social_med*urbanicity + human_interaction 
             + online_offline + ses + female + CCP_member + age, 
@@
 
-  a <- plot_model(mod5, type = "pred", title = "",
+  a <- plot_model(mod5margin, type = "pred", title = "",
                   terms = c("human_interaction", "urbanicity"), 
@@
 
-  b <- plot_model(mod6, type = "pred", title = "", 
+  b <- plot_model(mod6margin, type = "pred", title = "", 
                   terms = c("online_offline", "urbanicity"), 
@@
 
-  c <- plot_model(mod7, type = "pred", title = "", 
+  c <- plot_model(mod7margin, type = "pred", title = "", 
                   terms = c("gen_social_med", "urbanicity"), 
@@
 
-modelsfull <- list(
+modelsfull_prof <- list(
   "Human Interaction" = mod1_ordfull,
@@
 
-modelsummary(modelsfull, 
+modelsummary(modelsfull_prof, 
              coef_omit = ".*Connect|.*Intercept|.*No|.*Yes",
@@
 
-modsfull <- list(mod4full, mod5full, mod6full, mod7full)
-
-modelsummary(modsfull, 
+modsfull_soc <- list(mod4full, mod5full, mod6full, mod7full)
+
+modelsummary(modsfull_soc, 
              coef_omit = ".*Connect|.*Intercept|.*No|.*Yes",

### 2023-08-25 Social Isolation in China.qmd
Added residual plots and variable operationalizations.

@@
 library(sjPlot)
+library(ggResidpanel)
 
@@
 found a negative relationship between social media use and social isolation in youth in a representative sample [@primack2017].
-A meta-review of the literature on adolescent social media usage notes that while the effect size is often small the relationship in most studies is negative [@valkenburg2022].
+A meta-review of the literature on adolescent social media usage notes that while the effect size is often small the relationship in most studies on social media's linkage to ill-being is negative [@valkenburg2022] while emphasizing the importance of heterogeneous effects.
 There are relatively fewer studies that consider all ages.
-However, those that have been conducted also generally find a negative (if modest) relationship [@appel2020].
-More recent research has suggested that the effect of social media on measures like social isolation may be highly heterogeneous across individuals, a finding that would help reconcile some of the discrepancies in the literature [@beyens2020; @ostic2021].
+However, those that have been conducted also emphasize that the relationship between social media use and well-being has possible negative effects but the effects seem to vary by personality type [@appel2020].
+More recent research has reinforced the finding that the effect of social media on measures like social isolation may be highly heterogeneous across individuals [@beyens2020; @ostic2021].
 
@@
 Many people are aware that the Chinese government heavily censors politically sensitive content on online platforms.
-However, fewer are aware that the Chinese government spends as much if not more effort to clean up non-political but negative or distressing content on the Chinese internet, such as scams, instances of cyber bullying, disturbing videos, and vulgar content [@wang2020].
+However, fewer are aware that the Chinese government spends as much, if not more, effort to clean up non-political as negative or distressing content on the Chinese internet, such as scams, instances of cyber bullying, disturbing videos, and vulgar content [@wang2020].
 This control impulse also extends content the government views as spiritually polluting, such as pornography, scantily dressed women, and other escapist content.
@@
 If one of the main mechanisms through which social media promotes social isolation occurs is exposure to negative content, then this online environment should lead to a weaker relationship between social media use and isolation.
-Suggestive of this is a a study by Liu and Liu that finds those who consumed more commercialized and sensationalized media reported more trauma during the first COVID-19 in China than those who followed government sources [@liu2020].
+Suggestive of this is a a study by Liu and Liu that finds Chinese who consumed who consumed more commercialized and sensationalized media reported more trauma during the first COVID-19 outbreak in China than those who followed government sources [@liu2020].
 
@@
 
-Aditionally, China's social media environment is relatively unique in that the dominant messaging platform is also the largest social media app (WeChat).
+Additionally, China's social media environment is relatively unique in that the dominant messaging platform is also the largest social media app (WeChat).
 Users can use it simply to chat with family and friends, they can use it to post photos and other content about their life in a feed that works similarly to Facebook, or they can browse videos of others in a method similar to Tiktok.
@@
 Our contribution here is that we look at some well-established theoretical arguments in a context outside that of where most of the research centered on these type questions has examined.
-While our study is far from the last word on the subject, these results suggest that the mechanisms that link social media use and social isolation are relatively context-insensitive.
+While our study is far from the last word on the subject, these results suggest that the mechanisms that link social media use and social isolation are relatively consistent across countries.
 
@@
 
+SES is an additive index of these two questions regarding income and education.
+Each of the following questions were rescaled to range from 0 through 1, then the two questions were summed, and then rescaled to range from 0 through 1 again.
+
+-   Here is a table showing the range of monthly incomes that people have. Which of the letters on this table best represents the total monthly income of your household (after tax)?
+
+    -   0 - 3,000,
+
+    -   3,000 - 6,000,
+
+    -   6,000 - 10,000,
+
+    -   10,000 - 15,000,
+
+    -   15,000 - 25,000,
+
+    -   25,000 - 40,000,
+
+    -   More than 40,000
+
+-   What is the highest level of education that you have obtained?
+
+    -   No formal education,
+
+    -   Primary,
+
+    -   Middle school,
+
+    -   High school,
+
+    -   University,
+
+    -   Advanced Studies/Graduate School
+
+Other important predictor variables are operationalized as follows:
+
+-   Gender
+
+    -   0 = male,
+
+    -   1 = female
+
+-   Are you a member or probationary member of the CCP?
+
+    -   0 = no,
+
+    -   1 = yes
+
+-   How old are you? (rescaled to range from 0 through 1)
+
+{{< pagebreak >}}
+
 ### Residual Analysis
+
+```{r}
+#| label: fig-resids-human
+#| fig-cap: "Human Interaction Model Residuals"
+
+resid_panel(mod5, plots = "R")
+```
+
+```{r}
+#| label: fig-resids-online-offline
+#| fig-cap: "Online/Offline Model Residuals"
+
+resid_panel(mod6, plots = "R")
+```
 

### 2023-08-31 Social Isolation in China.qmd
prep for journal submission

@@
 title: "The Spatial Relationship between Social Media, Digital Connectedness, and Social Isolation in China: Revisting Cyber-Optimism"
-author: 
-  - Jason Gainous^[University of Louisville, jason.gainous@louisville.edu]
-  - Andrew W. MacDonald^[Duke Kunshan University, andrew.macdonald@dukekunshan.edu.cn]
+
 date: '`r format(Sys.time(), "%B %d, %Y")`'
-abstract: "Early research and popular discourse on the promise of the internet was optimistic.
-Many believed it would promote social interconnectedness and, ultimately, be a positive force in people’s lives.
-Since these early predictions, research has become much less positive, usually pointing to the negative aspects of social media.
-Here we test whether the digital environment can actually create a space that deters feelings of social isolationism especially for those living outside cities in restrictive information environments where citizens are often disconnected from the outside world.
-Using data from a nationwide survey of Chinese citizens we conducted in 2015, we do find that the more citizens digitally connect with others, the less personally isolated they feel, but that this relationship is less pronounced for those in rural communities.
+abstract: "Early research and popular discourse on the promise of the internet's impact on social isolation was optimistic.
+Since these early predictions, research has become less positive, usually pointing to the negative role of social media.
+However, little is known about this relationship in highly controlled, autocratic social media environments.
+Using data from a nationwide survey of Chinese citizens, we do find that the more citizens digitally connect with others, the less personally isolated they feel.
 Conversely, though, the more likely people are to move relationships from online to offline, and the more they use social media, the more personally isolated they feel.
-These counter-relationships are more pronounced for those in rural communities.
-Generally, those living in urban environments tend to feel more isolated, and digital connection does not seem to mediate this spatial factor.
-In fact, it exacerbates loneliness."
+We also find that this relationship interacts with urbanicity - being in rural areas tends to amplify the effect.
+Overall, our findings suggest that institutional context may not play an important role in the social media - social isolation relationship."
 keywords: 
@@
   warning: false
+keep-tex: true
 bibliography: references.bib
+csl: sage-harvard.csl
 ---
@@
 
+{{< pagebreak >}}
+
 # Social Isolation in China
@@
 Early research suggested that the internet would build social capital, or an interconnectedness between people, and that social media platforms were the ultimate way to bring people together.
-Since then, research indicates that the effect may be the opposite for many.
+Since then, research indicates that the effect may be the opposite among at least some part of the population.
 Social media may encourage social isolation, and ultimately, social media users may feel more disconnected from others than those who do not use social media.
@@
 This allows us to test whether such features moderate or exacerbate the relationship between social media use and social isolation.
-To fully test this theory, we employ a large survey of Chinese internet users and test a variety of regression specifications.
-The main result is that social media use is robustly negatively related to social isolation, though the nature of this relationship changes depending on the urbanicity of the respondent - being in a rural area amplifies this relationship.
+To fully test this theory, we employ a large survey of Chinese internet users and test a variety of regression specifications.[^1] The main result is that social media use is robustly negatively related to social isolation, though the nature of this relationship changes depending on the urbanicity of the respondent - being in a rural area amplifies this relationship.
+
+[^1]: All data and analysis files for this research are available at the author's website.
 
@@
 However, those that have been conducted also emphasize that the relationship between social media use and well-being has possible negative effects but the effects seem to vary by personality type [@appel2020].
-More recent research has reinforced the finding that the effect of social media on measures like social isolation may be highly heterogeneous across individuals [@beyens2020; @ostic2021].
+More recent research has reinforced the finding that the effect of social media on measures like social isolation may be highly heterogeneous across individuals; for some individuals, the effect may be quite negative for some while for others social media usage may have a modestly positive impact on well-being [@beyens2020; @ostic2021].
 
 While most of the studies agree that the causal direction flows from social media use to feelings of isolation (though see [@nowland2018; @kim2017]), there is disagreement among authors about the specific mechanisms and causal pathways through which this relationship exists.
-One set of mechanisms find that the social media itself that is the problem.
+For those who find a negative relationship between social media and well-being, one set of mechanisms suggests that the social media itself that is the problem.
 Cyberbullying, or more generally, repeated and aggressive online attacks against users has been systematically linked to feelings of social isolation [@ademiluyi2022].
-Upward comparisons of others and the weak nature of online connections has been found to generate social anxiety and social isolation [@alabri2022; @büttner2022].
-Another set of mechanisms primarily concern themselves with the physical changes that social media causes.
+Another proposed mechanism is upward comparisons of others and the weak nature of online connections - both of these have been found to generate social anxiety and social isolation [@alabri2022; @büttner2022].
+A third set of mechanisms primarily concern themselves with the physical changes that social media causes.
 Social media use has been shown to displace face to face activity, which leads to greater social isolation [@larson2018].
@@
 While the Chinese government and online platforms are not 100 per cent effective in their ability to completely stamp out such content, the default is that such content is actively restricted, while US platforms tent to take a more pro-speech regulatory position [@liu2022].
-If one of the main mechanisms through which social media promotes social isolation occurs is exposure to negative content, then this online environment should lead to a weaker relationship between social media use and isolation.
-Suggestive of this is a a study by Liu and Liu that finds Chinese who consumed who consumed more commercialized and sensationalized media reported more trauma during the first COVID-19 outbreak in China than those who followed government sources [@liu2020].
+If one of the main mechanisms through which social media promotes social isolation occurs is exposure to negative content, then this highly regulated online environment should lead to a weaker relationship between social media use and isolation.
+Suggestive of this is a a study by Liu and Liu that finds Chinese who consumed more commercialized and sensationalized media reported more trauma during the first COVID-19 outbreak in China than those who followed government sources [@liu2020].
 
@@
 In this influencer culture, less attention is paid to authenticity and personality and relatively more emphasis is placed on consumerism, brand promotion, and image [@tam2019; @wei2023].
-Given that previous research has suggested one of the main channels through which social media creates feelings of isolation is negative personal comparisons with online content (so-called "FOMO" - fear of missing out), heavy social media use may increase the strength of the relationship between social media use and social isolation.
+Given that previous research has suggested one of the main channels through which social media creates feelings of isolation is negative personal comparisons with online content (so-called "FOMO" - fear of missing out), heavy social media use may increase the strength of the relationship between social media use and social isolation through consumption of such highly commercialized content.
 
@@
 Previous research has indicated that while, on the whole, social media increases social isolation, for users that primarily use it to contact friends and family, its use can counteract the negative effects [@hajek2019; @lim2020].
-Given the ubiquity of WeChat in China, we expect to find similar results.
+In this way, those that heavily use these type of combined platforms may engage in multiple uses of social media that tend to cancel each other out.
+Given the ubiquity of WeChat in China, such a relationship seems plausible.
 
@@
 
-## Data, Measurement and Descriptives
+## Data, Measurement, and Descriptives
 
-The data from this study are original.
+The data used in this study are original.
 We designed a survey instrument in English, and translated it into Chinese, to measure a range of concepts including social isolationism and various dimensions of social media and digital information consumption.
 We employed Qualtrics to collect the data.
-They randomly selected 2292 respondents from their existing panel[^1] from November 25 to December 2, 2015.
-This sample size on provides for a roughly $\pm2$ margin of error.[^2]
+They randomly selected 2292 respondents from their existing panel[^2] from November 25 to December 2, 2015.
+This sample size on provides for a roughly $\pm2$ margin of error.[^3]
 
-[^1]: Qualtrics recruits a large pool of respondents for various survey projects through online advertising.
+[^2]: Qualtrics recruits a large pool of respondents for various survey projects through online advertising.
 Recruits who update their profiles at least once every 6 months are randomly invited to participate.
@@
 
-[^2]: We were able to first collect a small sample ($n=286$) to check the reliability and adjust the instrument after before proceeding with the final data collection.
+[^3]: We were able to first collect a small sample ($n=286$) to check the reliability and adjust the instrument after before proceeding with the final data collection.
 We made three adjustments, none of which are related to the measures used in the current study.
@@
 However, this does not seem to extend to those that use the internet to facilitate offline meetups.
-Finally, we find that the impact of the internet and social media vary significantly according to the level of urbanicity (**H3**).
-These findings are generally in line with previous research on the subject, suggesting that the mechanisms that generate feelings of social isolation are universal and not so sensitive to different social and governing contexts.
+Finally, we find that the impact of the internet and social media vary significantly according to the level of urbanicity (**H3**) - this matches with previous findings that suggest that there is significant heterogeneity in the impact of social media on social isloation.
+All of these findings are generally in line with previous research on the subject, suggesting that the mechanisms that generate feelings of social isolation are universal and not so sensitive to different social and governing contexts.
 
@@
 
+{{< pagebreak >}}
+
 ## References
@@
 :::
+
+{{< pagebreak >}}
 

### 2023-08-31 Social-Isolation-in-China.tex
prep for journal submission

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else  
+    % xetex/luatex font selection
 \fi
@@
 \makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 \usepackage{xcolor}
+\usepackage{siunitx}
+
+  \newcolumntype{d}{S[
+    input-open-uncertainty=,
+    input-close-uncertainty=,
+    parse-numbers = false,
+    table-align-text-pre=false,
+    table-align-text-post=false
+  ]}
+
 \KOMAoption{captions}{tableheading}
@@
 \makeatletter
-\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
+\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
 \makeatother
@@
 \@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
+\makeatother
+\makeatletter
 \makeatother
@@
   pdftitle={The Spatial Relationship between Social Media, Digital Connectedness, and Social Isolation in China: Revisting Cyber-Optimism},
-  pdfauthor={Jason Gainous; Andrew W. MacDonald},
-  pdfkeywords={social isolation, social media, digital
-connectedness, China},
+  pdfkeywords={Social Isolation, Social Media, Digital
+Communication, China},
   colorlinks=true,
@@
 Connectedness, and Social Isolation in China: Revisting Cyber-Optimism}
-\author{Jason Gainous\footnote{University of Louisville,
-  jason.gainous@louisville.edu} \and Andrew W. MacDonald\footnote{Duke
-  Kunshan University, andrew.macdonald@dukekunshan.edu.cn}}
-\date{3/5/23}
+\author{}
+\date{2023-08-31}
 
@@
 \begin{abstract}
-Early research and populuar discourse on the promise of the internet was
-optimistic. Many believed it would promote social interconnectedness
-and, ultimately, be a positive force in people's lives. Since these
-early predictions, research has become much less positive, usually
-pointing to the negative aspects of social media. Here we argue that the
-digital environment can actually create a space that deters feelings of
-social isolationism especially for those living outside cities in
-restrictive information environments where citizens are often
-disconnected from the outside world. Using data from a nationwide survey
-of Chinese citizens we conducted in 2015, we find that the more citizens
-digitally connect with others, the more likely they are to move
-relationships from online to offliine, and the more they use social
-media the less personally isolated they feel. Futher, those living in
-urban environments tend to feel more isolated, and this spatial factor
-seems to moderate the aforementioned relationships. All three of those
-observed relationships are stronger for those in less urban
-environments.
+Early research and popular discourse on the promise of the internet's
+impact on social isolation was optimistic. Since these early
+predictions, research has become less positive, usually pointing to the
+negative role of social media. However, little is known about this
+relationship in highly controlled, autocratic social media environments.
+Using data from a nationwide survey of Chinese citizens, we do find that
+the more citizens digitally connect with others, the less personally
+isolated they feel. Conversely, though, the more likely people are to
+move relationships from online to offline, and the more they use social
+media, the more personally isolated they feel. We also find that this
+relationship interacts with urbanicity - being in rural areas tends to
+amplify the effect. Overall, our findings suggest that institutional
+context may not play an important role in the social media - social
+isolation relationship.
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, enhanced, frame hidden, interior hidden, boxrule=0pt, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, interior hidden, frame hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, enhanced]}{\end{tcolorbox}}\fi
+
+\newpage{}
 
@@
 the ultimate way to bring people together. Since then, research
-indicates that the effect may be the opposite for many. Social media may
-encourage social isolation, and ultimately, social media users may feel
-more disconnected from others than those who do not use social media. We
-know very little about this phenomenon in China. China presents an
-interesting case because the internet is bifurcated to some degree --
-there is the Chinese internet and the outside internet available via
-VPNs. Being isolation to the outside world may lessen feelings of
-isolation, or it may increase these feelings because digital exposure to
-a world is much larger than that in people's immediate environment
-without the ability to have in-person connection to may make one feel
-isolated. Interestingly, and somewhat ironically though, it may also
-matter, too, whether someone lives in a city. Research has suggested
-that urban living can actually lead to feelings of isolation.
+indicates that the effect may be the opposite among at least some part
+of the population. Social media may encourage social isolation, and
+ultimately, social media users may feel more disconnected from others
+than those who do not use social media. We know very little about this
+phenomenon in China. China presents an interesting case because the
+institutional structures, level of development and the cultural context
+are all quite different than the areas studied in most existing studies.
+This allows us to test whether such features moderate or exacerbate the
+relationship between social media use and social isolation. To fully
+test this theory, we employ a large survey of Chinese internet users and
+test a variety of regression specifications.\footnote{All data and
+  analysis files for this research are available at the author's
+  website.} The main result is that social media use is robustly
+negatively related to social isolation, though the nature of this
+relationship changes depending on the urbanicity of the respondent -
+being in a rural area amplifies this relationship.
 
-\hypertarget{introduction-1}{%
-\subsection{Introduction}\label{introduction-1}}
+\hypertarget{literature-review-and-theory}{%
+\subsection{Literature Review and
+Theory}\label{literature-review-and-theory}}
 
-Research is quite mixed when it comes to identifying the relationship
-between social media use and feelings of isolationism. Early research
-suggested that the internet would build social capital, or an
-interconnectedness between people, and that social media platforms were
-the ultimate way to bring people together. Since then, research
-indicates that the effect may be the opposite for many. Social media may
-encourage social isolation, and ultimately, social media users may feel
-more disconnected from others than those who do not use social media. We
-know very little about this phenomenon in China. China presents an
-interesting case because the internet is bifurcated to some degree --
-there is the Chinese internet and the outside internet available via
-VPNs. Being isolation to the outside world may lessen feelings of
-isolation, or it may increase these feelings because digital exposure to
-a world is much larger than that in people's immediate environment
-without the ability to have in-person connection to may make one feel
-isolated. Interestingly, and somewhat ironically though, it may also
-matter, too, whether someone lives in a city. Research has suggested
-that urban living can actually lead to feelings of isolation.
+The existing literature on social isolation and social media use
+generally finds a negative relationship between the two. However, there
+are some remaining questions regarding whether this relationship remains
+significant in different cultural and regulatory environments. Based on
+the existing literature, we then develop some testable hypotheses
+regarding how the relationship between usage and isolation may vary in
+the context of China. The result of these hypotheses tests will help to
+better understand the mechanism that links the two variables.
 
-\hypertarget{data}{%
-\subsection{Data}\label{data}}
+Initially, scholars imagined that social media would create more
+opportunities for users to create unique and fulfilling social
+relationships. The early theorizing about the possible benefits of
+social media hypothesized three important mechanisms by which social
+media could decrease loneliness. 1) creating more opportunities for
+online to offline meetups and 2) helping to alleviate feelings of
+isolation for those who have difficulty making in-person social
+connections via joining an online communities, and 3) facilitating
+keeping in touch with family and friends (Ellison et al., 2007;
+Steinfield et al., 2008; Subrahmanyam et al., 2008).
 
-Our data are based on a random Internet survey conducted by Qualtrics
-from November 25 to December 2, 2015. We designed the instrument,
-content and structure. After we designed the instrument in English and
-translated it into Chinese, we entered the questions into the graphical
-interface provided from our survey provider, Qualtrics. We were careful
-at this stage to make the formatting clear, and to distribute the
-questions across numerous pages to prevent overwhelming respondents with
-too many questions at once. This helped us achieve a high completion and
-response rate. Additionally, we were particularly attentive to the
-possibility of question order effects. Many of the questions are
-sensitive and could cue responses to subsequent questions. We grouped
-and placed questions strategically to limit any such potential for
-response bias. Once we settled on the design, Qualtrics administered the
-survey in November 2015. They recruit a large pool of respondents for
-various survey projects through online advertising on websites such as
-local portals, search engines, social networking services, and/or online
-shopping services. Panelists who update their profiles at least once
-every 6 months are randomly invited to participate in surveys for which
-they qualify. Online points are awarded to the corresponding panelists,
-which they may accumulate and exchange for cash or various other
-country-specific gifts to serve as an incentive for completion. This
-number of points is based on the length of the survey. Ours had over
-fifty questions, so respondents received a relatively high number of
-points.
+More recent studies on the subject have found significantly more mixed
+and often negative evidence regarding the impact of social media on
+feelings of isolation. Primack et al.~found a negative relationship
+between social media use and social isolation in youth in a
+representative sample (Primack et al., 2017). A meta-review of the
+literature on adolescent social media usage notes that while the effect
+size is often small the relationship in most studies on social media's
+linkage to ill-being is negative (Valkenburg et al., 2022) while
+emphasizing the importance of heterogeneous effects. There are
+relatively fewer studies that consider all ages. However, those that
+have been conducted also emphasize that the relationship between social
+media use and well-being has possible negative effects but the effects
+seem to vary by personality type (Appel et al., 2020). More recent
+research has reinforced the finding that the effect of social media on
+measures like social isolation may be highly heterogeneous across
+individuals; for some individuals, the effect may be quite negative for
+some while for others social media usage may have a modestly positive
+impact on well-being (Beyens et al., 2020; Ostic et al., 2021).
 
-The data collection had two phases. For the first phase, Qualtrics
-collected and submitted to us a trial run of 286 cases. We were able to
-check the data for reliability and adjust the instrument before
-proceeding with the second phase, the final data collection. We only
-made three adjustments, all of which turned out to be important and
-central to our analysis. For the trial run, we only asked respondents
-about pro-government Internet posters and did not ask them about
-potential net-spy or hostile posters. We amended this oversight and it
-became central to the analysis that follows. In addition, much of our
-theory focuses on the impact of Chinese Internet users circumventing
-government filters on the Internet. We initially had a question about
-whether citizens had jumped the wall to read sensitive political
-information (see Appendix A -- Q25), but decided to add whether they had
-done so for entertainment purposes as well (Q26 - to watch foreign
-movies, television shows, etc.). Finally, we also included an attention
-filter question as part of a battery of institutional trust questions
-where respondents were simply told to select the ``None at all''
-response (Q13H). If they did not select this response, we could assume
-they were not paying attention to the questions, and the survey ended
-for these respondents and the data were not collected for them. In the
-end, the full sample included a total of 2292 respondents. This sample
-size provides for a roughly ±2 margin of error.
+While most of the studies agree that the causal direction flows from
+social media use to feelings of isolation (though see (Kim, 2017;
+Nowland et al., 2018)), there is disagreement among authors about the
+specific mechanisms and causal pathways through which this relationship
+exists. For those who find a negative relationship between social media
+and well-being, one set of mechanisms suggests that the social media
+itself that is the problem. Cyberbullying, or more generally, repeated
+and aggressive online attacks against users has been systematically
+linked to feelings of social isolation (Ademiluyi et al., 2022). Another
+proposed mechanism is upward comparisons of others and the weak nature
+of online connections - both of these have been found to generate social
+anxiety and social isolation (Alabri, 2022; Büttner and Rudert, 2022). A
+third set of mechanisms primarily concern themselves with the physical
+changes that social media causes. Social media use has been shown to
+displace face to face activity, which leads to greater social isolation
+(Larson et al., 2018). Heavy social media use also decreases hours of
+sleep, leading to greater feelings of anxiety and more social isolation
+(Twenge et al., 2017). The current research suggests that which of these
+mechanisms is dominant depends on the age/demographic group in question
+and the societal context (Twenge, 2019).
 
-While our sample was randomly selected, the sampling frame was based
-only on Internet users that Qualtrics can access. Qualtrics recruits
-their frame subjects through online advertising on websites such as
-local portals, search engines, social networking services, and/or online
-shopping services. We do not contend that our sample is representative
-of the Chinese population, as the method of obtaining respondents
-obviously greatly limits those citizens with little or no access to the
-Internet. That said, we are comfortable that our sample is generally
-representative of Chinese Internet users. Given that our research focus
-centers on Internet effects, it makes sense to have a large sample of
-Internet users. A sampling frame including the entire Chinese population
-did not make sense for this research. Half of the population do not
-regularly access the Internet according to World Bank and China Internet
-Network Information Center (CNNIC) data as of late 2015 when we
-conducted our survey. Using a sample of the entire population could
-potentially limit the degrees of freedom in our models and the marginals
-of nuanced measures of digital media use would likely become too small
-to have any value. Thus, the large sample of Internet users adds to our
-confidence in the inferences throughout the book.
+Most of the existing research on the subject focuses on Western highly
+developed societies, and this focus may limit variation on key
+independent variables given the similar social and institutional context
+in which users are embedded. To address this problem, this study aims to
+understand how these complex dynamics interact in the non-Western
+setting of China. Relatively little is known about China's level of
+social isolation, though what evidence that does exist suggests that it
+is on the rise. Twenge et al.'s study found that adolescent feelings of
+loneliness have generally been on the rise in comparable East Asian
+countries (Twenge et al., 2021). News reports have highlighted the
+increasing number of people who consider themselves to be online
+outcasts or losers (\emph{diaosi}) (China{'}s latest social media trend:
+Diaosi / loser subculture, 2016; Nan, 2013; Szablewicz, 2014). We do not
+aim to make a direct comparison between China and Western countries but
+rather highlight the way in which China's unique context helps shed
+light on which contextual factors matter in understanding the linkage
+between the two variables.
+
+The most important of these contextual factor in China is that social
+media space that is highly controlled online environment. Many people
+are aware that the Chinese government heavily censors politically
+sensitive content on online platforms. However, fewer are aware that the
+Chinese government spends as much, if not more, effort to clean up
+non-political as negative or distressing content on the Chinese
+internet, such as scams, instances of cyber bullying, disturbing videos,
+and vulgar content (Wang, 2020). This control impulse also extends
+content the government views as spiritually polluting, such as
+pornography, scantily dressed women, and other escapist content. While
+the Chinese government and online platforms are not 100 per cent
+effective in their ability to completely stamp out such content, the
+default is that such content is actively restricted, while US platforms
+tent to take a more pro-speech regulatory position (Liu and Yang, 2022).
+If one of the main mechanisms through which social media promotes social
+isolation occurs is exposure to negative content, then this highly
+regulated online environment should lead to a weaker relationship
+between social media use and isolation. Suggestive of this is a a study
+by Liu and Liu that finds Chinese who consumed more commercialized and
+sensationalized media reported more trauma during the first COVID-19
+outbreak in China than those who followed government sources (Liu and
+Liu, 2020).
+
+On the other hand, China also has a highly robust online influencer
+culture. While social media influencers are a global phenomena, China
+has perhaps the most commercialized version of influencing. Social media
+influencers are developed by large agencies and work in an almost
+assembly-line fashion to promote products on livestreams or pitch
+sponsor products. In this influencer culture, less attention is paid to
+authenticity and personality and relatively more emphasis is placed on
+consumerism, brand promotion, and image (Tam, 2019; Wei, 2023). Given
+that previous research has suggested one of the main channels through
+which social media creates feelings of isolation is negative personal
+comparisons with online content (so-called ``FOMO'' - fear of missing
+out), heavy social media use may increase the strength of the
+relationship between social media use and social isolation through
+consumption of such highly commercialized content.
+
+Additionally, China's social media environment is relatively unique in
+that the dominant messaging platform is also the largest social media
+app (WeChat). Users can use it simply to chat with family and friends,
+they can use it to post photos and other content about their life in a
+feed that works similarly to Facebook, or they can browse videos of
+others in a method similar to Tiktok. Previous research has indicated
+that while, on the whole, social media increases social isolation, for
+users that primarily use it to contact friends and family, its use can
+counteract the negative effects (Hajek and König, 2019; Lim et al.,
+2020). In this way, those that heavily use these type of combined
+platforms may engage in multiple uses of social media that tend to
+cancel each other out. Given the ubiquity of WeChat in China, such a
+relationship seems plausible.
+
+Finally, the nexus of social isolation and social media use in China has
+played out in the context of one of the most rapid periods of
+urbanization in human history. Hundreds of millions of people have
+shifted from rural subsistence farming to participating in an urban
+market economy. The existing literature finds that urbanicity is an
+important factor in levels and mechanisms for social isolation; many
+studies of Western societies have found that rural residents, while
+having stronger familial bonds, also can more easily experience social
+isolation without those bonds (Henning-Smith et al., 2018; Kaye, 2017;
+Koning et al., 2017). In China, less is known about the differential
+effects of the urban rural divide on feelings of social isolation but
+the research that does exist suggests that urban environments can be
+especially isolating, particularly for rural to urban migrants
+particularly due to lack of access to traditional support systems and
+familial connections (Li and Rose, 2017).
+
+Given the existing literature and the context of China, this leads to a
+series of testable hypotheses.
+
+\begin{itemize}
+\item
+  \textbf{H1a:} social media use should have a weak or possibly positive
+  connection to social isolation due to strengthened government control
+  over online content
+\item
+  \textbf{H1b:} social media use should have a negative connection to
+  social isolation due to the dominance of influencer culture in China
+\item
+  \textbf{H2:} those who are able to use social media to make new
+  friends will have lower social isolation scores than those who do not
+\item
+  \textbf{H3:} the urban/rural divide will produce differential impacts
+  in the above hypotheses on the relationship between social media use
+  and social isolation
+\end{itemize}
+
+\hypertarget{data-measurement-and-descriptives}{%
+\subsection{Data, Measurement, and
+Descriptives}\label{data-measurement-and-descriptives}}
+
+The data used in this study are original. We designed a survey
+instrument in English, and translated it into Chinese, to measure a
+range of concepts including social isolationism and various dimensions
+of social media and digital information consumption. We employed
+Qualtrics to collect the data. They randomly selected 2292 respondents
+from their existing panel\footnote{Qualtrics recruits a large pool of
+  respondents for various survey projects through online advertising.
+  Recruits who update their profiles at least once every 6 months are
+  randomly invited to participate. These recruits are awarded online
+  points that can be exchanged for cash or various other
+  country-specific gifts. The number of points is based on the length of
+  the survey, and since our survey had over fifty questions, respondents
+  received a relatively high number of points.} from November 25 to
+December 2, 2015. This sample size on provides for a roughly \(\pm2\)
+margin of error.\footnote{We were able to first collect a small sample
+  (\(n=286\)) to check the reliability and adjust the instrument after
+  before proceeding with the final data collection. We made three
+  adjustments, none of which are related to the measures used in the
+  current study.}
+
+Our dependent variable, \emph{social isolationism}, is a three-item
+additive index. Respondents were given the following introduction: The
+next question is about how you feel about different aspects of your
+life. Could you tell me for each one if you feel that way always, almost
+always, some of the time, rarely or never? Then they were asked: A) How
+often do you feel that you lack companionship, B) How often do you feel
+isolated from others?, and C) How often do you feel left out? Response
+options were recoded so that higher responses equated to feeling more
+socially isolated, they were all three added together, and then rescaled
+to range from 0 through 1 maintaining the original intervals
+(\(\alpha = 0.86\)). The distribution of that index is presented in
+Figure~\ref{fig-social-iso-dist}. The distribution is relatively normal
+centered around the midpoint with a slight skew to the right. Most
+respondents appear to be on the low end, indicating the the majority of
+those in our sample do not feel particularly isolated. Conversely, the
+right skew in the distribution does suggest that a sizable chunk of
+folks feel quite socially isolated. Altogether, the spread out
+distribution indicates quite a bit of variance (\(\mu = 0.41\),
+\(sd = 0.20\)).
+
+\begin{figure}
+
+{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-social-iso-dist-1.pdf}
+
+}
+
+\caption{\label{fig-social-iso-dist}Distribution of Social Isolationism
+Index}
+
+\end{figure}
+
+We have several primary independent variables including human
+interaction, online to offline relationships, general social media use,
+and urbanicity. We measured human interaction with a single item: ``Has
+the internet and phone applications increased your contact with the
+following groups of people (check yes to all that apply)?'' The response
+options were: 1) Family that lives nearby, 2) Family that lives far
+away, 3) Friends that live nearby, 4) Friends that live far away, 5)
+People you met on the internet that live nearby, and 6) People you met
+on the internet that live far away. We simply counted the number of
+selected responses so the item ranged from 0 to 6, and then for the
+models that come later, we rescaled it to range from 0 through 1
+maintaining the original intervals. Online to offline relationships was
+also measured with a single item: Have you met someone offline that you
+initially met online? Response options were: 1) Yes, many times, 2) Yes,
+several times, 3) Yes, once, and 4) No, never. We inverted this scale so
+that higher values represented more offline relationships, and again,
+rescaled it to range from 0 through 1 for the models that follow.
+
+The distributions of these ordinal independent variables are reflected
+in Figure~\ref{fig-var-dist}. Very few people claimed to never have
+increased their contact/connections with others through the internet.
+The modal number of increased connections respondents claimed to have
+made through the internet was 2, followed closely by 1, but a sizable
+proportion of the sample, about 48\% claimed to have increased their
+number of personal connections by 3 or more through the internet.
+Perhaps not surprisingly, the modal response when asked whether one had
+met someone online and that relationship moved offline was ``No,
+never''. On the other hand, we were surprised that about 37\% of those
+sampled claimed to have moved relationships offline several times, over
+10\% said they had done so many times, and about 13\% did so once. Taken
+altogether, a large proportion of our respondents seem to using the
+internet to facilitate social relations.
+
+\begin{figure}
+
+{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-var-dist-1.pdf}
+
+}
+
+\caption{\label{fig-var-dist}Primary Independent Variables
+Distributions}
+
+\end{figure}
+
+We measured general social media use with an index based on the
+following three items: 1) About how many hours a day would you estimate
+you spend using only social media? Social media means applications like
+Weibo, QQ, Renren, Kaixin001, Douban, WeChat or other sites and services
+that allow users to interact with each other. (0-1, 1-2, 2-3, 3-4, 4-5,
+5-6, 6-7, 7-8, 8-9, or More than 9), 2) Do you check email, read
+websites, and use social media (social media means applications like
+Weibo, QQ, Renren, Kaixin001, Douban, WeChat or other sites and services
+that allow users to interact with each other) more than you did five
+years ago? (Yes, No), and 3) How often do you read news stories about
+political events that have been posted on social media (social media
+means applications like Weibo, QQ, Renren, Kaixin001, Douban, WeChat or
+other sites and services that allow users to interact with each other)?
+(More than once a day, Everyday, Three-to-five days per week, One-to-two
+days per week, Less often, Never). Each was recoded so that higher
+values represented more social media use, rescaled to range from 0
+through 1, added together, and then again, rescaled to range from 0
+through 1 maintaining all original intervals. The distribution of this
+index is presented in Figure~\ref{fig-sm-use-dist}. The distribution is
+relatively normal and tightly centered around the mean 0.63 with a
+standard deviation of 0.17, but there is a left skew suggesting that a
+portion of the population is not that social media active, but clearly
+the bulk of the population are.
+
+\begin{figure}
+
+{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-sm-use-dist-1.pdf}
+
+}
+
+\caption{\label{fig-sm-use-dist}General Social Media Use Distribution}
+
+\end{figure}
+
+Our final primary independent variable, urbanicity, was measured using a
+single item: Which of these best describes the place in which you live?
+(Countryside/Village, Small City, Mid-Sized City, Suburban Area of a Big
+City, Big City). For the purpose of the models, we rescaled this item to
+range from 0 through 1 maintaining the original intervals. The
+distribution is reflected in Figure~\ref{fig-urban-dist}. Given the
+rural to urban Chinese migration since the founding of the People's
+Republic (Xia, 1995), it is not surprising to see that nearly 45\% of
+those in our sample live in cities, 7\% in suburbs, and about 27\% in
+mid-sized cities. About 16\% say they live in small cities and only
+about 5\% say they live in villages.
+
+\begin{figure}
+
+{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-urban-dist-1.pdf}
+
+}
+
+\caption{\label{fig-urban-dist}Urbanicity Distribution}
+
+\end{figure}
+
+Our modeling strategy that follows is straightforward. We begin by
+modeling each of our internet communication independent variables as
+function of socio-economic status (SES), gender, Chinese Communist Party
+membership (CCP), and age to create an individual profile of each type
+of digital user (see the Online Appendix for the operationalization of
+these variables). This provides some context for the models that follow
+which are intended to test our primary hypotheses, that is that internet
+communication can deter social isolation and that this is particularly
+true for those who do not have the convenience of the high social
+interaction opportunity provided by urban living. For those we begin by
+fitting an additive model of our index of social isolationism as
+function of each of our primary independent variables while also
+controlling for the same variables included in our profile models.
+Finally, we refit three models with the same specification but introduce
+an interactive term between each of our internet communication
+indicators, respectively, with our measure of urbanicity. This allows us
+to test whether the observed additive effects are stronger for those
+living outside cities.
+
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
+
+Given that the first two dependent variables (human interaction, online
+to offline to offline relationships) in our profile models are
+distributed ordinally, we initially estimate linear models of those
+outcomes and examine the residual behavior to determine if a linear
+model fits the data well or if an ordered outcome model is a better fit.
+The results were clear, a linear model is not a good fit for either
+outcome (see the figures in the Online Appendix), so we fit the models
+using ordered logit. Because our measure of general social media is
+based on an additive index, we treat it as continuous, and accordingly
+fit a linear model.
+
+\hypertarget{tbl-profile-models}{}
+\begin{table}
+\caption{\label{tbl-profile-models}Modeling Profiles of Digital Communication }\tabularnewline
+
+\centering
+\begin{threeparttable}
+\begin{tabular}[t]{lccc}
+\toprule
+  & Human Interaction & Online/Offline Interaction & General Social Media\\
+\midrule
+SES & \num{2.35}* & \num{2.16}* & \num{0.24}*\\
+ & (\num{0.27}) & (\num{0.28}) & (\num{0.03})\\
+Female & \num{-0.03} & \num{-0.35}* & \num{0.01}\\
+ & (\num{0.08}) & (\num{0.08}) & (\num{0.01})\\
+CCP Member & \num{-0.17} & \num{0.23}* & \num{0.01}\\
+ & (\num{0.09}) & (\num{0.09}) & (\num{0.01})\\
+Age & \num{0.51}* & \num{-0.82}* & \num{-0.12}*\\
+ & (\num{0.26}) & (\num{0.27}) & (\num{0.02})\\
+\midrule
+N & \num{2277} & \num{2276} & \num{2198}\\
+Pseudo R2 & \num{0.07} & \num{0.05} & \\
+R2 &  &  & \num{0.05}\\
+\bottomrule
+\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.05}\\
+\end{tabular}
+\begin{tablenotes}
+\item \textit{Note: } 
+\item Human Interaction and Offline/Online Relationships estimates are derived from ordered logit and General Social Media from ordinary least squares.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+The results of our profile models are presented in
+Table~\ref{tbl-profile-models}. When it comes to SES, the relationship
+across all three of our internet communication is consistent. As SES
+goes up so does digital human interaction, the move from online to
+offline relationships, and general social media use. That gender is only
+statistically significant in the model of the move from online to
+offline relationships where women are less likely to do so.
+Interestingly, being a CCP member has inverse relationships with human
+interaction and the move from online to offline, where members are less
+likely to increase digital human interaction but are more likely to move
+online relationships offline. Finally, the older respondents were the
+more likely they were to increase human interaction, and the less likely
+they were to move relationships offline and use social media. These
+profile results provide background context for the models that follow.
+The internet communication indicators are our primary independent
+variables, so these profile models give us a sense for whom they matter
+the most when it comes to deterring social isolation.
+
+\hypertarget{tbl-social-isolation-models}{}
+\begin{table}
+\caption{\label{tbl-social-isolation-models}Modeling Social Isolation }\tabularnewline
+
+\centering
+\begin{threeparttable}
+\begin{tabular}[t]{lcccc}
+\toprule
+  & (1) & (2) & (3) & (4)\\
+\midrule
+Human Interaction & \num{-0.14}* & \num{-0.04} & \num{-0.14}* & \num{-0.14}*\\
+ & (\num{0.02}) & (\num{0.04}) & (\num{0.02}) & (\num{0.02})\\
+Online-Offline & \num{0.07}* & \num{0.07}* & \num{0.15}* & \num{0.07}*\\
+ & (\num{0.01}) & (\num{0.01}) & (\num{0.03}) & (\num{0.01})\\
+Social Media & \num{0.05}* & \num{0.05}* & \num{0.05}* & \num{0.13}*\\
+ & (\num{0.03}) & (\num{0.02}) & (\num{0.02}) & (\num{0.05})\\
+Urbanicity & \num{-0.04}* & \num{0.02} & \num{0.01} & \num{0.04}\\
+ & (\num{0.01}) & (\num{0.03}) & (\num{0.02}) & (\num{0.05})\\
+SES & \num{-0.04} & \num{-0.04} & \num{-0.04} & \num{-0.04}\\
+ & (\num{0.03}) & (\num{0.03}) & (\num{0.03}) & \vphantom{1} (\num{0.03})\\
+Female & \num{0.02}* & \num{0.02}* & \num{0.02}* & \num{0.02}*\\
+ & (\num{0.01}) & (\num{0.01}) & (\num{0.01}) & \vphantom{1} (\num{0.01})\\
+CCP Member & \num{0.00} & \num{0.00} & \num{0.00} & \num{0.00}\\
+ & (\num{0.01}) & (\num{0.01}) & (\num{0.01}) & (\num{0.01})\\
+Age & \num{-0.19}* & \num{-0.20}* & \num{-0.20}* & \num{-0.20}*\\
+ & (\num{0.03}) & (\num{0.03}) & (\num{0.03}) & (\num{0.03})\\
+Human Interaction*Urbanicity &  & \num{-0.14}* &  & \\
+ &  & (\num{0.05}) &  & \\
+Online-Offline*Urbanicity &  &  & \num{-0.12}* & \\
+ &  &  & (\num{0.03}) & \\
+Social Media*Urbanicity &  &  &  & \num{-0.13}\\
+ &  &  &  & (\num{0.07})\\
+\midrule
+N & \num{2173} & \num{2173} & \num{2173} & \num{2173}\\
+R2 & \num{0.08} & \num{0.08} & \num{0.09} & \num{0.08}\\
+\bottomrule
+\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05}\\
+\end{tabular}
+\begin{tablenotes}
+\item \textit{Note: } 
+\item Estimates are derived using ordinary least squares
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+The results of our models of social isolation are presented in
+Table~\ref{tbl-social-isolation-models}. The additive estimates in model
+(1) provide mixed results regarding whether internet communication is a
+positive force in deterring social isolation. Not surprisingly, there is
+a negative relationship between the number of digital connections (human
+interaction) folks make and feelings of social isolation. On the other
+hand, though, both moving online relationships offline and general
+social media use are positively related to feelings of social isolation.
+The latter is consistent with much of the literature outlined above, but
+the former is not. Perhaps, this is context driven. The results also
+indicate that those living in more urban environments tend to feel less
+socially isolated.
+
+Models (2) - (4) in Table 2 include each of the interactions between our
+three internet communication measures and urbanicity. The consistent
+result across the interactions is that the relationships are dulled for
+those living in more rural areas. The interaction between digital humna
+interaction and urbanicity is statistically significant (\(p < 0.01\)),
+as is that between the move from online to offline relationships and
+urbanicity (\(p < 0.001\)), and that between general social media use
+and urbanicity only slightly misses the arbitrary \(0.05\) threshold
+(\(p = 0.07\)). The interactions are most easily interpreted graphically
+(see Figure~\ref{fig-social-isolation-interactions}).
+
+\begin{figure}
+
+{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-social-isolation-interactions-1.pdf}
+
+}
+
+\caption{\label{fig-social-isolation-interactions}Modeling Social
+Isolation: Interaction Results}
+
+\end{figure}
+
+The model (2) results are graphed in the upper left hand figure. Here it
+is clear that the negative relationship between digital human
+interaction and feelings of social isolation is considerably stronger
+for those in cities. For that matter, notice that the relationship for
+those in villages is basically flat; the 95 percent confidence interval
+around the slight negative slope indicates that the relationship could
+be flat.
+
+The results from the interaction between online to offline relationships
+and urbanicity are displayed in the graph in the upper right hand corner
+of Figure 5. Again, here, the main effects run in the opposite direction
+than those of digital human interaction. Those who are more likely to
+move relationships from online to offline tend to feel more isolated,
+and the interactive results presented here suggest that this relations
+is stronger for those living in less urban spaces. Likewise, the same is
+the case for those using social media more frequently. In fact, the
+relationship here for those living in the largest cities is completely
+non-existent.
+
+In terms of our original hypotheses, we find support for the idea that
+China's social media environment is not particularly unique with respect
+to generating feelings of social isolation (\textbf{H1b}). Whether or
+not this is due to the influencer culture or other factors, we cannot
+say with our data but it at least does suggest that greater content
+regulation is not likely to moderate the amount of isolation that social
+media produces. We also find, as has been found in other studies, that
+users who use the internet to create new connections are less likely to
+feel isolated (\textbf{H2}). However, this does not seem to extend to
+those that use the internet to facilitate offline meetups. Finally, we
+find that the impact of the internet and social media vary significantly
+according to the level of urbanicity (\textbf{H3}) - this matches with
+previous findings that suggest that there is significant heterogeneity
+in the impact of social media on social isloation. All of these findings
+are generally in line with previous research on the subject, suggesting
+that the mechanisms that generate feelings of social isolation are
+universal and not so sensitive to different social and governing
+contexts.
+
+\hypertarget{conclusion}{%
+\subsection{Conclusion}\label{conclusion}}
+
+Cyberoptimists heralded the internet as means by which people could
+connect, build social capital, and some suggested this could deter
+social isolationism. Our results provide little evidence of this
+optimistic view of the internet and its ability to improve the quality
+of people's lives. We do find that some are more likely to interact with
+family and friends and that this does deter feelings of social
+isolation, but on the other hand, even though many move online
+relationships offline and connect through social media, doing so does
+not deter feelings of social isolation. Instead, such digital actively
+is actually associated with increased feelings of social isolation.
+
+We also found no evidence that the internet could serve as bridge to
+build connections for those living outside of cities. The optimistic
+view here would be that the internet could lower the costs of making
+connections for those who have less social opportunity, those living in
+less populated areas, and as a result, help them to feel less isolated.
+We, in fact, found the opposite. Internet communication had either less
+positive effect or more negative effect on feelings of social isolation
+for those living in less urban spaces.
+
+Our contribution here is that we look at some well-established
+theoretical arguments in a context outside that of where most of the
+research centered on these type questions has examined. While our study
+is far from the last word on the subject, these results suggest that the
+mechanisms that link social media use and social isolation are
+relatively consistent across countries.
+
+\newpage{}
+
+\hypertarget{references}{%
+\subsection{References}\label{references}}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-ademiluyi2022}{}}%
+Ademiluyi A, Li C and Park A (2022)
+\href{https://doi.org/10.2196/30286}{Implications and Preventions of
+Cyberbullying and Social Exclusion in Social Media: Systematic Review}.
+\emph{JMIR Formative Research} 6(1): e30286.
+
+\leavevmode\vadjust pre{\hypertarget{ref-alabri2022}{}}%
+Alabri A (2022) \href{https://doi.org/10.1155/2022/4824256}{Fear of
+Missing Out (FOMO): The Effects of the Need to Belong, Perceived
+Centrality, and Fear of Social Exclusion}. \emph{Human Behavior and
+Emerging Technologies} 2022: e4824256.
+
+\leavevmode\vadjust pre{\hypertarget{ref-appel2020}{}}%
+Appel M, Marker C and Gnambs T (2020)
+\href{https://doi.org/10.1177/1089268019880891}{Are Social Media Ruining
+Our Lives? A Review of Meta-Analytic Evidence}. \emph{Review of General
+Psychology} 24(1): 60--74.
+
+\leavevmode\vadjust pre{\hypertarget{ref-beyens2020}{}}%
+Beyens I, Pouwels JL, Driel II van, et al. (2020)
+\href{https://doi.org/10.1038/s41598-020-67727-7}{The effect of social
+media on well-being differs from adolescent to adolescent}.
+\emph{Scientific Reports} 10(1): 10763.
+
+\leavevmode\vadjust pre{\hypertarget{ref-buxfcttner2022}{}}%
+Büttner CM and Rudert SC (2022)
+\href{https://doi.org/10.1016/j.chb.2021.107062}{Why didn't you tag
+me?!: Social exclusion from Instagram posts hurts, especially those with
+a high need to belong}. \emph{Computers in Human Behavior} 127: 107062.
+
+\leavevmode\vadjust pre{\hypertarget{ref-chinas2016}{}}%
+China{'}s latest social media trend: Diaosi / loser subculture (2016).
+Available at:
+\url{https://www.appnova.com/chinas-latest-social-media-trend-diaosi-loser-subculture/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ellison2007}{}}%
+Ellison NB, Steinfield C and Lampe C (2007)
+\href{https://doi.org/10.1111/j.1083-6101.2007.00367.x}{The Benefits of
+Facebook {``}Friends:{''} Social Capital and College Students{'} Use of
+Online Social Network Sites}. \emph{Journal of Computer-Mediated
+Communication} 12(4): 1143--1168.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hajek2019}{}}%
+Hajek A and König H-H (2019)
+\href{https://doi.org/10.1186/s12889-018-6369-6}{The association between
+use of online social networks sites and perceived social isolation among
+individuals in the second half of life: results based on a nationally
+representative sample in Germany}. \emph{BMC Public Health} 19(1): 40.
+
+\leavevmode\vadjust pre{\hypertarget{ref-henning-smith2018}{}}%
+Henning-Smith C, Ecklund A and Kozhimannil K (2018)
+\href{https://doi.org/10.1093/geroni/igy023.2851}{RURAL-URBAN
+DIFFERENCES IN SOCIAL ISOLATION AND ITS RELATIONSHIP TO HEALTH}.
+\emph{Innovation in Aging} 2(Suppl 1): 770.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kaye2017}{}}%
+Kaye LW (2017) \href{https://doi.org/10.1093/ppar/prx029}{Older adults,
+rural living, and the escalating risk of social isolation}. \emph{Public
+Policy \& Aging Report} 27(4): 139--144.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kim2017}{}}%
+Kim HH (2017) \href{https://doi.org/10.1080/02673843.2016.1197135}{The
+impact of online social networking on adolescent psychological
+well-being (WB): A population-level analysis of korean school-aged
+children}. \emph{International Journal of Adolescence and Youth} 22(3):
+364--376.
+
+\leavevmode\vadjust pre{\hypertarget{ref-koning2017}{}}%
+Koning JLD, Stathi A and Richards S (2017)
+\href{https://doi.org/10.1017/S0144686X16000696}{Predictors of
+loneliness and different types of social isolation of rural-living older
+adults in the United Kingdom}. \emph{Ageing \& Society} 37(10):
+2012--2043.
+
+\leavevmode\vadjust pre{\hypertarget{ref-larson2018}{}}%
+Larson LR, Szczytko R, Bowers EP, et al. (2018) Outdoor Time, Screen
+Time, and Connection to Nature: Troubling Trends Among Rural Youth?
+\emph{Environment and Behavior}. Epub ahead of print 20 October 2018.
+DOI:
+\href{https://doi.org/10.1177/0013916518806686}{10.1177/0013916518806686}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-li2017}{}}%
+Li J and Rose N (2017)
+\href{https://doi.org/10.1016/j.healthplace.2017.08.009}{Urban social
+exclusion and mental health of China's rural-urban migrants
+{\textendash} A review and call for research}. \emph{Health \& Place}
+48: 20--30.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lim2020}{}}%
+Lim MH, Eres R and Vasan S (2020)
+\href{https://doi.org/10.1007/s00127-020-01889-7}{Understanding
+loneliness in the twenty-first century: An update on correlates, risk
+factors, and potential solutions}. \emph{Social Psychiatry and
+Psychiatric Epidemiology} 55(7): 793--810.
+
+\leavevmode\vadjust pre{\hypertarget{ref-liu2020}{}}%
+Liu C and Liu Y (2020)
+\href{https://doi.org/10.3390/ijerph17134720}{Media Exposure and Anxiety
+during COVID-19: The Mediation Effect of Media Vicarious
+Traumatization}. \emph{International Journal of Environmental Research
+and Public Health} 17(13): 4720.
+
+\leavevmode\vadjust pre{\hypertarget{ref-liu2022}{}}%
+Liu J and Yang L (2022)
+\href{https://doi.org/10.1002/poi3.307}{{``}Dual-Track{''} platform
+governance on content: A comparative study between China and United
+States}. \emph{Policy \& Internet} 14(2): 304--323.
+
+\leavevmode\vadjust pre{\hypertarget{ref-nan2013}{}}%
+Nan W (2013)
+\href{https://www.scmp.com/news/china/article/1232976/chinas-underdog-youth-find-success-diaosi-or-loser-identity}{China's
+underdog youth find success in 'diaosi' - or 'loser' - identity}.
+\emph{South China Morning Post}. Epub ahead of print 8 May 2013.
+
+\leavevmode\vadjust pre{\hypertarget{ref-nowland2018}{}}%
+Nowland R, Necka EA and Cacioppo JT (2018)
+\href{https://doi.org/10.1177/1745691617713052}{Loneliness and Social
+Internet Use: Pathways to Reconnection in a Digital World?}
+\emph{Perspectives on Psychological Science} 13(1): 70--87.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ostic2021}{}}%
+Ostic D, Qalati SA, Barbosa B, et al. (2021)
+\href{https://www.frontiersin.org/articles/10.3389/fpsyg.2021.678766}{Effects
+of social media use on psychological well-being: A mediated model}.
+\emph{Frontiers in Psychology} 12.
+
+\leavevmode\vadjust pre{\hypertarget{ref-primack2017}{}}%
+Primack BA, Shensa A, Sidani JE, et al. (2017)
+\href{https://doi.org/10.1016/j.amepre.2017.01.010}{Social Media Use and
+Perceived Social Isolation Among Young Adults in the U.S.}
+\emph{American Journal of Preventive Medicine} 53(1): 1--8.
+
+\leavevmode\vadjust pre{\hypertarget{ref-steinfield2008}{}}%
+Steinfield C, Ellison NB and Lampe C (2008)
+\href{https://doi.org/10.1016/j.appdev.2008.07.002}{Social capital,
+self-esteem, and use of online social network sites: A longitudinal
+analysis}. \emph{Journal of Applied Developmental Psychology} 29(6).
+Social Networking on the Internet: 434--445.
+
+\leavevmode\vadjust pre{\hypertarget{ref-subrahmanyam2008}{}}%
+Subrahmanyam K, Reich SM, Waechter N, et al. (2008)
+\href{https://doi.org/10.1016/j.appdev.2008.07.003}{Online and offline
+social networks: Use of social networking sites by emerging adults}.
+\emph{Journal of Applied Developmental Psychology} 29(6). Social
+Networking on the Internet: 420--433.
+
+\leavevmode\vadjust pre{\hypertarget{ref-szablewicz2014}{}}%
+Szablewicz M (2014) \href{https://doi.org/10.1177/0920203X14531538}{The
+{`}losers{'} of China{'}s Internet: Memes as {`}structures of feeling{'}
+for disillusioned young netizens}. \emph{China Information} 28(2):
+259--275.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tam2019}{}}%
+Tam L (2019)
+\href{https://www.scmp.com/lifestyle/entertainment/article/2183174/trust-me-you-need-how-chinas-live-streaming-kol-stars-are}{The
+China fame factory training online influencers to sell}. \emph{South
+China Morning Post}. Epub ahead of print 24 January 2019.
+
+\leavevmode\vadjust pre{\hypertarget{ref-twenge2019}{}}%
+Twenge JM (2019) \href{https://doi.org/10.1177/0963721419838244}{More
+Time on Technology, Less Happiness? Associations Between Digital-Media
+Use and Psychological Well-Being}. \emph{Current Directions in
+Psychological Science} 28(4): 372--379.
+
+\leavevmode\vadjust pre{\hypertarget{ref-twenge2017}{}}%
+Twenge JM, Krizan Z and Hisler G (2017)
+\href{https://doi.org/10.1016/j.sleep.2017.08.013}{Decreases in
+self-reported sleep duration among U.S. adolescents
+2009{\textendash}2015 and association with new media screen time}.
+\emph{Sleep Medicine} 39: 47--53.
+
+\leavevmode\vadjust pre{\hypertarget{ref-twenge2021}{}}%
+Twenge JM, Haidt J, Blake AB, et al. (2021)
+\href{https://doi.org/10.1016/j.adolescence.2021.06.006}{Worldwide
+increases in adolescent loneliness}. \emph{Journal of Adolescence} 93:
+257--269.
+
+\leavevmode\vadjust pre{\hypertarget{ref-valkenburg2022}{}}%
+Valkenburg PM, Meier A and Beyens I (2022)
+\href{https://doi.org/10.1016/j.copsyc.2021.08.017}{Social media use and
+its impact on adolescent mental health: An umbrella review of the
+evidence}. \emph{Current Opinion in Psychology} 44: 58--68.
+
+\leavevmode\vadjust pre{\hypertarget{ref-wang2020}{}}%
+Wang J (2020) \emph{Regulation of digital media platforms: The case of
+china}. 6 November. Foundation for Law, Justice,; Society. Available at:
+\url{https://www.fljs.org/banning-regulating-tiktok-addressing-concerns-national-security-privacy-and-online-harms}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-wei2023}{}}%
+Wei AC (2023)
+\href{https://www.straitstimes.com/asia/east-asia/wang-hong-culture-booms-in-china-as-more-young-people-dream-of-becoming-influencers}{{`}Wang
+hong{'} culture booms in China as more young people dream of becoming
+influencers}. \emph{The Straits Times}. Epub ahead of print 27 May 2023.
+
+\leavevmode\vadjust pre{\hypertarget{ref-xia1995}{}}%
+Xia M (1995) Changes in the {Pattern} of {Migration} in {Urban} {China}.
+In: Day LH, Xia M, and Xia M (eds) \emph{Migration and {Urbanization} in
+{China}}. New York, NY: Routledge.
+
+\end{CSLReferences}
+
+\newpage{}
+
+\hypertarget{online-appendix}{%
+\subsection{Online Appendix}\label{online-appendix}}
+
+\hypertarget{variable-operationalization}{%
+\subsubsection{Variable
+Operationalization}\label{variable-operationalization}}
+
+SES is an additive index of these two questions regarding income and
+education. Each of the following questions were rescaled to range from 0
+through 1, then the two questions were summed, and then rescaled to
+range from 0 through 1 again.
+
+\begin{itemize}
+\item
+  Here is a table showing the range of monthly incomes that people have.
+  Which of the letters on this table best represents the total monthly
+  income of your household (after tax)?
+
+  \begin{itemize}
+  \item
+    0 - 3,000,
+  \item
+    3,000 - 6,000,
+  \item
+    6,000 - 10,000,
+  \item
+    10,000 - 15,000,
+  \item
+    15,000 - 25,000,
+  \item
+    25,000 - 40,000,
+  \item
+    More than 40,000
+  \end{itemize}
+\item
+  What is the highest level of education that you have obtained?
+
+  \begin{itemize}
+  \item
+    No formal education,
+  \item
+    Primary,
+  \item
+    Middle school,
+  \item
+    High school,
+  \item
+    University,
+  \item
+    Advanced Studies/Graduate School
+  \end{itemize}
+\end{itemize}
+
+Other important predictor variables are operationalized as follows:
+
+\begin{itemize}
+\item
+  Gender
+
+  \begin{itemize}
+  \item
+    0 = male,
+  \item
+    1 = female
+  \end{itemize}
+\item
+  Are you a member or probationary member of the CCP?
+
+  \begin{itemize}
+  \item
+    0 = no,
+  \item
+    1 = yes
+  \end{itemize}
+\item
+  How old are you? (rescaled to range from 0 through 1)
+\end{itemize}
+
+\newpage{}
+
+\hypertarget{residual-analysis}{%
+\subsubsection{Residual Analysis}\label{residual-analysis}}
+
+\begin{figure}
+
+{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-resids-human-1.pdf}
+
+}
+
+\caption{\label{fig-resids-human}Human Interaction Model Residuals}
+
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-resids-online-offline-1.pdf}
+
+}
+
+\caption{\label{fig-resids-online-offline}Online/Offline Model
+Residuals}
+
+\end{figure}
 

### 2023-08-31 sage/template.qmd
prep for journal submission

---
title: Sage Template
format:
  sage-pdf:
    keep-tex: true  
  sage-html: default
author:
  - name: Sarah Malloc
    affiliations:
      - name: An Organization
        department: The Department
        address: 1 Main St
        city: Boston
        country: USA
        postal-code: 02210-1022
      - A second affilication
    orcid: 0000-0000-0000-0000
    email: sm@example.org
    url: https://example.org/
  - name: Eliza Dealloc
    affiliations:
      - Another Affiliation
abstract: |
  This document is a template demonstrating the Sage format.
keywords: [template, demo]
bibliography: bibliography.bib  
---

## Introduction {#sec-intro}

*TODO* Create a template that demonstrates the appearance, formatting, layout, and functionality of your format. Learn more about journal formats at <https://quarto.org/docs/journals/>.

### 2023-10-08 Social Isolation in China.qmd
prepared for t and f submission

@@
 ---
-title: "The Spatial Relationship between Social Media, Digital Connectedness, and Social Isolation in China: Revisting Cyber-Optimism"
-
+title: "Lonely and online: an investigation of social media use and social isolation in China"
+format:
+  tandf-pdf:
+    keep-tex: true 
 date: '`r format(Sys.time(), "%B %d, %Y")`'
 abstract: "Early research and popular discourse on the promise of the internet's impact on social isolation was optimistic.
-Since these early predictions, research has become less positive, usually pointing to the negative role of social media.
-However, little is known about this relationship in highly controlled, autocratic social media environments.
-Using data from a nationwide survey of Chinese citizens, we do find that the more citizens digitally connect with others, the less personally isolated they feel.
-Conversely, though, the more likely people are to move relationships from online to offline, and the more they use social media, the more personally isolated they feel.
-We also find that this relationship interacts with urbanicity - being in rural areas tends to amplify the effect.
+Since these early predictions, research has become less positive, usually pointing to the negative role of social media, withn more recent studies focused on heterogeneous effects.
+Using data from a nationwide survey of Chinese citizens to gain leverage on this disagreement in the literature, our research finds support for those that have focused on heterogeneous effects - we find that urbancity is a key moderating variable.
+Additionally, our results lend support to a FOMO mechanism while they are not suggestive of a mechanism by which negative content is the channel through which social media generates feelings of social isolations.
 Overall, our findings suggest that institutional context may not play an important role in the social media - social isolation relationship."
-keywords: 
-  - Social Isolation
-  - Social Media
-  - Digital Communication
-  - China
-format: pdf
+keywords: [Social Isolation, Social Media, Digital Communication, China]
 execute: 
@@
 bibliography: references.bib
-csl: sage-harvard.csl
+csl: taylor-and-francis-apa.csl
+author:
+  - name: Jason Gainous
+    affiliations:
+      - name: University of Sharjah
+        department: Department of Mass Communication
+        city: Sharjah
+        country: United Arab Emirates
+    orcid: 0000-0002-3104-2313
+    email: jgainous@sharjah.ac.ae
+  - name: Andrew W. MacDonald
+    affiliations:
+      - name: Duke Kunshan University
+        department: Division of Social Sciences
+        city: Kunshan
+        country: China
+    orcid: 0000-0002-4695-1560
+    email: andrew.macdonald@dukekunshan.edu.cn
+    attributes:
+      corresponding: true
 ---
@@
 Early research suggested that the internet would build social capital, or an interconnectedness between people, and that social media platforms were the ultimate way to bring people together.
-Since then, research indicates that the effect may be the opposite among at least some part of the population.
-Social media may encourage social isolation, and ultimately, social media users may feel more disconnected from others than those who do not use social media.
-We know very little about this phenomenon in China.
-China presents an interesting case because the institutional structures, level of development and the cultural context are all quite different than the areas studied in most existing studies.
-This allows us to test whether such features moderate or exacerbate the relationship between social media use and social isolation.
-To fully test this theory, we employ a large survey of Chinese internet users and test a variety of regression specifications.[^1] The main result is that social media use is robustly negatively related to social isolation, though the nature of this relationship changes depending on the urbanicity of the respondent - being in a rural area amplifies this relationship.
+Since then, research on the subject has been decidedly more mixed.
+On one hand, some authors have found social media may encourage social isolation, and ultimately, social media users may feel more disconnected from others than those who do not use social media.
+On the other hand, others have found that there is only a minimal relationship between these two variables.
+More recent scholarship has suggested that social media may produce heterogeneous effects on individuals.
+This study uses the little-studied Chinese social media environment to try and gain leverage on this question - the Chinese online environment has certain features that should both moderate and exacerbate key causal pathways previously identified in the literature.
+To we employ a large survey of Chinese internet users and test a variety of regression specifications.[^1] The main result is that social media use is generally negatively related to social isolation, though the nature of this relationship changes depending on the urbanicity of the respondent - being in a rural area amplifies this relationship.
+This finding lends support both to the previous negative relationship findings and also reinforce the findings that emphasize heterogeneous effects.
 
@@
 
-The existing literature on social isolation and social media use generally finds a negative relationship between the two.
-However, there are some remaining questions regarding whether this relationship remains significant in different cultural and regulatory environments.
-Based on the existing literature, we then develop some testable hypotheses regarding how the relationship between usage and isolation may vary in the context of China.
-The result of these hypotheses tests will help to better understand the mechanism that links the two variables.
+The existing literature on social isolation and social media use generally finds a negative to null relationship between the two variables, while the most recent research has suggested that social media has heterogeneous effects.
+Based on this existing literature, we then develop some testable hypotheses regarding how the relationship between usage and isolation may vary in the context of China.
+The result of these hypotheses tests will help to better understand the possible mechanism that links these two variables.
 
@@
 Many people are aware that the Chinese government heavily censors politically sensitive content on online platforms.
-However, fewer are aware that the Chinese government spends as much, if not more, effort to clean up non-political as negative or distressing content on the Chinese internet, such as scams, instances of cyber bullying, disturbing videos, and vulgar content [@wang2020].
+Fewer are aware that the Chinese government spends as much, if not more, effort to clean up non-political negative or distressing content on the Chinese internet, such as scams, instances of cyber bullying, disturbing videos, and vulgar content [@wang2020].
 This control impulse also extends content the government views as spiritually polluting, such as pornography, scantily dressed women, and other escapist content.
@@
 While social media influencers are a global phenomena, China has perhaps the most commercialized version of influencing.
-Social media influencers are developed by large agencies and work in an almost assembly-line fashion to promote products on livestreams or pitch sponsor products.
+Social media influencers are developed by large agencies and work in an almost assembly-line fashion to promote products on livestreams or pitch sponsored products.
 In this influencer culture, less attention is paid to authenticity and personality and relatively more emphasis is placed on consumerism, brand promotion, and image [@tam2019; @wei2023].
 Given that previous research has suggested one of the main channels through which social media creates feelings of isolation is negative personal comparisons with online content (so-called "FOMO" - fear of missing out), heavy social media use may increase the strength of the relationship between social media use and social isolation through consumption of such highly commercialized content.
+These influencers are most popular among young consumers so one may expect that only younger users would experience these effects.
 
@@
 
--   **H1b:** social media use should have a negative connection to social isolation due to the dominance of influencer culture in China
+-   **H1b:** social media use should have a strongly negative connection to social isolation due to the dominance of influencer culture in China, possibly moderated by age.
 
@@
 The latter is consistent with much of the literature outlined above, but the former is not.
-Perhaps, this is context driven.
 The results also indicate that those living in more urban environments tend to feel less socially isolated.
@@
 In terms of our original hypotheses, we find support for the idea that China's social media environment is not particularly unique with respect to generating feelings of social isolation (**H1b**).
-Whether or not this is due to the influencer culture or other factors, we cannot say with our data but it at least does suggest that greater content regulation is not likely to moderate the amount of isolation that social media produces.
+Whether or not this is due to the influencer culture or other factors, we cannot say with our data, however age is a consistently negative predictor of social isolation even when controlling for amount of social media use.
+This result is at least suggestive of the negative online influencer culture.
 We also find, as has been found in other studies, that users who use the internet to create new connections are less likely to feel isolated (**H2**).
@@
 Finally, we find that the impact of the internet and social media vary significantly according to the level of urbanicity (**H3**) - this matches with previous findings that suggest that there is significant heterogeneity in the impact of social media on social isloation.
-All of these findings are generally in line with previous research on the subject, suggesting that the mechanisms that generate feelings of social isolation are universal and not so sensitive to different social and governing contexts.
 
@@
 Cyberoptimists heralded the internet as means by which people could connect, build social capital, and some suggested this could deter social isolationism.
-Our results provide little evidence of this optimistic view of the internet and its ability to improve the quality of people's lives.
-We do find that some are more likely to interact with family and friends and that this does deter feelings of social isolation, but on the other hand, even though many move online relationships offline and connect through social media, doing so does not deter feelings of social isolation.
-Instead, such digital actively is actually associated with increased feelings of social isolation.
+On the other hand, more recent research and popular media coverage of the subject has presented a deeply negative view of the role of social media.
+Our results do lean toward supporting the negative conclusions but add important contextualization and are suggestive of which of the hypothesized mechanisms are most relevant.
 
-We also found no evidence that the internet could serve as bridge to build connections for those living outside of cities.
-The optimistic view here would be that the internet could lower the costs of making connections for those who have less social opportunity, those living in less populated areas, and as a result, help them to feel less isolated.
+Firstly, we found no evidence that the internet could serve as bridge to build connections for those living outside of cities.
+The optimistic view that internet use could lower the costs of making connections for those who have less social opportunity, those living in less populated areas, and as a result, help them to feel less isolated.
 We, in fact, found the opposite.
 Internet communication had either less positive effect or more negative effect on feelings of social isolation for those living in less urban spaces.
+This finding lends support to the FOMO channel - viewing lots of content from influencers in a rural area compounds feelings of isolation.
 
-Our contribution here is that we look at some well-established theoretical arguments in a context outside that of where most of the research centered on these type questions has examined.
-While our study is far from the last word on the subject, these results suggest that the mechanisms that link social media use and social isolation are relatively consistent across countries.
+Additionally, given the robustly negative relationship between social media use and social isolation even in the context of China's highly policed internet, our results cast some doubt on theories that suggest it is the negative content, such as cyberbullying or violent/graphic posts, that drives the relationship.
+Finally, our results also further suggest more work needs to be done in identifying important hetergeneous effects - in our results, those living in a big city experienced almost no change in social isolation as social media use increased while the relationship becomes increasingly negative by ruralness.
+This specific heterogeneous effect may be unique to China but the strength of it suggests that important inter-personal factors may be relevant in other contexts.
+
+While our study is far from the last word on the subject, we hope this paper further helps move researchers away from considering the binary question of whether social media use has a negative relationship with social isolation to more productively considering the contextual and personal attributes that moderate and mediate this relationship.
 

### 2023-10-08 tandf/Social Isolation in China.qmd
prepared for t and f submission

--- 2023-10-08 Social Isolation in China.qmd
@@
 title: "Lonely and online: an investigation of social media use and social isolation in China"
-format:
-  tandf-pdf:
-    keep-tex: true 
 date: '`r format(Sys.time(), "%B %d, %Y")`'
@@
 keywords: [Social Isolation, Social Media, Digital Communication, China]
+format:
+  tandf-pdf:
+    keep-tex: true 
 execute: 

### 2023-10-08 tandf/Social-Isolation-in-China.tex
prepared for t and f submission

--- 2023-08-31 Social-Isolation-in-China.tex
@@
 %
-\documentclass[
-  letterpaper,
-  DIV=11,
-  numbers=noendperiod]{scrartcl}
+\documentclass[]{interact}
+
+\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
+\usepackage[caption=false]{subfig}% Support for small, `sub' figures and tables
+
+\usepackage[natbibapa,nodoi]{apacite}% Citation support using apacite.sty. Commands using natbib.sty MUST be deactivated first!
+\setlength\bibhang{12pt}% To set the indentation in the list of references using apacite.sty. Commands using natbib.sty MUST be deactivated first!
+\renewcommand\bibliographytypesize{\fontsize{10}{12}\selectfont}% To set the list of references in 10 point font using apacite.sty. Commands using natbib.sty MUST be deactivated first!
+
+\let\subcaption\relax
+\let\subfloat\relax
+
+\theoremstyle{plain}% Theorem-like structures provided by amsthm.sty
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{proposition}[theorem]{Proposition}
+
+\theoremstyle{definition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{example}[theorem]{Example}
+
+\theoremstyle{remark}
+\newtheorem{remark}{Remark}
+\newtheorem{notation}{Notation}
 
@@
 \setlength{\emergencystretch}{3em} % prevent overfull lines
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\setcounter{secnumdepth}{5}
 % Make \paragraph and \subparagraph free-standing
@@
 
-\KOMAoption{captions}{tableheading}
 \makeatletter
@@
 \hypersetup{
-  pdftitle={The Spatial Relationship between Social Media, Digital Connectedness, and Social Isolation in China: Revisting Cyber-Optimism},
+  pdftitle={Lonely and online: an investigation of social media use and social isolation in China},
+  pdfauthor={Jason Gainous; Andrew W. MacDonald},
   pdfkeywords={Social Isolation, Social Media, Digital
@@
 
-\title{The Spatial Relationship between Social Media, Digital
-Connectedness, and Social Isolation in China: Revisting Cyber-Optimism}
-\author{}
-\date{2023-08-31}
-
 \begin{document}
+\title{Lonely and online: an investigation of social media use and
+social isolation in China}
+
+\author{\name{Jason Gainous\textsuperscript{a} and Andrew W.
+MacDonald\textsuperscript{b}\thanks{CONTACT Andrew W.
+MacDonald. Email: andrew.macdonald@dukekunshan.edu.cn}}
+\affil{\textsuperscript{a}Department of Mass Communication, University
+of Sharjah, Sharjah, United Arab Emirates;
+\textsuperscript{b}Division of Social Sciences, Duke Kunshan
+University, Kunshan, China}}
+
+%\author[1]{Jason Gainous%
+%%
+%}
+% \ead{jgainous@sharjah.ac.ae} 
+%\author[2]{Andrew W. MacDonald%
+%\corref{cor1}%
+%}
+% \ead{andrew.macdonald@dukekunshan.edu.cn} 
+%
+
+%\author{
+%\name{A.~N. Author\textsuperscript{a}\thanks{CONTACT A.~N. Author. Email: latex.helpdesk@tandf.co.uk} and John Smith\textsuperscript{b}}
+%\affil{\textsuperscript{a}Taylor \& Francis, 4 Park Square, Milton Park, Abingdon, UK; \textsuperscript{b}Institut f\"{u}r Informatik, Albert-Ludwigs-Universit\"{a}t, Freiburg, Germany}
+%}
+
 \maketitle
+
 \begin{abstract}
@@
 predictions, research has become less positive, usually pointing to the
-negative role of social media. However, little is known about this
-relationship in highly controlled, autocratic social media environments.
-Using data from a nationwide survey of Chinese citizens, we do find that
-the more citizens digitally connect with others, the less personally
-isolated they feel. Conversely, though, the more likely people are to
-move relationships from online to offline, and the more they use social
-media, the more personally isolated they feel. We also find that this
-relationship interacts with urbanicity - being in rural areas tends to
-amplify the effect. Overall, our findings suggest that institutional
-context may not play an important role in the social media - social
-isolation relationship.
+negative role of social media, withn more recent studies focused on
+heterogeneous effects. Using data from a nationwide survey of Chinese
+citizens to gain leverage on this disagreement in the literature, our
+research finds support for those that have focused on heterogeneous
+effects - we find that urbancity is a key moderating variable.
+Additionally, our results lend support to a FOMO mechanism while they
+are not suggestive of a mechanism by which negative content is the
+channel through which social media generates feelings of social
+isolations. Overall, our findings suggest that institutional context may
+not play an important role in the social media - social isolation
+relationship.
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, interior hidden, frame hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, enhanced]}{\end{tcolorbox}}\fi
+
+\begin{keywords}
+    Social Isolation, Social Media, Digital Communication, 
+    China
+\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, sharp corners, boxrule=0pt, frame hidden, enhanced, breakable, interior hidden]}{\end{tcolorbox}}\fi
 
@@
 interconnectedness between people, and that social media platforms were
-the ultimate way to bring people together. Since then, research
-indicates that the effect may be the opposite among at least some part
-of the population. Social media may encourage social isolation, and
-ultimately, social media users may feel more disconnected from others
-than those who do not use social media. We know very little about this
-phenomenon in China. China presents an interesting case because the
-institutional structures, level of development and the cultural context
-are all quite different than the areas studied in most existing studies.
-This allows us to test whether such features moderate or exacerbate the
-relationship between social media use and social isolation. To fully
-test this theory, we employ a large survey of Chinese internet users and
+the ultimate way to bring people together. Since then, research on the
+subject has been decidedly more mixed. On one hand, some authors have
+found social media may encourage social isolation, and ultimately,
+social media users may feel more disconnected from others than those who
+do not use social media. On the other hand, others have found that there
+is only a minimal relationship between these two variables. More recent
+scholarship has suggested that social media may produce heterogeneous
+effects on individuals. This study uses the little-studied Chinese
+social media environment to try and gain leverage on this question - the
+Chinese online environment has certain features that should both
+moderate and exacerbate key causal pathways previously identified in the
+literature. To we employ a large survey of Chinese internet users and
 test a variety of regression specifications.\footnote{All data and
   analysis files for this research are available at the author's
-  website.} The main result is that social media use is robustly
+  website.} The main result is that social media use is generally
 negatively related to social isolation, though the nature of this
 relationship changes depending on the urbanicity of the respondent -
-being in a rural area amplifies this relationship.
+being in a rural area amplifies this relationship. This finding lends
+support both to the previous negative relationship findings and also
+reinforce the findings that emphasize heterogeneous effects.
 
@@
 The existing literature on social isolation and social media use
-generally finds a negative relationship between the two. However, there
-are some remaining questions regarding whether this relationship remains
-significant in different cultural and regulatory environments. Based on
-the existing literature, we then develop some testable hypotheses
-regarding how the relationship between usage and isolation may vary in
-the context of China. The result of these hypotheses tests will help to
-better understand the mechanism that links the two variables.
+generally finds a negative to null relationship between the two
+variables, while the most recent research has suggested that social
+media has heterogeneous effects. Based on this existing literature, we
+then develop some testable hypotheses regarding how the relationship
+between usage and isolation may vary in the context of China. The result
+of these hypotheses tests will help to better understand the possible
+mechanism that links these two variables.
 
@@
 of online connections - both of these have been found to generate social
-anxiety and social isolation (Alabri, 2022; Büttner and Rudert, 2022). A
+anxiety and social isolation (Alabri, 2022; Büttner \& Rudert, 2022). A
 third set of mechanisms primarily concern themselves with the physical
@@
 increasing number of people who consider themselves to be online
-outcasts or losers (\emph{diaosi}) (China{'}s latest social media trend:
-Diaosi / loser subculture, 2016; Nan, 2013; Szablewicz, 2014). We do not
-aim to make a direct comparison between China and Western countries but
-rather highlight the way in which China's unique context helps shed
-light on which contextual factors matter in understanding the linkage
-between the two variables.
+outcasts or losers (\emph{diaosi}) (\emph{China{'}s Latest Social Media
+Trend}, 2016; Nan, 2013; Szablewicz, 2014). We do not aim to make a
+direct comparison between China and Western countries but rather
+highlight the way in which China's unique context helps shed light on
+which contextual factors matter in understanding the linkage between the
+two variables.
 
@@
 are aware that the Chinese government heavily censors politically
-sensitive content on online platforms. However, fewer are aware that the
-Chinese government spends as much, if not more, effort to clean up
-non-political as negative or distressing content on the Chinese
-internet, such as scams, instances of cyber bullying, disturbing videos,
-and vulgar content (Wang, 2020). This control impulse also extends
-content the government views as spiritually polluting, such as
-pornography, scantily dressed women, and other escapist content. While
-the Chinese government and online platforms are not 100 per cent
-effective in their ability to completely stamp out such content, the
-default is that such content is actively restricted, while US platforms
-tent to take a more pro-speech regulatory position (Liu and Yang, 2022).
-If one of the main mechanisms through which social media promotes social
-isolation occurs is exposure to negative content, then this highly
-regulated online environment should lead to a weaker relationship
-between social media use and isolation. Suggestive of this is a a study
-by Liu and Liu that finds Chinese who consumed more commercialized and
-sensationalized media reported more trauma during the first COVID-19
-outbreak in China than those who followed government sources (Liu and
-Liu, 2020).
+sensitive content on online platforms. Fewer are aware that the Chinese
+government spends as much, if not more, effort to clean up non-political
+negative or distressing content on the Chinese internet, such as scams,
+instances of cyber bullying, disturbing videos, and vulgar content
+(Wang, 2020). This control impulse also extends content the government
+views as spiritually polluting, such as pornography, scantily dressed
+women, and other escapist content. While the Chinese government and
+online platforms are not 100 per cent effective in their ability to
+completely stamp out such content, the default is that such content is
+actively restricted, while US platforms tent to take a more pro-speech
+regulatory position (J. Liu \& Yang, 2022). If one of the main
+mechanisms through which social media promotes social isolation occurs
+is exposure to negative content, then this highly regulated online
+environment should lead to a weaker relationship between social media
+use and isolation. Suggestive of this is a a study by Liu and Liu that
+finds Chinese who consumed more commercialized and sensationalized media
+reported more trauma during the first COVID-19 outbreak in China than
+those who followed government sources (C. Liu \& Liu, 2020).
 
@@
 assembly-line fashion to promote products on livestreams or pitch
-sponsor products. In this influencer culture, less attention is paid to
-authenticity and personality and relatively more emphasis is placed on
-consumerism, brand promotion, and image (Tam, 2019; Wei, 2023). Given
+sponsored products. In this influencer culture, less attention is paid
+to authenticity and personality and relatively more emphasis is placed
+on consumerism, brand promotion, and image (Tam, 2019; Wei, 2023). Given
 that previous research has suggested one of the main channels through
@@
 relationship between social media use and social isolation through
-consumption of such highly commercialized content.
+consumption of such highly commercialized content. These influencers are
+most popular among young consumers so one may expect that only younger
+users would experience these effects.
 
@@
 users that primarily use it to contact friends and family, its use can
-counteract the negative effects (Hajek and König, 2019; Lim et al.,
+counteract the negative effects (Hajek \& König, 2019; Lim et al.,
 2020). In this way, those that heavily use these type of combined
@@
 particularly due to lack of access to traditional support systems and
-familial connections (Li and Rose, 2017).
+familial connections (Li \& Rose, 2017).
 
@@
 \item
-  \textbf{H1b:} social media use should have a negative connection to
-  social isolation due to the dominance of influencer culture in China
+  \textbf{H1b:} social media use should have a strongly negative
+  connection to social isolation due to the dominance of influencer
+  culture in China, possibly moderated by age.
 \item
@@
 The latter is consistent with much of the literature outlined above, but
-the former is not. Perhaps, this is context driven. The results also
-indicate that those living in more urban environments tend to feel less
-socially isolated.
+the former is not. The results also indicate that those living in more
+urban environments tend to feel less socially isolated.
 
@@
 not this is due to the influencer culture or other factors, we cannot
-say with our data but it at least does suggest that greater content
-regulation is not likely to moderate the amount of isolation that social
-media produces. We also find, as has been found in other studies, that
-users who use the internet to create new connections are less likely to
-feel isolated (\textbf{H2}). However, this does not seem to extend to
-those that use the internet to facilitate offline meetups. Finally, we
-find that the impact of the internet and social media vary significantly
+say with our data, however age is a consistently negative predictor of
+social isolation even when controlling for amount of social media use.
+This result is at least suggestive of the negative online influencer
+culture. We also find, as has been found in other studies, that users
+who use the internet to create new connections are less likely to feel
+isolated (\textbf{H2}). However, this does not seem to extend to those
+that use the internet to facilitate offline meetups. Finally, we find
+that the impact of the internet and social media vary significantly
 according to the level of urbanicity (\textbf{H3}) - this matches with
 previous findings that suggest that there is significant heterogeneity
-in the impact of social media on social isloation. All of these findings
-are generally in line with previous research on the subject, suggesting
-that the mechanisms that generate feelings of social isolation are
-universal and not so sensitive to different social and governing
-contexts.
+in the impact of social media on social isloation.
 
@@
 connect, build social capital, and some suggested this could deter
-social isolationism. Our results provide little evidence of this
-optimistic view of the internet and its ability to improve the quality
-of people's lives. We do find that some are more likely to interact with
-family and friends and that this does deter feelings of social
-isolation, but on the other hand, even though many move online
-relationships offline and connect through social media, doing so does
-not deter feelings of social isolation. Instead, such digital actively
-is actually associated with increased feelings of social isolation.
-
-We also found no evidence that the internet could serve as bridge to
+social isolationism. On the other hand, more recent research and popular
+media coverage of the subject has presented a deeply negative view of
+the role of social media. Our results do lean toward supporting the
+negative conclusions but add important contextualization and are
+suggestive of which of the hypothesized mechanisms are most relevant.
+
+Firstly, we found no evidence that the internet could serve as bridge to
 build connections for those living outside of cities. The optimistic
-view here would be that the internet could lower the costs of making
-connections for those who have less social opportunity, those living in
-less populated areas, and as a result, help them to feel less isolated.
-We, in fact, found the opposite. Internet communication had either less
-positive effect or more negative effect on feelings of social isolation
-for those living in less urban spaces.
-
-Our contribution here is that we look at some well-established
-theoretical arguments in a context outside that of where most of the
-research centered on these type questions has examined. While our study
-is far from the last word on the subject, these results suggest that the
-mechanisms that link social media use and social isolation are
-relatively consistent across countries.
+view that internet use could lower the costs of making connections for
+those who have less social opportunity, those living in less populated
+areas, and as a result, help them to feel less isolated. We, in fact,
+found the opposite. Internet communication had either less positive
+effect or more negative effect on feelings of social isolation for those
+living in less urban spaces. This finding lends support to the FOMO
+channel - viewing lots of content from influencers in a rural area
+compounds feelings of isolation.
+
+Additionally, given the robustly negative relationship between social
+media use and social isolation even in the context of China's highly
+policed internet, our results cast some doubt on theories that suggest
+it is the negative content, such as cyberbullying or violent/graphic
+posts, that drives the relationship. Finally, our results also further
+suggest more work needs to be done in identifying important hetergeneous
+effects - in our results, those living in a big city experienced almost
+no change in social isolation as social media use increased while the
+relationship becomes increasingly negative by ruralness. This specific
+heterogeneous effect may be unique to China but the strength of it
+suggests that important inter-personal factors may be relevant in other
+contexts.
+
+While our study is far from the last word on the subject, we hope this
+paper further helps move researchers away from considering the binary
+question of whether social media use has a negative relationship with
+social isolation to more productively considering the contextual and
+personal attributes that moderate and mediate this relationship.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ademiluyi2022}{}}%
-Ademiluyi A, Li C and Park A (2022)
-\href{https://doi.org/10.2196/30286}{Implications and Preventions of
-Cyberbullying and Social Exclusion in Social Media: Systematic Review}.
-\emph{JMIR Formative Research} 6(1): e30286.
+Ademiluyi, A., Li, C., \& Park, A. (2022). Implications and Preventions
+of Cyberbullying and Social Exclusion in Social Media: Systematic
+Review. \emph{JMIR Formative Research}, \emph{6}(1), e30286.
+\url{https://doi.org/10.2196/30286}
 
 \leavevmode\vadjust pre{\hypertarget{ref-alabri2022}{}}%
-Alabri A (2022) \href{https://doi.org/10.1155/2022/4824256}{Fear of
-Missing Out (FOMO): The Effects of the Need to Belong, Perceived
-Centrality, and Fear of Social Exclusion}. \emph{Human Behavior and
-Emerging Technologies} 2022: e4824256.
+Alabri, A. (2022). Fear of Missing Out (FOMO): The Effects of the Need
+to Belong, Perceived Centrality, and Fear of Social Exclusion.
+\emph{Human Behavior and Emerging Technologies}, \emph{2022}, e4824256.
+\url{https://doi.org/10.1155/2022/4824256}
 
 \leavevmode\vadjust pre{\hypertarget{ref-appel2020}{}}%
-Appel M, Marker C and Gnambs T (2020)
-\href{https://doi.org/10.1177/1089268019880891}{Are Social Media Ruining
-Our Lives? A Review of Meta-Analytic Evidence}. \emph{Review of General
-Psychology} 24(1): 60--74.
+Appel, M., Marker, C., \& Gnambs, T. (2020). Are Social Media Ruining
+Our Lives? A Review of Meta-Analytic Evidence. \emph{Review of General
+Psychology}, \emph{24}(1), 60--74.
+\url{https://doi.org/10.1177/1089268019880891}
 
 \leavevmode\vadjust pre{\hypertarget{ref-beyens2020}{}}%
-Beyens I, Pouwels JL, Driel II van, et al. (2020)
-\href{https://doi.org/10.1038/s41598-020-67727-7}{The effect of social
-media on well-being differs from adolescent to adolescent}.
-\emph{Scientific Reports} 10(1): 10763.
+Beyens, I., Pouwels, J. L., Driel, I. I. van, Keijsers, L., \&
+Valkenburg, P. M. (2020). The effect of social media on well-being
+differs from adolescent to adolescent. \emph{Scientific Reports},
+\emph{10}(1), 10763. \url{https://doi.org/10.1038/s41598-020-67727-7}
 
 \leavevmode\vadjust pre{\hypertarget{ref-buxfcttner2022}{}}%
-Büttner CM and Rudert SC (2022)
-\href{https://doi.org/10.1016/j.chb.2021.107062}{Why didn't you tag
-me?!: Social exclusion from Instagram posts hurts, especially those with
-a high need to belong}. \emph{Computers in Human Behavior} 127: 107062.
+Büttner, C. M., \& Rudert, S. C. (2022). Why didn't you tag me?!: Social
+exclusion from Instagram posts hurts, especially those with a high need
+to belong. \emph{Computers in Human Behavior}, \emph{127}, 107062.
+\url{https://doi.org/10.1016/j.chb.2021.107062}
 
 \leavevmode\vadjust pre{\hypertarget{ref-chinas2016}{}}%
-China{'}s latest social media trend: Diaosi / loser subculture (2016).
-Available at:
-\url{https://www.appnova.com/chinas-latest-social-media-trend-diaosi-loser-subculture/}.
+\emph{China{'}s latest social media trend: Diaosi / loser subculture}.
+(2016).
+\url{https://www.appnova.com/chinas-latest-social-media-trend-diaosi-loser-subculture/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-ellison2007}{}}%
-Ellison NB, Steinfield C and Lampe C (2007)
-\href{https://doi.org/10.1111/j.1083-6101.2007.00367.x}{The Benefits of
+Ellison, N. B., Steinfield, C., \& Lampe, C. (2007). The Benefits of
 Facebook {``}Friends:{''} Social Capital and College Students{'} Use of
-Online Social Network Sites}. \emph{Journal of Computer-Mediated
-Communication} 12(4): 1143--1168.
+Online Social Network Sites. \emph{Journal of Computer-Mediated
+Communication}, \emph{12}(4), 1143--1168.
+\url{https://doi.org/10.1111/j.1083-6101.2007.00367.x}
 
 \leavevmode\vadjust pre{\hypertarget{ref-hajek2019}{}}%
-Hajek A and König H-H (2019)
-\href{https://doi.org/10.1186/s12889-018-6369-6}{The association between
-use of online social networks sites and perceived social isolation among
-individuals in the second half of life: results based on a nationally
-representative sample in Germany}. \emph{BMC Public Health} 19(1): 40.
+Hajek, A., \& König, H.-H. (2019). The association between use of online
+social networks sites and perceived social isolation among individuals
+in the second half of life: results based on a nationally representative
+sample in Germany. \emph{BMC Public Health}, \emph{19}(1), 40.
+\url{https://doi.org/10.1186/s12889-018-6369-6}
 
 \leavevmode\vadjust pre{\hypertarget{ref-henning-smith2018}{}}%
-Henning-Smith C, Ecklund A and Kozhimannil K (2018)
-\href{https://doi.org/10.1093/geroni/igy023.2851}{RURAL-URBAN
-DIFFERENCES IN SOCIAL ISOLATION AND ITS RELATIONSHIP TO HEALTH}.
-\emph{Innovation in Aging} 2(Suppl 1): 770.
+Henning-Smith, C., Ecklund, A., \& Kozhimannil, K. (2018). RURAL-URBAN
+DIFFERENCES IN SOCIAL ISOLATION AND ITS RELATIONSHIP TO HEALTH.
+\emph{Innovation in Aging}, \emph{2}(Suppl 1), 770.
+\url{https://doi.org/10.1093/geroni/igy023.2851}
 
 \leavevmode\vadjust pre{\hypertarget{ref-kaye2017}{}}%
-Kaye LW (2017) \href{https://doi.org/10.1093/ppar/prx029}{Older adults,
-rural living, and the escalating risk of social isolation}. \emph{Public
-Policy \& Aging Report} 27(4): 139--144.
+Kaye, L. W. (2017). Older adults, rural living, and the escalating risk
+of social isolation. \emph{Public Policy \& Aging Report}, \emph{27}(4),
+139--144. \url{https://doi.org/10.1093/ppar/prx029}
 
 \leavevmode\vadjust pre{\hypertarget{ref-kim2017}{}}%
-Kim HH (2017) \href{https://doi.org/10.1080/02673843.2016.1197135}{The
-impact of online social networking on adolescent psychological
-well-being (WB): A population-level analysis of korean school-aged
-children}. \emph{International Journal of Adolescence and Youth} 22(3):
-364--376.
+Kim, H. H. (2017). The impact of online social networking on adolescent
+psychological well-being (WB): A population-level analysis of korean
+school-aged children. \emph{International Journal of Adolescence and
+Youth}, \emph{22}(3), 364--376.
+\url{https://doi.org/10.1080/02673843.2016.1197135}
 
 \leavevmode\vadjust pre{\hypertarget{ref-koning2017}{}}%
-Koning JLD, Stathi A and Richards S (2017)
-\href{https://doi.org/10.1017/S0144686X16000696}{Predictors of
+Koning, J. L. D., Stathi, A., \& Richards, S. (2017). Predictors of
 loneliness and different types of social isolation of rural-living older
-adults in the United Kingdom}. \emph{Ageing \& Society} 37(10):
-2012--2043.
+adults in the United Kingdom. \emph{Ageing \& Society}, \emph{37}(10),
+2012--2043. \url{https://doi.org/10.1017/S0144686X16000696}
 
 \leavevmode\vadjust pre{\hypertarget{ref-larson2018}{}}%
-Larson LR, Szczytko R, Bowers EP, et al. (2018) Outdoor Time, Screen
-Time, and Connection to Nature: Troubling Trends Among Rural Youth?
-\emph{Environment and Behavior}. Epub ahead of print 20 October 2018.
-DOI:
-\href{https://doi.org/10.1177/0013916518806686}{10.1177/0013916518806686}.
+Larson, L. R., Szczytko, R., Bowers, E. P., Stephens, L. E., Stevenson,
+K. T., \& Floyd, M. F. (2018). Outdoor Time, Screen Time, and Connection
+to Nature: Troubling Trends Among Rural Youth? \emph{Environment and
+Behavior}. \url{https://doi.org/10.1177/0013916518806686}
 
 \leavevmode\vadjust pre{\hypertarget{ref-li2017}{}}%
-Li J and Rose N (2017)
-\href{https://doi.org/10.1016/j.healthplace.2017.08.009}{Urban social
-exclusion and mental health of China's rural-urban migrants
-{\textendash} A review and call for research}. \emph{Health \& Place}
-48: 20--30.
+Li, J., \& Rose, N. (2017). Urban social exclusion and mental health of
+China's rural-urban migrants {\textendash} A review and call for
+research. \emph{Health \& Place}, \emph{48}, 20--30.
+\url{https://doi.org/10.1016/j.healthplace.2017.08.009}
 
 \leavevmode\vadjust pre{\hypertarget{ref-lim2020}{}}%
-Lim MH, Eres R and Vasan S (2020)
-\href{https://doi.org/10.1007/s00127-020-01889-7}{Understanding
-loneliness in the twenty-first century: An update on correlates, risk
-factors, and potential solutions}. \emph{Social Psychiatry and
-Psychiatric Epidemiology} 55(7): 793--810.
+Lim, M. H., Eres, R., \& Vasan, S. (2020). Understanding loneliness in
+the twenty-first century: An update on correlates, risk factors, and
+potential solutions. \emph{Social Psychiatry and Psychiatric
+Epidemiology}, \emph{55}(7), 793--810.
+\url{https://doi.org/10.1007/s00127-020-01889-7}
 
 \leavevmode\vadjust pre{\hypertarget{ref-liu2020}{}}%
-Liu C and Liu Y (2020)
-\href{https://doi.org/10.3390/ijerph17134720}{Media Exposure and Anxiety
-during COVID-19: The Mediation Effect of Media Vicarious
-Traumatization}. \emph{International Journal of Environmental Research
-and Public Health} 17(13): 4720.
+Liu, C., \& Liu, Y. (2020). Media Exposure and Anxiety during COVID-19:
+The Mediation Effect of Media Vicarious Traumatization.
+\emph{International Journal of Environmental Research and Public
+Health}, \emph{17}(13), 4720.
+\url{https://doi.org/10.3390/ijerph17134720}
 
 \leavevmode\vadjust pre{\hypertarget{ref-liu2022}{}}%
-Liu J and Yang L (2022)
-\href{https://doi.org/10.1002/poi3.307}{{``}Dual-Track{''} platform
-governance on content: A comparative study between China and United
-States}. \emph{Policy \& Internet} 14(2): 304--323.
+Liu, J., \& Yang, L. (2022). {``}Dual-Track{''} platform governance on
+content: A comparative study between China and United States.
+\emph{Policy \& Internet}, \emph{14}(2), 304--323.
+\url{https://doi.org/10.1002/poi3.307}
 
 \leavevmode\vadjust pre{\hypertarget{ref-nan2013}{}}%
-Nan W (2013)
-\href{https://www.scmp.com/news/china/article/1232976/chinas-underdog-youth-find-success-diaosi-or-loser-identity}{China's
-underdog youth find success in 'diaosi' - or 'loser' - identity}.
-\emph{South China Morning Post}. Epub ahead of print 8 May 2013.
+Nan, W. (2013). China's underdog youth find success in 'diaosi' - or
+'loser' - identity. \emph{South China Morning Post}.
+\url{https://www.scmp.com/news/china/article/1232976/chinas-underdog-youth-find-success-diaosi-or-loser-identity}
 
 \leavevmode\vadjust pre{\hypertarget{ref-nowland2018}{}}%
-Nowland R, Necka EA and Cacioppo JT (2018)
-\href{https://doi.org/10.1177/1745691617713052}{Loneliness and Social
-Internet Use: Pathways to Reconnection in a Digital World?}
-\emph{Perspectives on Psychological Science} 13(1): 70--87.
+Nowland, R., Necka, E. A., \& Cacioppo, J. T. (2018). Loneliness and
+Social Internet Use: Pathways to Reconnection in a Digital World?
+\emph{Perspectives on Psychological Science}, \emph{13}(1), 70--87.
+\url{https://doi.org/10.1177/1745691617713052}
 
 \leavevmode\vadjust pre{\hypertarget{ref-ostic2021}{}}%
-Ostic D, Qalati SA, Barbosa B, et al. (2021)
-\href{https://www.frontiersin.org/articles/10.3389/fpsyg.2021.678766}{Effects
-of social media use on psychological well-being: A mediated model}.
-\emph{Frontiers in Psychology} 12.
+Ostic, D., Qalati, S. A., Barbosa, B., Shah, S. M. M., Galvan Vela, E.,
+Herzallah, A. M., \& Liu, F. (2021). Effects of social media use on
+psychological well-being: A mediated model. \emph{Frontiers in
+Psychology}, \emph{12}.
+\url{https://www.frontiersin.org/articles/10.3389/fpsyg.2021.678766}
 
 \leavevmode\vadjust pre{\hypertarget{ref-primack2017}{}}%
-Primack BA, Shensa A, Sidani JE, et al. (2017)
-\href{https://doi.org/10.1016/j.amepre.2017.01.010}{Social Media Use and
-Perceived Social Isolation Among Young Adults in the U.S.}
-\emph{American Journal of Preventive Medicine} 53(1): 1--8.
+Primack, B. A., Shensa, A., Sidani, J. E., Whaite, E. O., Lin, L. yi,
+Rosen, D., Colditz, J. B., Radovic, A., \& Miller, E. (2017). Social
+Media Use and Perceived Social Isolation Among Young Adults in the U.S.
+\emph{American Journal of Preventive Medicine}, \emph{53}(1), 1--8.
+\url{https://doi.org/10.1016/j.amepre.2017.01.010}
 
 \leavevmode\vadjust pre{\hypertarget{ref-steinfield2008}{}}%
-Steinfield C, Ellison NB and Lampe C (2008)
-\href{https://doi.org/10.1016/j.appdev.2008.07.002}{Social capital,
+Steinfield, C., Ellison, N. B., \& Lampe, C. (2008). Social capital,
 self-esteem, and use of online social network sites: A longitudinal
-analysis}. \emph{Journal of Applied Developmental Psychology} 29(6).
-Social Networking on the Internet: 434--445.
+analysis. \emph{Journal of Applied Developmental Psychology},
+\emph{29}(6), 434--445.
+\url{https://doi.org/10.1016/j.appdev.2008.07.002}
 
 \leavevmode\vadjust pre{\hypertarget{ref-subrahmanyam2008}{}}%
-Subrahmanyam K, Reich SM, Waechter N, et al. (2008)
-\href{https://doi.org/10.1016/j.appdev.2008.07.003}{Online and offline
-social networks: Use of social networking sites by emerging adults}.
-\emph{Journal of Applied Developmental Psychology} 29(6). Social
-Networking on the Internet: 420--433.
+Subrahmanyam, K., Reich, S. M., Waechter, N., \& Espinoza, G. (2008).
+Online and offline social networks: Use of social networking sites by
+emerging adults. \emph{Journal of Applied Developmental Psychology},
+\emph{29}(6), 420--433.
+\url{https://doi.org/10.1016/j.appdev.2008.07.003}
 
 \leavevmode\vadjust pre{\hypertarget{ref-szablewicz2014}{}}%
-Szablewicz M (2014) \href{https://doi.org/10.1177/0920203X14531538}{The
-{`}losers{'} of China{'}s Internet: Memes as {`}structures of feeling{'}
-for disillusioned young netizens}. \emph{China Information} 28(2):
-259--275.
+Szablewicz, M. (2014). The {`}losers{'} of China{'}s Internet: Memes as
+{`}structures of feeling{'} for disillusioned young netizens.
+\emph{China Information}, \emph{28}(2), 259--275.
+\url{https://doi.org/10.1177/0920203X14531538}
 
 \leavevmode\vadjust pre{\hypertarget{ref-tam2019}{}}%
-Tam L (2019)
-\href{https://www.scmp.com/lifestyle/entertainment/article/2183174/trust-me-you-need-how-chinas-live-streaming-kol-stars-are}{The
-China fame factory training online influencers to sell}. \emph{South
-China Morning Post}. Epub ahead of print 24 January 2019.
+Tam, L. (2019). The China fame factory training online influencers to
+sell. \emph{South China Morning Post}.
+\url{https://www.scmp.com/lifestyle/entertainment/article/2183174/trust-me-you-need-how-chinas-live-streaming-kol-stars-are}
 
 \leavevmode\vadjust pre{\hypertarget{ref-twenge2019}{}}%
-Twenge JM (2019) \href{https://doi.org/10.1177/0963721419838244}{More
-Time on Technology, Less Happiness? Associations Between Digital-Media
-Use and Psychological Well-Being}. \emph{Current Directions in
-Psychological Science} 28(4): 372--379.
+Twenge, J. M. (2019). More Time on Technology, Less Happiness?
+Associations Between Digital-Media Use and Psychological Well-Being.
+\emph{Current Directions in Psychological Science}, \emph{28}(4),
+372--379. \url{https://doi.org/10.1177/0963721419838244}
+
+\leavevmode\vadjust pre{\hypertarget{ref-twenge2021}{}}%
+Twenge, J. M., Haidt, J., Blake, A. B., McAllister, C., Lemon, H., \& Le
+Roy, A. (2021). Worldwide increases in adolescent loneliness.
+\emph{Journal of Adolescence}, \emph{93}, 257--269.
+\url{https://doi.org/10.1016/j.adolescence.2021.06.006}
 
 \leavevmode\vadjust pre{\hypertarget{ref-twenge2017}{}}%
-Twenge JM, Krizan Z and Hisler G (2017)
-\href{https://doi.org/10.1016/j.sleep.2017.08.013}{Decreases in
+Twenge, J. M., Krizan, Z., \& Hisler, G. (2017). Decreases in
 self-reported sleep duration among U.S. adolescents
-2009{\textendash}2015 and association with new media screen time}.
-\emph{Sleep Medicine} 39: 47--53.
-
-\leavevmode\vadjust pre{\hypertarget{ref-twenge2021}{}}%
-Twenge JM, Haidt J, Blake AB, et al. (2021)
-\href{https://doi.org/10.1016/j.adolescence.2021.06.006}{Worldwide
-increases in adolescent loneliness}. \emph{Journal of Adolescence} 93:
-257--269.
+2009{\textendash}2015 and association with new media screen time.
+\emph{Sleep Medicine}, \emph{39}, 47--53.
+\url{https://doi.org/10.1016/j.sleep.2017.08.013}
 
 \leavevmode\vadjust pre{\hypertarget{ref-valkenburg2022}{}}%
-Valkenburg PM, Meier A and Beyens I (2022)
-\href{https://doi.org/10.1016/j.copsyc.2021.08.017}{Social media use and
+Valkenburg, P. M., Meier, A., \& Beyens, I. (2022). Social media use and
 its impact on adolescent mental health: An umbrella review of the
-evidence}. \emph{Current Opinion in Psychology} 44: 58--68.
+evidence. \emph{Current Opinion in Psychology}, \emph{44}, 58--68.
+\url{https://doi.org/10.1016/j.copsyc.2021.08.017}
 
 \leavevmode\vadjust pre{\hypertarget{ref-wang2020}{}}%
-Wang J (2020) \emph{Regulation of digital media platforms: The case of
-china}. 6 November. Foundation for Law, Justice,; Society. Available at:
-\url{https://www.fljs.org/banning-regulating-tiktok-addressing-concerns-national-security-privacy-and-online-harms}.
+Wang, J. (2020). \emph{Regulation of digital media platforms: The case
+of china}.
+\url{https://www.fljs.org/banning-regulating-tiktok-addressing-concerns-national-security-privacy-and-online-harms}
 
 \leavevmode\vadjust pre{\hypertarget{ref-wei2023}{}}%
-Wei AC (2023)
-\href{https://www.straitstimes.com/asia/east-asia/wang-hong-culture-booms-in-china-as-more-young-people-dream-of-becoming-influencers}{{`}Wang
-hong{'} culture booms in China as more young people dream of becoming
-influencers}. \emph{The Straits Times}. Epub ahead of print 27 May 2023.
+Wei, A. C. (2023). {`}Wang hong{'} culture booms in China as more young
+people dream of becoming influencers. \emph{The Straits Times}.
+\url{https://www.straitstimes.com/asia/east-asia/wang-hong-culture-booms-in-china-as-more-young-people-dream-of-becoming-influencers}
 
 \leavevmode\vadjust pre{\hypertarget{ref-xia1995}{}}%
-Xia M (1995) Changes in the {Pattern} of {Migration} in {Urban} {China}.
-In: Day LH, Xia M, and Xia M (eds) \emph{Migration and {Urbanization} in
-{China}}. New York, NY: Routledge.
+Xia, M. (1995). Changes in the {Pattern} of {Migration} in {Urban}
+{China}. In L. H. Day, M. Xia, \& M. Xia (Eds.), \emph{Migration and
+{Urbanization} in {China}}. Routledge.
 

### 2023-10-08 tandf/_extensions/tandf/partials/doc-class.tex
prepared for t and f submission

--- 2023-05-29 Social-Isolation-in-China.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
-%
-\documentclass[
-  letterpaper,
-  DIV=11,
-  numbers=noendperiod]{scrartcl}
+\documentclass[]{interact}
 
-\usepackage{amsmath,amssymb}
-\usepackage{lmodern}
-\usepackage{iftex}
-\ifPDFTeX
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-% Make \paragraph and \subparagraph free-standing
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
+\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
+\usepackage[caption=false]{subfig}% Support for small, `sub' figures and tables
 
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
+\usepackage[natbibapa,nodoi]{apacite}% Citation support using apacite.sty. Commands using natbib.sty MUST be deactivated first!
+\setlength\bibhang{12pt}% To set the indentation in the list of references using apacite.sty. Commands using natbib.sty MUST be deactivated first!
+\renewcommand\bibliographytypesize{\fontsize{10}{12}\selectfont}% To set the list of references in 10 point font using apacite.sty. Commands using natbib.sty MUST be deactivated first!
 
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
-\KOMAoption{captions}{tableheading}
-\makeatletter
-\makeatother
-\makeatletter
-\makeatother
-\makeatletter
-\@ifpackageloaded{caption}{}{\usepackage{caption}}
-\AtBeginDocument{%
-\ifdefined\contentsname
-  \renewcommand*\contentsname{Table of contents}
-\else
-  \newcommand\contentsname{Table of contents}
-\fi
-\ifdefined\listfigurename
-  \renewcommand*\listfigurename{List of Figures}
-\else
-  \newcommand\listfigurename{List of Figures}
-\fi
-\ifdefined\listtablename
-  \renewcommand*\listtablename{List of Tables}
-\else
-  \newcommand\listtablename{List of Tables}
-\fi
-\ifdefined\figurename
-  \renewcommand*\figurename{Figure}
-\else
-  \newcommand\figurename{Figure}
-\fi
-\ifdefined\tablename
-  \renewcommand*\tablename{Table}
-\else
-  \newcommand\tablename{Table}
-\fi
-}
-\@ifpackageloaded{float}{}{\usepackage{float}}
-\floatstyle{ruled}
-\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
-\floatname{codelisting}{Listing}
-\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
-\makeatother
-\makeatletter
-\@ifpackageloaded{caption}{}{\usepackage{caption}}
-\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
-\makeatother
-\makeatletter
-\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
-\makeatother
-\makeatletter
-\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
-\makeatother
-\makeatletter
-\makeatother
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={The Spatial Relationship between Social Media, Digital Connectedness, and Social Isolation in China: Revisting Cyber-Optimism},
-  pdfauthor={Jason Gainous; Andrew W. MacDonald},
-  pdfkeywords={social isolation, social media, digital
-connectedness, China},
-  colorlinks=true,
-  linkcolor={blue},
-  filecolor={Maroon},
-  citecolor={Blue},
-  urlcolor={Blue},
-  pdfcreator={LaTeX via pandoc}}
+\let\subcaption\relax
+\let\subfloat\relax
 
-\title{The Spatial Relationship between Social Media, Digital
-Connectedness, and Social Isolation in China: Revisting Cyber-Optimism}
-\author{Jason Gainous\footnote{University of Louisville,
-  jason.gainous@louisville.edu} \and Andrew W. MacDonald\footnote{Duke
-  Kunshan University, andrew.macdonald@dukekunshan.edu.cn}}
-\date{3/5/23}
+\theoremstyle{plain}% Theorem-like structures provided by amsthm.sty
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{proposition}[theorem]{Proposition}
 
-\begin{document}
-\maketitle
-\begin{abstract}
-Early research and populuar discourse on the promise of the internet was
-optimistic. Many believed it would promote social interconnectedness
-and, ultimately, be a positive force in people's lives. Since these
-early predictions, research has become much less positive, usually
-pointing to the negative aspects of social media. Here we argue that the
-digital environment can actually create a space that deters feelings of
-social isolationism especially for those living outside cities in
-restrictive information environments where citizens are often
-disconnected from the outside world. Using data from a nationwide survey
-of Chinese citizens we conducted in 2015, we find that the more citizens
-digitally connect with others, the more likely they are to move
-relationships from online to offliine, and the more they use social
-media the less personally isolated they feel. Futher, those living in
-urban environments tend to feel more isolated, and this spatial factor
-seems to moderate the aforementioned relationships. All three of those
-observed relationships are stronger for those in less urban
-environments.
-\end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, enhanced, frame hidden, interior hidden, boxrule=0pt, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
+\theoremstyle{definition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{example}[theorem]{Example}
 
-\hypertarget{social-isolation-in-china}{%
-\section{Social Isolation in China}\label{social-isolation-in-china}}
-
-\hypertarget{introduction}{%
-\subsection{Introduction}\label{introduction}}
-
-Research is quite mixed when it comes to identifying the relationship
-between social media use and feelings of isolationism. Early research
-suggested that the internet would build social capital, or an
-interconnectedness between people, and that social media platforms were
-the ultimate way to bring people together. Since then, research
-indicates that the effect may be the opposite for many. Social media may
-encourage social isolation, and ultimately, social media users may feel
-more disconnected from others than those who do not use social media. We
-know very little about this phenomenon in China. China presents an
-interesting case because the internet is bifurcated to some degree --
-there is the Chinese internet and the outside internet available via
-VPNs. Being isolation to the outside world may lessen feelings of
-isolation, or it may increase these feelings because digital exposure to
-a world is much larger than that in people's immediate environment
-without the ability to have in-person connection to may make one feel
-isolated. Interestingly, and somewhat ironically though, it may also
-matter, too, whether someone lives in a city. Research has suggested
-that urban living can actually lead to feelings of isolation.
-
-\hypertarget{introduction-1}{%
-\subsection{Introduction}\label{introduction-1}}
-
-Research is quite mixed when it comes to identifying the relationship
-between social media use and feelings of isolationism. Early research
-suggested that the internet would build social capital, or an
-interconnectedness between people, and that social media platforms were
-the ultimate way to bring people together. Since then, research
-indicates that the effect may be the opposite for many. Social media may
-encourage social isolation, and ultimately, social media users may feel
-more disconnected from others than those who do not use social media. We
-know very little about this phenomenon in China. China presents an
-interesting case because the internet is bifurcated to some degree --
-there is the Chinese internet and the outside internet available via
-VPNs. Being isolation to the outside world may lessen feelings of
-isolation, or it may increase these feelings because digital exposure to
-a world is much larger than that in people's immediate environment
-without the ability to have in-person connection to may make one feel
-isolated. Interestingly, and somewhat ironically though, it may also
-matter, too, whether someone lives in a city. Research has suggested
-that urban living can actually lead to feelings of isolation.
-
-\hypertarget{data}{%
-\subsection{Data}\label{data}}
-
-Our data are based on a random Internet survey conducted by Qualtrics
-from November 25 to December 2, 2015. We designed the instrument,
-content and structure. After we designed the instrument in English and
-translated it into Chinese, we entered the questions into the graphical
-interface provided from our survey provider, Qualtrics. We were careful
-at this stage to make the formatting clear, and to distribute the
-questions across numerous pages to prevent overwhelming respondents with
-too many questions at once. This helped us achieve a high completion and
-response rate. Additionally, we were particularly attentive to the
-possibility of question order effects. Many of the questions are
-sensitive and could cue responses to subsequent questions. We grouped
-and placed questions strategically to limit any such potential for
-response bias. Once we settled on the design, Qualtrics administered the
-survey in November 2015. They recruit a large pool of respondents for
-various survey projects through online advertising on websites such as
-local portals, search engines, social networking services, and/or online
-shopping services. Panelists who update their profiles at least once
-every 6 months are randomly invited to participate in surveys for which
-they qualify. Online points are awarded to the corresponding panelists,
-which they may accumulate and exchange for cash or various other
-country-specific gifts to serve as an incentive for completion. This
-number of points is based on the length of the survey. Ours had over
-fifty questions, so respondents received a relatively high number of
-points.
-
-The data collection had two phases. For the first phase, Qualtrics
-collected and submitted to us a trial run of 286 cases. We were able to
-check the data for reliability and adjust the instrument before
-proceeding with the second phase, the final data collection. We only
-made three adjustments, all of which turned out to be important and
-central to our analysis. For the trial run, we only asked respondents
-about pro-government Internet posters and did not ask them about
-potential net-spy or hostile posters. We amended this oversight and it
-became central to the analysis that follows. In addition, much of our
-theory focuses on the impact of Chinese Internet users circumventing
-government filters on the Internet. We initially had a question about
-whether citizens had jumped the wall to read sensitive political
-information (see Appendix A -- Q25), but decided to add whether they had
-done so for entertainment purposes as well (Q26 - to watch foreign
-movies, television shows, etc.). Finally, we also included an attention
-filter question as part of a battery of institutional trust questions
-where respondents were simply told to select the ``None at all''
-response (Q13H). If they did not select this response, we could assume
-they were not paying attention to the questions, and the survey ended
-for these respondents and the data were not collected for them. In the
-end, the full sample included a total of 2292 respondents. This sample
-size provides for a roughly ±2 margin of error.
-
-While our sample was randomly selected, the sampling frame was based
-only on Internet users that Qualtrics can access. Qualtrics recruits
-their frame subjects through online advertising on websites such as
-local portals, search engines, social networking services, and/or online
-shopping services. We do not contend that our sample is representative
-of the Chinese population, as the method of obtaining respondents
-obviously greatly limits those citizens with little or no access to the
-Internet. That said, we are comfortable that our sample is generally
-representative of Chinese Internet users. Given that our research focus
-centers on Internet effects, it makes sense to have a large sample of
-Internet users. A sampling frame including the entire Chinese population
-did not make sense for this research. Half of the population do not
-regularly access the Internet according to World Bank and China Internet
-Network Information Center (CNNIC) data as of late 2015 when we
-conducted our survey. Using a sample of the entire population could
-potentially limit the degrees of freedom in our models and the marginals
-of nuanced measures of digital media use would likely become too small
-to have any value. Thus, the large sample of Internet users adds to our
-confidence in the inferences throughout the book.
-
-\end{document}
+\theoremstyle{remark}
+\newtheorem{remark}{Remark}
+\newtheorem{notation}{Notation}

### 2023-10-08 Author bios.qmd
File cleanup

---
title: "Author bios"
format: pdf
---

## Jason Gainous

Dr. Jason Gainous is a Professor of Mass Communications at the Univesrity of Sharjah. His research focuses on information technology and politics. He has published two books, one with Oxford University Press (Tweeting to Power: The Social Media Revolution in American Politics) and one with Rowman and Littlefield (Rebooting American Politics: The Internet Revolution). He has also published various articles in journals including American Politics Research, Democratization, Information, Communication and Society, International Journal of Press/Politics, International Journal of Communication, Journal of Information Technology & Politics, Political Behavior, Political Research Quarterly, Political Communication, Social Science Quarterly, and Statistical Science among others.

His research has won awards from the American Political Science Association, the Kentucky Political Science Association, the Southwestern Social Science Association, and the Florida Political Science Association. The University of Louisville has also honored him with their most prestigious award for research as well as their most prestigious award for teaching.

Dr. Gainous is also the Co-Editor in Chief of the Journal of Information Technology & Politics.

## Andrew W. MacDonald

Andrew W. MacDonald is an Assistant Professor of Social Science at Duke Kunshan University. He primarily works in the area of Chinese public opinion research, having authored nearly a dozen surveys of Chinese attitudes on politics, technology, and social questions. His work on this topic has been published in a wide variety of communication, technology, and experimental design journals.

His latest projects examine how Chinese feel about state versus corporate control of online personal information and how Chinese people read and interpret state propaganda messages. Taken as a whole, his work seeks to complexify simple narratives about Chinese public opinion; that either the public passively accepts state narratives or becomes an all-out regime opponent. In fact, public opinion is surprisingly nuanced given that China is an authoritarian context.

His other interests lie in data visualization and making data science more approachable using new technological tools. He has developed several innovative, web-based approaches for learning statistical concepts and regularly teaches his universities Stats 101 class.

### 2023-10-08 tandf/Social Isolation in China.qmd
File cleanup

@@
 csl: taylor-and-francis-apa.csl
-author:
-  - name: Jason Gainous
-    affiliations:
-      - name: University of Sharjah
-        department: Department of Mass Communication
-        city: Sharjah
-        country: United Arab Emirates
-    orcid: 0000-0002-3104-2313
-    email: jgainous@sharjah.ac.ae
-  - name: Andrew W. MacDonald
-    affiliations:
-      - name: Duke Kunshan University
-        department: Division of Social Sciences
-        city: Kunshan
-        country: China
-    orcid: 0000-0002-4695-1560
-    email: andrew.macdonald@dukekunshan.edu.cn
-    attributes:
-      corresponding: true
 ---

### 2023-10-08 tandf/Social-Isolation-in-China.tex
File cleanup

@@
   pdftitle={Lonely and online: an investigation of social media use and social isolation in China},
-  pdfauthor={Jason Gainous; Andrew W. MacDonald},
   pdfkeywords={Social Isolation, Social Media, Digital
@@
 
-\author{\name{Jason Gainous\textsuperscript{a} and Andrew W.
-MacDonald\textsuperscript{b}\thanks{CONTACT Andrew W.
-MacDonald. Email: andrew.macdonald@dukekunshan.edu.cn}}
-\affil{\textsuperscript{a}Department of Mass Communication, University
-of Sharjah, Sharjah, United Arab Emirates;
-\textsuperscript{b}Division of Social Sciences, Duke Kunshan
-University, Kunshan, China}}
-
-%\author[1]{Jason Gainous%
-%%
-%}
-% \ead{jgainous@sharjah.ac.ae} 
-%\author[2]{Andrew W. MacDonald%
-%\corref{cor1}%
-%}
-% \ead{andrew.macdonald@dukekunshan.edu.cn} 
 %
@@
     China
-\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, sharp corners, boxrule=0pt, frame hidden, enhanced, breakable, interior hidden]}{\end{tcolorbox}}\fi
+\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, boxrule=0pt, interior hidden, sharp corners, frame hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
 

### 2024-03-19 tandf/Response to reviewers.qmd
Revision updates

---
title: "Response to reviewers"
format: pdf
---

## Reviewer 1

*However, the introduction of the current manuscript should be rewritten. The authors used lots of sentences to describe the background of social media use in China to introduce the research questions. This is unhelpful. It is suggested to examine the related theories to answer, why the phenomenon of social media use in Mainland China may be different from others.*

We introduce the context of China primarily in the Literature Review and Theory section, so we are assuming this is the section to which the reviewer is referring. We agree that the China section is perhaps too long. We have trimmed it and added links to relevant theories.

## Reviewer 2

*1.	In the abstract, there is more information that needs to be added: a clear aim of this research and a few words about the sample size.*

Abstract rewritten and sample size added.

*2.	What is FOMO in abstract? Needs to be clarified here to be understood by the readers.*

Definition added.

*3.	References need to be added in the Introduction section. Also, I suggest merging the introduction section with the literature review and theory section.*

References added. We welcome additional feedback on how to merge the introduction and literature review sections but we believe after deleting the first paragraph of the lit review section, there is a clearer delineation between the two sections.

*4.	In Literature Review and Theory subtitle, the first sentence needs a reference.*

The sentence is deleted as per the comment to point 5 below.

*5.	The second and third sentence in the Literature Review and Theory section (first paragraph) can be moved in the end of the introduction section or can be omitted.*

The sentences have been deleted, additionally, the first sentence read awkwardly without the following sentences and did not add significantly to the section, so we also chose to delete that sentence.

*6.	Reference is needed in the first sentence of the second paragraph in the Literature Review and Theory section.*

The references for this claim was located at the end of the paragraph where the arguments of the authors were described in detail. Though, we can see how it would be confusing. We moved the references to the end of the first sentence.

*7.	Nothing in the literature review about social media addiction. I suggest to see: Social isolation, social support and their relationship with smartphone addiction; examples: The relationship between addiction to smartphone usage and depression among adults: A crosssectional study, Smartphone addiction among university students in the light of some variables, and Examining the effects of motives and gender differences on smartphone addiction.*

*8.	I believe that the testable hypotheses are clear but I suggest to be more in a direct way. Why use “weak or possibly” for example? Why “a strongly”? The results will explain these.*

Fair point. Qualifying words have been removed.

*9.	Also, a clear research question need to be stated in the end of the introduction section.*

We re-wrote the second half of the introduction to clarify our research question and contribution.

*10.	How can the researchers explain that the sample represent ALL China? We know the cultural diversity in a “BIG” China.*

*11.	Need more explanation about the sample. Researchers stated it is random sample. How? Clarification is needed.*

*12.	I suggest that the method section needs to start with sample.*

*13.	No need for the margin in the end of page 5. This information is vital and essential procedures. Need to be moved in the body of the research.*

*14.	Validity and reliability are needed for thew measurements.*

*15.	Sample description is needed in the method section, sample.*

*16.	Figure ?? and Table ?? are  noticed. Need to number the figures and tables.*

This may be a font issue, as our version of the PDF does not contain any missing figure or table numbers, nor does the LaTeX file. Happy to help troubleshoot further but everything on our end looks complete.

### 2024-03-19 tandf/Social Isolation in China.qmd
Revision updates

@@
 date: '`r format(Sys.time(), "%B %d, %Y")`'
-abstract: "Early research and popular discourse on the promise of the internet's impact on social isolation was optimistic.
-Since these early predictions, research has become less positive, usually pointing to the negative role of social media, withn more recent studies focused on heterogeneous effects.
-Using data from a nationwide survey of Chinese citizens to gain leverage on this disagreement in the literature, our research finds support for those that have focused on heterogeneous effects - we find that urbancity is a key moderating variable.
-Additionally, our results lend support to a FOMO mechanism while they are not suggestive of a mechanism by which negative content is the channel through which social media generates feelings of social isolations.
-Overall, our findings suggest that institutional context may not play an important role in the social media - social isolation relationship."
+abstract: "Research on the link between social media and well being has lead to ambiguous findings - some research has found a positive, negative, and mixed relationship between the two.
+We employ the case of China, in which social media is controlled in important ways, as a useful alternative case to gain leverage on these ambiguities.
+Using data from a nationwide survey of Chinese citizens (n=2292), we principally find that individual, heterogeneous effects are an important driver of the relationship between levels of social media use and reported well-being.
+Additionally, our results lend support to a FOMO (fear of missing out) mechanism as an important driver of the relationship while not finding support for the mechanism of exposure to negative content on social media as a predictor of well-being.
+Finally, our findings suggest that institutional context may not play an important role in the social media - social isolation relationship."
 keywords: [Social Isolation, Social Media, Digital Communication, China]
@@
 csl: taylor-and-francis-apa.csl
+shift-heading-level-by: -1
 ---
@@
 
-# Social Isolation in China
-
 ## Introduction
@@
 Research is quite mixed when it comes to identifying the relationship between social media use and feelings of isolationism.
-Early research suggested that the internet would build social capital, or an interconnectedness between people, and that social media platforms were the ultimate way to bring people together.
-Since then, research on the subject has been decidedly more mixed.
+Early research suggested that the internet would build social capital, or an interconnectedness between people, and that social media platforms were the ultimate way to bring people together [@ellison2007].
+Since then, research on the subject has been decidedly more mixed [@duradoni2020; @jiménez2022; @valkenburg2022].
 On one hand, some authors have found social media may encourage social isolation, and ultimately, social media users may feel more disconnected from others than those who do not use social media.
 On the other hand, others have found that there is only a minimal relationship between these two variables.
-More recent scholarship has suggested that social media may produce heterogeneous effects on individuals.
-This study uses the little-studied Chinese social media environment to try and gain leverage on this question - the Chinese online environment has certain features that should both moderate and exacerbate key causal pathways previously identified in the literature.
-To we employ a large survey of Chinese internet users and test a variety of regression specifications.[^1] The main result is that social media use is generally negatively related to social isolation, though the nature of this relationship changes depending on the urbanicity of the respondent - being in a rural area amplifies this relationship.
-This finding lends support both to the previous negative relationship findings and also reinforce the findings that emphasize heterogeneous effects.
+More recent scholarship has suggested that social media use may produce heterogeneous effects on individuals' sense of well-being [@ivie2020; @ostic2021].
+
+This study uses the little-studied Chinese social media environment to answer two research questions that remain unresolved in the literature: 1) through which channels or mechanisms do possible heterogeneous effects operate through and 2) how much does internet context change the relationship between social isolation and social media use.
+The reason that we believe the case of China can be helpful in answering these question is that Chinese online environment has certain features that should both moderate and exacerbate key causal pathways previously identified in the literature.
+To resolve these debates, we employ a large survey (n=2292) of Chinese internet users and test a variety of regression specifications.[^1] The main result is that social media use is generally negatively related to social isolation, though the nature of this relationship changes depending on the urbanicity of the respondent - being in a rural area amplifies this relationship.
+These results are consistent with a mechanism that links the two via the harmfulness of being exposed to constant online comparisons (so-called FOMO or fear of missing out).
+However, the contextual differences of the Chinese internet compared to the Western intern do not appear to significantly alter the relationship.
 
@@
 
-The existing literature on social isolation and social media use generally finds a negative to null relationship between the two variables, while the most recent research has suggested that social media has heterogeneous effects.
-Based on this existing literature, we then develop some testable hypotheses regarding how the relationship between usage and isolation may vary in the context of China.
-The result of these hypotheses tests will help to better understand the possible mechanism that links these two variables.
-
-Initially, scholars imagined that social media would create more opportunities for users to create unique and fulfilling social relationships.
+Initially, scholars imagined that social media would create more opportunities for users to create unique and fulfilling social relationships [@ellison2007; @steinfield2008; @subrahmanyam2008].
 The early theorizing about the possible benefits of social media hypothesized three important mechanisms by which social media could decrease loneliness.
-1) creating more opportunities for online to offline meetups and 2) helping to alleviate feelings of isolation for those who have difficulty making in-person social connections via joining an online communities, and 3) facilitating keeping in touch with family and friends [@ellison2007; @steinfield2008; @subrahmanyam2008].
+1) creating more opportunities for online to offline meetups and 2) helping to alleviate feelings of isolation for those who have difficulty making in-person social connections via joining an online communities, and 3) facilitating keeping in touch with family and friends.
 
@@
 Most of the existing research on the subject focuses on Western highly developed societies, and this focus may limit variation on key independent variables given the similar social and institutional context in which users are embedded.
+In particular, we believe the case of China can provide leverage in three areas that existing theories have difficulty resolving.
+The first is that
+
 To address this problem, this study aims to understand how these complex dynamics interact in the non-Western setting of China.
@@
 If one of the main mechanisms through which social media promotes social isolation occurs is exposure to negative content, then this highly regulated online environment should lead to a weaker relationship between social media use and isolation.
-Suggestive of this is a a study by Liu and Liu that finds Chinese who consumed more commercialized and sensationalized media reported more trauma during the first COVID-19 outbreak in China than those who followed government sources [@liu2020].
+Suggestive of this is a study by Liu and Liu that finds Chinese who consumed more commercialized and sensationalized media reported more trauma during the first COVID-19 outbreak in China than those who followed government sources [@liu2020].
 
@@
 
--   **H1a:** social media use should have a weak or possibly positive connection to social isolation due to strengthened government control over online content
+-   **H1a:** social media use should have a positive connection to social isolation due to strengthened government control over online content
 
--   **H1b:** social media use should have a strongly negative connection to social isolation due to the dominance of influencer culture in China, possibly moderated by age.
+-   **H1b:** social media use should have a negative connection to social isolation due to the dominance of influencer culture in China, moderated by age.
 

### 2024-03-19 tandf/Social-Isolation-in-China.tex
Revision updates

@@
 
-%
-
-%\author{
-%\name{A.~N. Author\textsuperscript{a}\thanks{CONTACT A.~N. Author. Email: latex.helpdesk@tandf.co.uk} and John Smith\textsuperscript{b}}
-%\affil{\textsuperscript{a}Taylor \& Francis, 4 Park Square, Milton Park, Abingdon, UK; \textsuperscript{b}Institut f\"{u}r Informatik, Albert-Ludwigs-Universit\"{a}t, Freiburg, Germany}
-%}
+\author{\name{\textsuperscript{a} and }
+\affil{\textsuperscript{a}
+\textsuperscript{b}}}
 
@@
 \begin{abstract}
-Early research and popular discourse on the promise of the internet's
-impact on social isolation was optimistic. Since these early
-predictions, research has become less positive, usually pointing to the
-negative role of social media, withn more recent studies focused on
-heterogeneous effects. Using data from a nationwide survey of Chinese
-citizens to gain leverage on this disagreement in the literature, our
-research finds support for those that have focused on heterogeneous
-effects - we find that urbancity is a key moderating variable.
-Additionally, our results lend support to a FOMO mechanism while they
-are not suggestive of a mechanism by which negative content is the
-channel through which social media generates feelings of social
-isolations. Overall, our findings suggest that institutional context may
-not play an important role in the social media - social isolation
-relationship.
+Research on the link between social media and well being has lead to
+ambiguous findings - some research has found a positive, negative, and
+mixed relationship between the two. We employ the case of China, in
+which social media is controlled in important ways, as a useful
+alternative case to gain leverage on these ambiguities. Using data from
+a nationwide survey of Chinese citizens (n=2292), we principally find
+that individual, heterogeneous effects are an important driver of the
+relationship between levels of social media use and reported well-being.
+Additionally, our results lend support to a FOMO (fear of missing out)
+mechanism as an important driver of the relationship while not finding
+support for the mechanism of exposure to negative content on social
+media as a predictor of well-being. Finally, our findings suggest that
+institutional context may not play an important role in the social media
+- social isolation relationship.
 \end{abstract}
@@
     China
-\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, boxrule=0pt, interior hidden, sharp corners, frame hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
+\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, breakable, enhanced, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi
 
@@
 
-\hypertarget{social-isolation-in-china}{%
-\section{Social Isolation in China}\label{social-isolation-in-china}}
-
 \hypertarget{introduction}{%
-\subsection{Introduction}\label{introduction}}
+\section{Introduction}\label{introduction}}
 
@@
 is only a minimal relationship between these two variables. More recent
-scholarship has suggested that social media may produce heterogeneous
-effects on individuals. This study uses the little-studied Chinese
-social media environment to try and gain leverage on this question - the
-Chinese online environment has certain features that should both
-moderate and exacerbate key causal pathways previously identified in the
-literature. To we employ a large survey of Chinese internet users and
-test a variety of regression specifications.\footnote{All data and
-  analysis files for this research are available at the author's
-  website.} The main result is that social media use is generally
-negatively related to social isolation, though the nature of this
-relationship changes depending on the urbanicity of the respondent -
-being in a rural area amplifies this relationship. This finding lends
-support both to the previous negative relationship findings and also
-reinforce the findings that emphasize heterogeneous effects.
+scholarship has suggested that social media use may produce
+heterogeneous effects on individuals' sense of well-being. This study
+uses the little-studied Chinese social media environment to try and gain
+leverage on this question - the Chinese online environment has certain
+features that should both moderate and exacerbate key causal pathways
+previously identified in the literature. To resolve these debates, we
+employ a large survey (n=2292) of Chinese internet users and test a
+variety of regression specifications.\footnote{All data and analysis
+  files for this research are available at the author's website.} The
+main result is that social media use is generally negatively related to
+social isolation, though the nature of this relationship changes
+depending on the urbanicity of the respondent - being in a rural area
+amplifies this relationship. This finding lends support both to the
+previous negative relationship findings and also reinforce the findings
+that emphasize heterogeneous effects.
 
 \hypertarget{literature-review-and-theory}{%
-\subsection{Literature Review and
+\section{Literature Review and
 Theory}\label{literature-review-and-theory}}
-
-The existing literature on social isolation and social media use
-generally finds a negative to null relationship between the two
-variables, while the most recent research has suggested that social
-media has heterogeneous effects. Based on this existing literature, we
-then develop some testable hypotheses regarding how the relationship
-between usage and isolation may vary in the context of China. The result
-of these hypotheses tests will help to better understand the possible
-mechanism that links these two variables.
 
@@
 opportunities for users to create unique and fulfilling social
-relationships. The early theorizing about the possible benefits of
-social media hypothesized three important mechanisms by which social
-media could decrease loneliness. 1) creating more opportunities for
-online to offline meetups and 2) helping to alleviate feelings of
-isolation for those who have difficulty making in-person social
-connections via joining an online communities, and 3) facilitating
-keeping in touch with family and friends (Ellison et al., 2007;
-Steinfield et al., 2008; Subrahmanyam et al., 2008).
+relationships (Ellison et al., 2007; Steinfield et al., 2008;
+Subrahmanyam et al., 2008). The early theorizing about the possible
+benefits of social media hypothesized three important mechanisms by
+which social media could decrease loneliness. 1) creating more
+opportunities for online to offline meetups and 2) helping to alleviate
+feelings of isolation for those who have difficulty making in-person
+social connections via joining an online communities, and 3)
+facilitating keeping in touch with family and friends.
 
@@
 independent variables given the similar social and institutional context
-in which users are embedded. To address this problem, this study aims to
-understand how these complex dynamics interact in the non-Western
-setting of China. Relatively little is known about China's level of
-social isolation, though what evidence that does exist suggests that it
-is on the rise. Twenge et al.'s study found that adolescent feelings of
-loneliness have generally been on the rise in comparable East Asian
-countries (Twenge et al., 2021). News reports have highlighted the
-increasing number of people who consider themselves to be online
-outcasts or losers (\emph{diaosi}) (\emph{China{'}s Latest Social Media
-Trend}, 2016; Nan, 2013; Szablewicz, 2014). We do not aim to make a
-direct comparison between China and Western countries but rather
-highlight the way in which China's unique context helps shed light on
-which contextual factors matter in understanding the linkage between the
-two variables.
+in which users are embedded. In particular, we believe the case of China
+can provide leverage in three areas that existing theories have
+difficulty resolving. The first is that
+
+To address this problem, this study aims to understand how these complex
+dynamics interact in the non-Western setting of China. Relatively little
+is known about China's level of social isolation, though what evidence
+that does exist suggests that it is on the rise. Twenge et al.'s study
+found that adolescent feelings of loneliness have generally been on the
+rise in comparable East Asian countries (Twenge et al., 2021). News
+reports have highlighted the increasing number of people who consider
+themselves to be online outcasts or losers (\emph{diaosi})
+(\emph{China{'}s Latest Social Media Trend}, 2016; Nan, 2013;
+Szablewicz, 2014). We do not aim to make a direct comparison between
+China and Western countries but rather highlight the way in which
+China's unique context helps shed light on which contextual factors
+matter in understanding the linkage between the two variables.
 
@@
 environment should lead to a weaker relationship between social media
-use and isolation. Suggestive of this is a a study by Liu and Liu that
+use and isolation. Suggestive of this is a study by Liu and Liu that
 finds Chinese who consumed more commercialized and sensationalized media
@@
 \item
-  \textbf{H1a:} social media use should have a weak or possibly positive
-  connection to social isolation due to strengthened government control
-  over online content
-\item
-  \textbf{H1b:} social media use should have a strongly negative
-  connection to social isolation due to the dominance of influencer
-  culture in China, possibly moderated by age.
+  \textbf{H1a:} social media use should have a positive connection to
+  social isolation due to strengthened government control over online
+  content
+\item
+  \textbf{H1b:} social media use should have a negative connection to
+  social isolation due to the dominance of influencer culture in China,
+  moderated by age.
 \item
@@
 \hypertarget{data-measurement-and-descriptives}{%
-\subsection{Data, Measurement, and
+\section{Data, Measurement, and
 Descriptives}\label{data-measurement-and-descriptives}}
@@
 \hypertarget{results}{%
-\subsection{Results}\label{results}}
+\section{Results}\label{results}}
 
@@
 \hypertarget{conclusion}{%
-\subsection{Conclusion}\label{conclusion}}
+\section{Conclusion}\label{conclusion}}
 
@@
 \hypertarget{references}{%
-\subsection{References}\label{references}}
+\section{References}\label{references}}
 
@@
 \hypertarget{online-appendix}{%
-\subsection{Online Appendix}\label{online-appendix}}
+\section{Online Appendix}\label{online-appendix}}
 
 \hypertarget{variable-operationalization}{%
-\subsubsection{Variable
+\subsection{Variable
 Operationalization}\label{variable-operationalization}}
@@
 \hypertarget{residual-analysis}{%
-\subsubsection{Residual Analysis}\label{residual-analysis}}
+\subsection{Residual Analysis}\label{residual-analysis}}
 

### 2024-03-19 tandf/Social Isolation in China.qmd
More updates

@@
 Cyberbullying, or more generally, repeated and aggressive online attacks against users has been systematically linked to feelings of social isolation [@ademiluyi2022].
-Another proposed mechanism is upward comparisons of others and the weak nature of online connections - both of these have been found to generate social anxiety and social isolation [@alabri2022; @büttner2022].
+Another proposed mechanism is upward comparisons of others - users observe content of friends or influencers who post luxurious or exotic experiences which cause users to encounter feelings of unhappiness or FOMO about their own life situation [@alabri2022; @büttner2022].
 A third set of mechanisms primarily concern themselves with the physical changes that social media causes.
@@
 
-Most of the existing research on the subject focuses on Western highly developed societies, and this focus may limit variation on key independent variables given the similar social and institutional context in which users are embedded.
-In particular, we believe the case of China can provide leverage in three areas that existing theories have difficulty resolving.
-The first is that
+Most of the existing research on the subject focuses on Western highly developed societies, and this focus limits variation on key independent variables given the similar social and institutional context in which users are embedded.
+To address this problem, this study aims to understand how these complex dynamics interact in the non-Western setting of China.
+We believe the setting of China gives additional leverage to investigate issues of heterogeneity and the importance of context for several reasons.
+Firstly, the highly controlled nature of China's internet space prevents user exposure to some of the more threatening online content (such as cyberbullying) that is hypothesized to be a factor in creating a negative relationship between social media and feelings of social isolation [@wang2020].
+If this mechanism were the dominant reason for previous findings of a negative relationship between the two, one would expect the relationship to be more positive in China.
+Relatedly, China has a more commercial and robust influencer culture that often dominates user's social media consumption [@tam2019; @wei2023].
+If the main pathway creating a negative relationship is via user's comparisons of their lives with others (FOMO), we expect the relationship between social media use and feelings of social isolation to be greater in China.
 
-To address this problem, this study aims to understand how these complex dynamics interact in the non-Western setting of China.
-Relatively little is known about China's level of social isolation, though what evidence that does exist suggests that it is on the rise.
-Twenge et al.'s study found that adolescent feelings of loneliness have generally been on the rise in comparable East Asian countries [@twenge2021].
-News reports have highlighted the increasing number of people who consider themselves to be online outcasts or losers (*diaosi*) [@nan2013; @szablewicz2014; @chinas2016].
-We do not aim to make a direct comparison between China and Western countries but rather highlight the way in which China's unique context helps shed light on which contextual factors matter in understanding the linkage between the two variables.
+Finally, China has undergone a period of very rapid urbanization in the last 40 years, a development that has brought about enormous changes to traditional social structures [@xu2014].
+This rapid urbanization can help test two important unresolved questions in the existing literature that are difficult to resolve given that urbanization in Western countries is a process that largely finished by the advent of social media.
+The first is whether social media can provide a means to decrease social isolation among those who actively seek it out to make friends.
+China's rapid urbanization and attendant human migration has created a large population of people that lack strong social bonds and may use social media as a method to create new social bonds (as the earlier theorists of social media hypothesized users may employ the technology).
+The existing literature on the West finds that urbanicity is an important factor in levels and mechanisms for social isolation; many studies of Western societies have found that rural residents, while having stronger familial bonds, also can more easily experience social isolation without those bonds [@kaye2017; @koning2017; @henning-smith2018].
+Social media use in China could therefore either help mitigate the feelings of isolation brought on by rapid urbanization by connecting family members who have left the countryside for urban work (based on the earlier, more positive views of social media's potential) or amplify further the feelings of isolation due to several of the proposed negative relationship mechanisms.
 
-The most important of these contextual factor in China is that social media space that is highly controlled online environment.
-Many people are aware that the Chinese government heavily censors politically sensitive content on online platforms.
-Fewer are aware that the Chinese government spends as much, if not more, effort to clean up non-political negative or distressing content on the Chinese internet, such as scams, instances of cyber bullying, disturbing videos, and vulgar content [@wang2020].
-This control impulse also extends content the government views as spiritually polluting, such as pornography, scantily dressed women, and other escapist content.
-While the Chinese government and online platforms are not 100 per cent effective in their ability to completely stamp out such content, the default is that such content is actively restricted, while US platforms tent to take a more pro-speech regulatory position [@liu2022].
-If one of the main mechanisms through which social media promotes social isolation occurs is exposure to negative content, then this highly regulated online environment should lead to a weaker relationship between social media use and isolation.
-Suggestive of this is a study by Liu and Liu that finds Chinese who consumed more commercialized and sensationalized media reported more trauma during the first COVID-19 outbreak in China than those who followed government sources [@liu2020].
-
-On the other hand, China also has a highly robust online influencer culture.
-While social media influencers are a global phenomena, China has perhaps the most commercialized version of influencing.
-Social media influencers are developed by large agencies and work in an almost assembly-line fashion to promote products on livestreams or pitch sponsored products.
-In this influencer culture, less attention is paid to authenticity and personality and relatively more emphasis is placed on consumerism, brand promotion, and image [@tam2019; @wei2023].
-Given that previous research has suggested one of the main channels through which social media creates feelings of isolation is negative personal comparisons with online content (so-called "FOMO" - fear of missing out), heavy social media use may increase the strength of the relationship between social media use and social isolation through consumption of such highly commercialized content.
-These influencers are most popular among young consumers so one may expect that only younger users would experience these effects.
-
-Additionally, China's social media environment is relatively unique in that the dominant messaging platform is also the largest social media app (WeChat).
-Users can use it simply to chat with family and friends, they can use it to post photos and other content about their life in a feed that works similarly to Facebook, or they can browse videos of others in a method similar to Tiktok.
-Previous research has indicated that while, on the whole, social media increases social isolation, for users that primarily use it to contact friends and family, its use can counteract the negative effects [@hajek2019; @lim2020].
-In this way, those that heavily use these type of combined platforms may engage in multiple uses of social media that tend to cancel each other out.
-Given the ubiquity of WeChat in China, such a relationship seems plausible.
-
-Finally, the nexus of social isolation and social media use in China has played out in the context of one of the most rapid periods of urbanization in human history.
-Hundreds of millions of people have shifted from rural subsistence farming to participating in an urban market economy.
-The existing literature finds that urbanicity is an important factor in levels and mechanisms for social isolation; many studies of Western societies have found that rural residents, while having stronger familial bonds, also can more easily experience social isolation without those bonds [@kaye2017; @koning2017; @henning-smith2018].
-In China, less is known about the differential effects of the urban rural divide on feelings of social isolation but the research that does exist suggests that urban environments can be especially isolating, particularly for rural to urban migrants particularly due to lack of access to traditional support systems and familial connections [@li2017].
-
-Given the existing literature and the context of China, this leads to a series of testable hypotheses.
+The case of China cannot resolve every debate in the literature or test all possible mechanisms but we do believe it can provide insight into a few of the more prominent proposed processes.
+Thus, given the existing literature and the context of China, we develop a series of testable hypotheses.
 

### 2024-03-19 tandf/Social Isolation in China.qmd
First review pass done

@@
 More recent research has reinforced the finding that the effect of social media on measures like social isolation may be highly heterogeneous across individuals; for some individuals, the effect may be quite negative for some while for others social media usage may have a modestly positive impact on well-being [@beyens2020; @ostic2021].
+For example, for some users moderate social media use may have no significant impact but for those who suffer from social media addiction, the effect can be highly negative [@alhassan2018; @aljomaa2016] (though see [@al-kandari2021; @chen2017] for more complex findings).
 
@@
 Social media use has been shown to displace face to face activity, which leads to greater social isolation [@larson2018].
-Heavy social media use also decreases hours of sleep, leading to greater feelings of anxiety and more social isolation [@twenge2017].
 The current research suggests that which of these mechanisms is dominant depends on the age/demographic group in question and the societal context [@twenge2019].
@@
 The case of China cannot resolve every debate in the literature or test all possible mechanisms but we do believe it can provide insight into a few of the more prominent proposed processes.
-Thus, given the existing literature and the context of China, we develop a series of testable hypotheses.
+Thus, given the existing literature and the context of China, we develop a series of testable hypotheses that shed light on our research question.
 
--   **H1a:** social media use should have a positive connection to social isolation due to strengthened government control over online content
+-   **H$1_a$**: social media use should have a positive connection to social isolation due to strengthened government control over online content
 
--   **H1b:** social media use should have a negative connection to social isolation due to the dominance of influencer culture in China, moderated by age.
+-   **H$1_b$**: social media use should have a negative connection to social isolation due to the dominance of influencer culture in China, moderated by age.
 
--   **H2:** those who are able to use social media to make new friends will have lower social isolation scores than those who do not
+-   **H$2$**: those who are able to use social media to make new friends will have lower social isolation scores than those who do not
 
--   **H3:** the urban/rural divide will produce differential impacts in the above hypotheses on the relationship between social media use and social isolation
+-   **H$3$:** the urban/rural divide will produce differential impacts in the above hypotheses on the relationship between social media use and social isolation
 

### 2024-03-19 tandf/Social-Isolation-in-China.tex
First review pass done

@@
     China
-\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, breakable, enhanced, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi
+\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, breakable, sharp corners, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi
 
@@
 interconnectedness between people, and that social media platforms were
-the ultimate way to bring people together. Since then, research on the
-subject has been decidedly more mixed. On one hand, some authors have
-found social media may encourage social isolation, and ultimately,
-social media users may feel more disconnected from others than those who
-do not use social media. On the other hand, others have found that there
-is only a minimal relationship between these two variables. More recent
-scholarship has suggested that social media use may produce
-heterogeneous effects on individuals' sense of well-being. This study
-uses the little-studied Chinese social media environment to try and gain
-leverage on this question - the Chinese online environment has certain
-features that should both moderate and exacerbate key causal pathways
-previously identified in the literature. To resolve these debates, we
-employ a large survey (n=2292) of Chinese internet users and test a
-variety of regression specifications.\footnote{All data and analysis
-  files for this research are available at the author's website.} The
-main result is that social media use is generally negatively related to
-social isolation, though the nature of this relationship changes
-depending on the urbanicity of the respondent - being in a rural area
-amplifies this relationship. This finding lends support both to the
-previous negative relationship findings and also reinforce the findings
-that emphasize heterogeneous effects.
+the ultimate way to bring people together (Ellison et al., 2007). Since
+then, research on the subject has been decidedly more mixed (Duradoni et
+al., 2020; Jiménez et al., 2022; Valkenburg et al., 2022). On one hand,
+some authors have found social media may encourage social isolation, and
+ultimately, social media users may feel more disconnected from others
+than those who do not use social media. On the other hand, others have
+found that there is only a minimal relationship between these two
+variables. More recent scholarship has suggested that social media use
+may produce heterogeneous effects on individuals' sense of well-being
+(Ivie et al., 2020; Ostic et al., 2021).
+
+This study uses the little-studied Chinese social media environment to
+answer two research questions that remain unresolved in the literature:
+1) through which channels or mechanisms do possible heterogeneous
+effects operate through and 2) how much does internet context change the
+relationship between social isolation and social media use. The reason
+that we believe the case of China can be helpful in answering these
+question is that Chinese online environment has certain features that
+should both moderate and exacerbate key causal pathways previously
+identified in the literature. To resolve these debates, we employ a
+large survey (n=2292) of Chinese internet users and test a variety of
+regression specifications.\footnote{All data and analysis files for this
+  research are available at the author's website.} The main result is
+that social media use is generally negatively related to social
+isolation, though the nature of this relationship changes depending on
+the urbanicity of the respondent - being in a rural area amplifies this
+relationship. These results are consistent with a mechanism that links
+the two via the harmfulness of being exposed to constant online
+comparisons (so-called FOMO or fear of missing out). However, the
+contextual differences of the Chinese internet compared to the Western
+intern do not appear to significantly alter the relationship.
 
@@
 some while for others social media usage may have a modestly positive
-impact on well-being (Beyens et al., 2020; Ostic et al., 2021).
+impact on well-being (Beyens et al., 2020; Ostic et al., 2021). For
+example, for some users moderate social media use may have no
+significant impact but for those who suffer from social media addiction,
+the effect can be highly negative (Alhassan et al., 2018; Aljomaa et
+al., 2016) (though see (Al-Kandari \& Al-Sejari, 2021; Chen et al.,
+2017) for more complex findings).
 
@@
 linked to feelings of social isolation (Ademiluyi et al., 2022). Another
-proposed mechanism is upward comparisons of others and the weak nature
-of online connections - both of these have been found to generate social
-anxiety and social isolation (Alabri, 2022; Büttner \& Rudert, 2022). A
-third set of mechanisms primarily concern themselves with the physical
-changes that social media causes. Social media use has been shown to
-displace face to face activity, which leads to greater social isolation
-(Larson et al., 2018). Heavy social media use also decreases hours of
-sleep, leading to greater feelings of anxiety and more social isolation
-(Twenge et al., 2017). The current research suggests that which of these
-mechanisms is dominant depends on the age/demographic group in question
-and the societal context (Twenge, 2019).
+proposed mechanism is upward comparisons of others - users observe
+content of friends or influencers who post luxurious or exotic
+experiences which cause users to encounter feelings of unhappiness or
+FOMO about their own life situation (Alabri, 2022; Büttner \& Rudert,
+2022). A third set of mechanisms primarily concern themselves with the
+physical changes that social media causes. Social media use has been
+shown to displace face to face activity, which leads to greater social
+isolation (Larson et al., 2018). The current research suggests that
+which of these mechanisms is dominant depends on the age/demographic
+group in question and the societal context (Twenge, 2019).
 
 Most of the existing research on the subject focuses on Western highly
-developed societies, and this focus may limit variation on key
-independent variables given the similar social and institutional context
-in which users are embedded. In particular, we believe the case of China
-can provide leverage in three areas that existing theories have
-difficulty resolving. The first is that
-
-To address this problem, this study aims to understand how these complex
-dynamics interact in the non-Western setting of China. Relatively little
-is known about China's level of social isolation, though what evidence
-that does exist suggests that it is on the rise. Twenge et al.'s study
-found that adolescent feelings of loneliness have generally been on the
-rise in comparable East Asian countries (Twenge et al., 2021). News
-reports have highlighted the increasing number of people who consider
-themselves to be online outcasts or losers (\emph{diaosi})
-(\emph{China{'}s Latest Social Media Trend}, 2016; Nan, 2013;
-Szablewicz, 2014). We do not aim to make a direct comparison between
-China and Western countries but rather highlight the way in which
-China's unique context helps shed light on which contextual factors
-matter in understanding the linkage between the two variables.
-
-The most important of these contextual factor in China is that social
-media space that is highly controlled online environment. Many people
-are aware that the Chinese government heavily censors politically
-sensitive content on online platforms. Fewer are aware that the Chinese
-government spends as much, if not more, effort to clean up non-political
-negative or distressing content on the Chinese internet, such as scams,
-instances of cyber bullying, disturbing videos, and vulgar content
-(Wang, 2020). This control impulse also extends content the government
-views as spiritually polluting, such as pornography, scantily dressed
-women, and other escapist content. While the Chinese government and
-online platforms are not 100 per cent effective in their ability to
-completely stamp out such content, the default is that such content is
-actively restricted, while US platforms tent to take a more pro-speech
-regulatory position (J. Liu \& Yang, 2022). If one of the main
-mechanisms through which social media promotes social isolation occurs
-is exposure to negative content, then this highly regulated online
-environment should lead to a weaker relationship between social media
-use and isolation. Suggestive of this is a study by Liu and Liu that
-finds Chinese who consumed more commercialized and sensationalized media
-reported more trauma during the first COVID-19 outbreak in China than
-those who followed government sources (C. Liu \& Liu, 2020).
-
-On the other hand, China also has a highly robust online influencer
-culture. While social media influencers are a global phenomena, China
-has perhaps the most commercialized version of influencing. Social media
-influencers are developed by large agencies and work in an almost
-assembly-line fashion to promote products on livestreams or pitch
-sponsored products. In this influencer culture, less attention is paid
-to authenticity and personality and relatively more emphasis is placed
-on consumerism, brand promotion, and image (Tam, 2019; Wei, 2023). Given
-that previous research has suggested one of the main channels through
-which social media creates feelings of isolation is negative personal
-comparisons with online content (so-called ``FOMO'' - fear of missing
-out), heavy social media use may increase the strength of the
-relationship between social media use and social isolation through
-consumption of such highly commercialized content. These influencers are
-most popular among young consumers so one may expect that only younger
-users would experience these effects.
-
-Additionally, China's social media environment is relatively unique in
-that the dominant messaging platform is also the largest social media
-app (WeChat). Users can use it simply to chat with family and friends,
-they can use it to post photos and other content about their life in a
-feed that works similarly to Facebook, or they can browse videos of
-others in a method similar to Tiktok. Previous research has indicated
-that while, on the whole, social media increases social isolation, for
-users that primarily use it to contact friends and family, its use can
-counteract the negative effects (Hajek \& König, 2019; Lim et al.,
-2020). In this way, those that heavily use these type of combined
-platforms may engage in multiple uses of social media that tend to
-cancel each other out. Given the ubiquity of WeChat in China, such a
-relationship seems plausible.
-
-Finally, the nexus of social isolation and social media use in China has
-played out in the context of one of the most rapid periods of
-urbanization in human history. Hundreds of millions of people have
-shifted from rural subsistence farming to participating in an urban
-market economy. The existing literature finds that urbanicity is an
-important factor in levels and mechanisms for social isolation; many
-studies of Western societies have found that rural residents, while
+developed societies, and this focus limits variation on key independent
+variables given the similar social and institutional context in which
+users are embedded. To address this problem, this study aims to
+understand how these complex dynamics interact in the non-Western
+setting of China. We believe the setting of China gives additional
+leverage to investigate issues of heterogeneity and the importance of
+context for several reasons. Firstly, the highly controlled nature of
+China's internet space prevents user exposure to some of the more
+threatening online content (such as cyberbullying) that is hypothesized
+to be a factor in creating a negative relationship between social media
+and feelings of social isolation (Wang, 2020). If this mechanism were
+the dominant reason for previous findings of a negative relationship
+between the two, one would expect the relationship to be more positive
+in China. Relatedly, China has a more commercial and robust influencer
+culture that often dominates user's social media consumption (Tam, 2019;
+Wei, 2023). If the main pathway creating a negative relationship is via
+user's comparisons of their lives with others (FOMO), we expect the
+relationship between social media use and feelings of social isolation
+to be greater in China.
+
+Finally, China has undergone a period of very rapid urbanization in the
+last 40 years, a development that has brought about enormous changes to
+traditional social structures (Xu \& Xia, 2014). This rapid urbanization
+can help test two important unresolved questions in the existing
+literature that are difficult to resolve given that urbanization in
+Western countries is a process that largely finished by the advent of
+social media. The first is whether social media can provide a means to
+decrease social isolation among those who actively seek it out to make
+friends. China's rapid urbanization and attendant human migration has
+created a large population of people that lack strong social bonds and
+may use social media as a method to create new social bonds (as the
+earlier theorists of social media hypothesized users may employ the
+technology). The existing literature on the West finds that urbanicity
+is an important factor in levels and mechanisms for social isolation;
+many studies of Western societies have found that rural residents, while
 having stronger familial bonds, also can more easily experience social
 isolation without those bonds (Henning-Smith et al., 2018; Kaye, 2017;
-Koning et al., 2017). In China, less is known about the differential
-effects of the urban rural divide on feelings of social isolation but
-the research that does exist suggests that urban environments can be
-especially isolating, particularly for rural to urban migrants
-particularly due to lack of access to traditional support systems and
-familial connections (Li \& Rose, 2017).
-
-Given the existing literature and the context of China, this leads to a
-series of testable hypotheses.
+Koning et al., 2017). Social media use in China could therefore either
+help mitigate the feelings of isolation brought on by rapid urbanization
+by connecting family members who have left the countryside for urban
+work (based on the earlier, more positive views of social media's
+potential) or amplify further the feelings of isolation due to several
+of the proposed negative relationship mechanisms.
+
+The case of China cannot resolve every debate in the literature or test
+all possible mechanisms but we do believe it can provide insight into a
+few of the more prominent proposed processes. Thus, given the existing
+literature and the context of China, we develop a series of testable
+hypotheses that shed light on our research question.
 
@@
 \item
-  \textbf{H1a:} social media use should have a positive connection to
-  social isolation due to strengthened government control over online
+  \textbf{H\(1_a\)}: social media use should have a positive connection
+  to social isolation due to strengthened government control over online
   content
 \item
-  \textbf{H1b:} social media use should have a negative connection to
-  social isolation due to the dominance of influencer culture in China,
-  moderated by age.
-\item
-  \textbf{H2:} those who are able to use social media to make new
+  \textbf{H\(1_b\)}: social media use should have a negative connection
+  to social isolation due to the dominance of influencer culture in
+  China, moderated by age.
+\item
+  \textbf{H\(2\)}: those who are able to use social media to make new
   friends will have lower social isolation scores than those who do not
 \item
-  \textbf{H3:} the urban/rural divide will produce differential impacts
-  in the above hypotheses on the relationship between social media use
-  and social isolation
+  \textbf{H\(3\):} the urban/rural divide will produce differential
+  impacts in the above hypotheses on the relationship between social
+  media use and social isolation
 \end{itemize}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-alhassan2018}{}}%
+Alhassan, A. A., Alqadhib, E. M., Taha, N. W., Alahmari, R. A., Salam,
+M., \& Almutairi, A. F. (2018). The relationship between addiction to
+smartphone usage and depression among adults: a cross sectional study.
+\emph{BMC Psychiatry}, \emph{18}(1), 1--8.
+\url{https://doi.org/10.1186/s12888-018-1745-4}
+
+\leavevmode\vadjust pre{\hypertarget{ref-aljomaa2016}{}}%
+Aljomaa, S. S., Al.Qudah, M. F., Albursan, I. S., Bakhiet, S. F., \&
+Abduljabbar, A. S. (2016). Smartphone addiction among university
+students in the light of some variables. \emph{Computers in Human
+Behavior}, \emph{61}, 155--164.
+\url{https://doi.org/10.1016/j.chb.2016.03.041}
+
+\leavevmode\vadjust pre{\hypertarget{ref-al-kandari2021}{}}%
+Al-Kandari, Y. Y., \& Al-Sejari, M. M. (2021). Social isolation, social
+support and their relationship with smartphone addiction.
+\emph{Information, Communication \& Society}, \emph{24}(13), 1925--1943.
+\url{https://doi.org/10.1080/1369118X.2020.1749698}
+
 \leavevmode\vadjust pre{\hypertarget{ref-appel2020}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-chinas2016}{}}%
-\emph{China{'}s latest social media trend: Diaosi / loser subculture}.
-(2016).
-\url{https://www.appnova.com/chinas-latest-social-media-trend-diaosi-loser-subculture/}
+\leavevmode\vadjust pre{\hypertarget{ref-chen2017}{}}%
+Chen, C., Zhang, K. Z. K., Gong, X., Zhao, S. J., Lee, M. K. O., \&
+Liang, L. (2017). Examining the effects of motives and gender
+differences on smartphone addiction. \emph{Computers in Human Behavior},
+\emph{75}, 891--902. \url{https://doi.org/10.1016/j.chb.2017.07.002}
+
+\leavevmode\vadjust pre{\hypertarget{ref-duradoni2020}{}}%
+Duradoni, M., Innocenti, F., \& Guazzini, A. (2020). Well-Being and
+Social Media: A Systematic Review of Bergen Addiction Scales.
+\emph{Future Internet}, \emph{12}(2), 24.
+\url{https://doi.org/10.3390/fi12020024}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-hajek2019}{}}%
-Hajek, A., \& König, H.-H. (2019). The association between use of online
-social networks sites and perceived social isolation among individuals
-in the second half of life: results based on a nationally representative
-sample in Germany. \emph{BMC Public Health}, \emph{19}(1), 40.
-\url{https://doi.org/10.1186/s12889-018-6369-6}
-
 \leavevmode\vadjust pre{\hypertarget{ref-henning-smith2018}{}}%
@@
 \url{https://doi.org/10.1093/geroni/igy023.2851}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ivie2020}{}}%
+Ivie, E. J., Pettitt, A., Moses, L. J., \& Allen, N. B. (2020). A
+meta-analysis of the association between adolescent social media use and
+depressive symptoms. \emph{Journal of Affective Disorders}, \emph{275},
+165--174. \url{https://doi.org/10.1016/j.jad.2020.06.014}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jimuxe9nez2022}{}}%
+Jiménez, A. C., Vaillancourt, M., Zhu, P., \& Seon, Q. (2022). Social
+Media and Mental Health: What We Know. \emph{McGill Journal of
+Medicine}, \emph{20}(2). \url{https://doi.org/10.26443/mjm.v20i2.852}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-li2017}{}}%
-Li, J., \& Rose, N. (2017). Urban social exclusion and mental health of
-China's rural-urban migrants {\textendash} A review and call for
-research. \emph{Health \& Place}, \emph{48}, 20--30.
-\url{https://doi.org/10.1016/j.healthplace.2017.08.009}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lim2020}{}}%
-Lim, M. H., Eres, R., \& Vasan, S. (2020). Understanding loneliness in
-the twenty-first century: An update on correlates, risk factors, and
-potential solutions. \emph{Social Psychiatry and Psychiatric
-Epidemiology}, \emph{55}(7), 793--810.
-\url{https://doi.org/10.1007/s00127-020-01889-7}
-
-\leavevmode\vadjust pre{\hypertarget{ref-liu2020}{}}%
-Liu, C., \& Liu, Y. (2020). Media Exposure and Anxiety during COVID-19:
-The Mediation Effect of Media Vicarious Traumatization.
-\emph{International Journal of Environmental Research and Public
-Health}, \emph{17}(13), 4720.
-\url{https://doi.org/10.3390/ijerph17134720}
-
-\leavevmode\vadjust pre{\hypertarget{ref-liu2022}{}}%
-Liu, J., \& Yang, L. (2022). {``}Dual-Track{''} platform governance on
-content: A comparative study between China and United States.
-\emph{Policy \& Internet}, \emph{14}(2), 304--323.
-\url{https://doi.org/10.1002/poi3.307}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nan2013}{}}%
-Nan, W. (2013). China's underdog youth find success in 'diaosi' - or
-'loser' - identity. \emph{South China Morning Post}.
-\url{https://www.scmp.com/news/china/article/1232976/chinas-underdog-youth-find-success-diaosi-or-loser-identity}
-
 \leavevmode\vadjust pre{\hypertarget{ref-nowland2018}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-szablewicz2014}{}}%
-Szablewicz, M. (2014). The {`}losers{'} of China{'}s Internet: Memes as
-{`}structures of feeling{'} for disillusioned young netizens.
-\emph{China Information}, \emph{28}(2), 259--275.
-\url{https://doi.org/10.1177/0920203X14531538}
-
 \leavevmode\vadjust pre{\hypertarget{ref-tam2019}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-twenge2021}{}}%
-Twenge, J. M., Haidt, J., Blake, A. B., McAllister, C., Lemon, H., \& Le
-Roy, A. (2021). Worldwide increases in adolescent loneliness.
-\emph{Journal of Adolescence}, \emph{93}, 257--269.
-\url{https://doi.org/10.1016/j.adolescence.2021.06.006}
-
-\leavevmode\vadjust pre{\hypertarget{ref-twenge2017}{}}%
-Twenge, J. M., Krizan, Z., \& Hisler, G. (2017). Decreases in
-self-reported sleep duration among U.S. adolescents
-2009{\textendash}2015 and association with new media screen time.
-\emph{Sleep Medicine}, \emph{39}, 47--53.
-\url{https://doi.org/10.1016/j.sleep.2017.08.013}
-
 \leavevmode\vadjust pre{\hypertarget{ref-valkenburg2022}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-xu2014}{}}%
+Xu, A., \& Xia, Y. (2014). The changes in mainland chinese families
+during the social transition: A critical analysis. \emph{Journal of
+Comparative Family Studies}, \emph{45}(1), 31--53.
+\url{https://doi.org/10.3138/jcfs.45.1.31}
+
 \end{CSLReferences}

### 2024-06-10 tandf/Response to reviewers jg revised.qmd
updated files from jg

--- 2024-03-19 tandf/Response to reviewers.qmd
@@
 We agree that the China section is perhaps too long.
-We have trimmed it and added links to relevant theories.
+We have trimmed it and added linkages to relevant theories.
 
@@
 
+We agree that smartphone addiction, depression, and feelings of loneliness and a sense of isolation may be related.These works have been added to the literature review.
+
 *8.	I believe that the testable hypotheses are clear but I suggest to be more in a direct way. Why use “weak or possibly” for example? Why “a strongly”? The results will explain these.*
@@
 
+We added more details about the sampling strategy in the introduction of the data and measurement section to better explain the strengths and weaknesses of our data when it comes to their external validity.
+
 *11.	Need more explanation about the sample. Researchers stated it is random sample. How? Clarification is needed.*
+
+See point 10.
 
@@
 
+The first paragraph of the methods section now addresses the sample in more detail.
+
 *13.	No need for the margin in the end of page 5. This information is vital and essential procedures. Need to be moved in the body of the research.*
 
-*14.	Validity and reliability are needed for thew measurements.*
+We are not sure to exactly what the reviewer is referring here.
+We think the reference is to the footnote at the end of page 5, and there's a typo in the reviewer's comment ("margin" should be "footnote").
+We assumed this was the case.
+If so, we decided to leave the footnote as is.
+Because we added more description of the sample in the main body of the text, and the footnote draws attention to the fact that the adjustments we made were not related to the indicators used in the present studies, we thought it would unnecessarily interrupt the flow of the text.
 
-*15.	Sample description is needed in the method section, sample.*
+*14.	Validity and reliability are needed for the measurements.*
 
-*16.	Figure ?? and Table ?? are  noticed. Need to number the figures and tables.*
+We included the alpha statistic for the dependent variable; it is high at 0.86.
+We also added the reliability estimate for social media use.
+It was not high ($\alpha = 0.31$) but we moved forward with the index because the face validity is pretty clear, those who claim to use social media generally more often, claim to read political news more often, and claim to use it more than they did in the past, are likely to be more frequent social media users than those who do not do these things.
+Also we added confirmation to the measurement description that the three social media use items were all positively correlated with each other (p < 0.0001 for all pairwise relationships).
+
+*15.	Figure ?? and Table ?? are  noticed. Need to number the figures and tables.*
 

### 2024-06-10 tandf/Social Isolation in China jg revised.qmd
updated files from jg

--- 2024-03-19 tandf/Social Isolation in China.qmd
@@
 These results are consistent with a mechanism that links the two via the harmfulness of being exposed to constant online comparisons (so-called FOMO or fear of missing out).
-However, the contextual differences of the Chinese internet compared to the Western intern do not appear to significantly alter the relationship.
+However, the contextual differences of the Chinese internet compared to the Western internet do not appear to significantly alter the relationship.
 
@@
 They randomly selected 2292 respondents from their existing panel[^2] from November 25 to December 2, 2015.
-This sample size on provides for a roughly $\pm2$ margin of error.[^3]
+This sample size on provides for a roughly $\pm2$ margin of error.[^3] While our sample is selected randomly from Qualtrics' online user panel, it isn't representative of China's entire population due to its internet-based recruitment methods.
+The sample, however, aligns well with Chinese internet users, crucial for our internet effects research.
+Compared to national data, our sample skews younger and more educated but is similar in income and gender.[^4] These demographics reflect the global digital divide and are in line with expectations for internet users in developing regions.
+Our findings are particularly relevant for understanding digital media's impact among active internet users in China.
 
@@
 We made three adjustments, none of which are related to the measures used in the current study.
+
+[^4]: See https://data.worldbank.org/country/china (go to the Country Profile), and https://www.cnnic.com.cn/AU/Introduction/Introduction/201208/t20120815_33295.htm.
 
@@
 (More than once a day, Everyday, Three-to-five days per week, One-to-two days per week, Less often, Never).
-Each was recoded so that higher values represented more social media use, rescaled to range from 0 through 1, added together, and then again, rescaled to range from 0 through 1 maintaining all original intervals.
+Each was recoded so that higher values represented more social media use, rescaled to range from 0 through 1, added together, and then again, rescaled to range from 0 through 1 maintaining all original intervals.The Chronbach's alpha was relatively low for these three items ($\alpha = 0.31$), but we proceeded with the construction of this index because, first, the face validity is high.
+Simply, those who claim to use social media generally more often, claim to read political news more often, and claim to use it more than they did in the past, are certainly likely to be more frequent social media users than those who do not do all these things.Second, we confirmed that these three items were all positively correlated with each other (p < 0.0001 for all pairwise relationships).
 The distribution of this index is presented in @fig-sm-use-dist.

### 2024-06-10 tandf/Social Isolation in China jg revised.tex
updated files from jg

--- 2024-03-19 tandf/Social-Isolation-in-China.tex
@@
 %
-\documentclass[]{interact}
-
-\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
-\usepackage[caption=false]{subfig}% Support for small, `sub' figures and tables
-
-\usepackage[natbibapa,nodoi]{apacite}% Citation support using apacite.sty. Commands using natbib.sty MUST be deactivated first!
-\setlength\bibhang{12pt}% To set the indentation in the list of references using apacite.sty. Commands using natbib.sty MUST be deactivated first!
-\renewcommand\bibliographytypesize{\fontsize{10}{12}\selectfont}% To set the list of references in 10 point font using apacite.sty. Commands using natbib.sty MUST be deactivated first!
-
-\let\subcaption\relax
-\let\subfloat\relax
-
-\theoremstyle{plain}% Theorem-like structures provided by amsthm.sty
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{proposition}[theorem]{Proposition}
-
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-
-\theoremstyle{remark}
-\newtheorem{remark}{Remark}
-\newtheorem{notation}{Notation}
+\documentclass[
+  letterpaper,
+  DIV=11,
+  numbers=noendperiod]{scrartcl}
 
@@
 \setlength{\emergencystretch}{3em} % prevent overfull lines
-\setcounter{secnumdepth}{5}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 % Make \paragraph and \subparagraph free-standing
@@
 \makeatother
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
 
-\makeatletter
-\makeatother
-\makeatletter
-\makeatother
+\KOMAoption{captions}{tableheading}
 \makeatletter
@@
 \makeatletter
+\makeatother
+\makeatletter
 \@ifpackageloaded{caption}{}{\usepackage{caption}}
 \@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
-\makeatother
-\makeatletter
-\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
-\makeatother
-\makeatletter
-\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
-\makeatother
-\makeatletter
-\makeatother
-\makeatletter
 \makeatother
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{bookmark}
+
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
@@
 
-\begin{document}
 \title{Lonely and online: an investigation of social media use and
 social isolation in China}
-
-\author{\name{\textsuperscript{a} and }
-\affil{\textsuperscript{a}
-\textsuperscript{b}}}
-
+\author{}
+\date{2024-06-10}
+
+\begin{document}
 \maketitle
-
 \begin{abstract}
@@
 
-\begin{keywords}
-    Social Isolation, Social Media, Digital Communication, 
-    China
-\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, breakable, sharp corners, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi
-
 \newpage{}
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\section{Introduction}\label{introduction}
 
@@
 contextual differences of the Chinese internet compared to the Western
-intern do not appear to significantly alter the relationship.
-
-\hypertarget{literature-review-and-theory}{%
+internet do not appear to significantly alter the relationship.
+
 \section{Literature Review and
-Theory}\label{literature-review-and-theory}}
+Theory}\label{literature-review-and-theory}
 
@@
 
-\hypertarget{data-measurement-and-descriptives}{%
 \section{Data, Measurement, and
-Descriptives}\label{data-measurement-and-descriptives}}
+Descriptives}\label{data-measurement-and-descriptives}
 
@@
   adjustments, none of which are related to the measures used in the
-  current study.}
+  current study.} While our sample is selected randomly from Qualtrics'
+online user panel, it isn't representative of China's entire population
+due to its internet-based recruitment methods. The sample, however,
+aligns well with Chinese internet users, crucial for our internet
+effects research. Compared to national data, our sample skews younger
+and more educated but is similar in income and gender.\footnote{See
+  https://data.worldbank.org/country/china (go to the Country Profile),
+  and
+  https://www.cnnic.com.cn/AU/Introduction/Introduction/201208/t20120815\_33295.htm.}
+These demographics reflect the global digital divide and are in line
+with expectations for internet users in developing regions. Our findings
+are particularly relevant for understanding digital media's impact among
+active internet users in China.
 
@@
 
-{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-social-iso-dist-1.pdf}
+\centering{
+
+\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-social-iso-dist-1.pdf}
 
@@
 
-\end{figure}
+\end{figure}%
 
@@
 
-{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-var-dist-1.pdf}
+\centering{
+
+\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-var-dist-1.pdf}
 
@@
 through 1, added together, and then again, rescaled to range from 0
-through 1 maintaining all original intervals. The distribution of this
-index is presented in Figure~\ref{fig-sm-use-dist}. The distribution is
-relatively normal and tightly centered around the mean 0.63 with a
-standard deviation of 0.17, but there is a left skew suggesting that a
-portion of the population is not that social media active, but clearly
-the bulk of the population are.
+through 1 maintaining all original intervals.The Chronbach's alpha was
+relatively low for these three items (\(\alpha = 0.31\)), but we
+proceeded with the construction of this index because, first, the face
+validity is high. Simply, those who claim to use social media generally
+more often, claim to read political news more often, and claim to use it
+more than they did in the past, are certainly likely to be more frequent
+social media users than those who do not do all these things.Second, we
+confirmed that these three items were all positively correlated with
+each other (p \textless{} 0.0001 for all pairwise relationships). The
+distribution of this index is presented in Figure~\ref{fig-sm-use-dist}.
+The distribution is relatively normal and tightly centered around the
+mean 0.63 with a standard deviation of 0.17, but there is a left skew
+suggesting that a portion of the population is not that social media
+active, but clearly the bulk of the population are.
 
@@
 
-{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-sm-use-dist-1.pdf}
+\centering{
+
+\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-sm-use-dist-1.pdf}
 
@@
 
-{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-urban-dist-1.pdf}
+\centering{
+
+\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-urban-dist-1.pdf}
 
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\section{Results}\label{results}
 
@@
 
-\hypertarget{tbl-profile-models}{}
 \begin{table}
-\caption{\label{tbl-profile-models}Modeling Profiles of Digital Communication }\tabularnewline
+
+\caption{\label{tbl-profile-models}Modeling Profiles of Digital
+Communication}
+
+\centering{
 
@@
 \end{threeparttable}
-\end{table}
+
+}
+
+\end{table}%
 
@@
 
-\hypertarget{tbl-social-isolation-models}{}
 \begin{table}
-\caption{\label{tbl-social-isolation-models}Modeling Social Isolation }\tabularnewline
+
+\caption{\label{tbl-social-isolation-models}Modeling Social Isolation}
+
+\centering{
 
@@
 
-{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-social-isolation-interactions-1.pdf}
+\centering{
+
+\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-social-isolation-interactions-1.pdf}
 
@@
 
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
+\section{Conclusion}\label{conclusion}
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\hypertarget{refs}{}
+\section{References}\label{references}
+
+\phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-ademiluyi2022}{}}%
+\bibitem[\citeproctext]{ref-ademiluyi2022}
 Ademiluyi, A., Li, C., \& Park, A. (2022). Implications and Preventions
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-alabri2022}{}}%
+\bibitem[\citeproctext]{ref-alabri2022}
 Alabri, A. (2022). Fear of Missing Out (FOMO): The Effects of the Need
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-alhassan2018}{}}%
+\bibitem[\citeproctext]{ref-alhassan2018}
 Alhassan, A. A., Alqadhib, E. M., Taha, N. W., Alahmari, R. A., Salam,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-aljomaa2016}{}}%
+\bibitem[\citeproctext]{ref-aljomaa2016}
 Aljomaa, S. S., Al.Qudah, M. F., Albursan, I. S., Bakhiet, S. F., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-al-kandari2021}{}}%
+\bibitem[\citeproctext]{ref-al-kandari2021}
 Al-Kandari, Y. Y., \& Al-Sejari, M. M. (2021). Social isolation, social
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-appel2020}{}}%
+\bibitem[\citeproctext]{ref-appel2020}
 Appel, M., Marker, C., \& Gnambs, T. (2020). Are Social Media Ruining
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-beyens2020}{}}%
+\bibitem[\citeproctext]{ref-beyens2020}
 Beyens, I., Pouwels, J. L., Driel, I. I. van, Keijsers, L., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-buxfcttner2022}{}}%
+\bibitem[\citeproctext]{ref-buxfcttner2022}
 Büttner, C. M., \& Rudert, S. C. (2022). Why didn't you tag me?!: Social
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-chen2017}{}}%
+\bibitem[\citeproctext]{ref-chen2017}
 Chen, C., Zhang, K. Z. K., Gong, X., Zhao, S. J., Lee, M. K. O., \&
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-duradoni2020}{}}%
+\bibitem[\citeproctext]{ref-duradoni2020}
 Duradoni, M., Innocenti, F., \& Guazzini, A. (2020). Well-Being and
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ellison2007}{}}%
+\bibitem[\citeproctext]{ref-ellison2007}
 Ellison, N. B., Steinfield, C., \& Lampe, C. (2007). The Benefits of
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-henning-smith2018}{}}%
+\bibitem[\citeproctext]{ref-henning-smith2018}
 Henning-Smith, C., Ecklund, A., \& Kozhimannil, K. (2018). RURAL-URBAN
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ivie2020}{}}%
+\bibitem[\citeproctext]{ref-ivie2020}
 Ivie, E. J., Pettitt, A., Moses, L. J., \& Allen, N. B. (2020). A
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-jimuxe9nez2022}{}}%
+\bibitem[\citeproctext]{ref-jimuxe9nez2022}
 Jiménez, A. C., Vaillancourt, M., Zhu, P., \& Seon, Q. (2022). Social
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-kaye2017}{}}%
+\bibitem[\citeproctext]{ref-kaye2017}
 Kaye, L. W. (2017). Older adults, rural living, and the escalating risk
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-kim2017}{}}%
+\bibitem[\citeproctext]{ref-kim2017}
 Kim, H. H. (2017). The impact of online social networking on adolescent
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-koning2017}{}}%
+\bibitem[\citeproctext]{ref-koning2017}
 Koning, J. L. D., Stathi, A., \& Richards, S. (2017). Predictors of
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-larson2018}{}}%
+\bibitem[\citeproctext]{ref-larson2018}
 Larson, L. R., Szczytko, R., Bowers, E. P., Stephens, L. E., Stevenson,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-nowland2018}{}}%
+\bibitem[\citeproctext]{ref-nowland2018}
 Nowland, R., Necka, E. A., \& Cacioppo, J. T. (2018). Loneliness and
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ostic2021}{}}%
+\bibitem[\citeproctext]{ref-ostic2021}
 Ostic, D., Qalati, S. A., Barbosa, B., Shah, S. M. M., Galvan Vela, E.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-primack2017}{}}%
+\bibitem[\citeproctext]{ref-primack2017}
 Primack, B. A., Shensa, A., Sidani, J. E., Whaite, E. O., Lin, L. yi,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-steinfield2008}{}}%
+\bibitem[\citeproctext]{ref-steinfield2008}
 Steinfield, C., Ellison, N. B., \& Lampe, C. (2008). Social capital,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-subrahmanyam2008}{}}%
+\bibitem[\citeproctext]{ref-subrahmanyam2008}
 Subrahmanyam, K., Reich, S. M., Waechter, N., \& Espinoza, G. (2008).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-tam2019}{}}%
+\bibitem[\citeproctext]{ref-tam2019}
 Tam, L. (2019). The China fame factory training online influencers to
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-twenge2019}{}}%
+\bibitem[\citeproctext]{ref-twenge2019}
 Twenge, J. M. (2019). More Time on Technology, Less Happiness?
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-valkenburg2022}{}}%
+\bibitem[\citeproctext]{ref-valkenburg2022}
 Valkenburg, P. M., Meier, A., \& Beyens, I. (2022). Social media use and
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-wang2020}{}}%
+\bibitem[\citeproctext]{ref-wang2020}
 Wang, J. (2020). \emph{Regulation of digital media platforms: The case
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-wei2023}{}}%
+\bibitem[\citeproctext]{ref-wei2023}
 Wei, A. C. (2023). {`}Wang hong{'} culture booms in China as more young
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-xia1995}{}}%
+\bibitem[\citeproctext]{ref-xia1995}
 Xia, M. (1995). Changes in the {Pattern} of {Migration} in {Urban}
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-xu2014}{}}%
+\bibitem[\citeproctext]{ref-xu2014}
 Xu, A., \& Xia, Y. (2014). The changes in mainland chinese families
@@
 
-\hypertarget{online-appendix}{%
-\section{Online Appendix}\label{online-appendix}}
-
-\hypertarget{variable-operationalization}{%
+\section{Online Appendix}\label{online-appendix}
+
 \subsection{Variable
-Operationalization}\label{variable-operationalization}}
+Operationalization}\label{variable-operationalization}
 
@@
 
-\hypertarget{residual-analysis}{%
-\subsection{Residual Analysis}\label{residual-analysis}}
+\subsection{Residual Analysis}\label{residual-analysis}
 
@@
 
-{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-resids-human-1.pdf}
+\centering{
+
+\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-resids-human-1.pdf}
 
@@
 
-{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-resids-online-offline-1.pdf}
+\centering{
+
+\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-resids-online-offline-1.pdf}
 

### 2024-06-10 tandf/Social-Isolation-in-China-jg-revised.tex
updated files from jg

--- 2024-06-10 tandf/Social Isolation in China jg revised.tex
@@
 
+\begin{document}
 \title{Lonely and online: an investigation of social media use and
 social isolation in China}
-\author{}
-\date{2024-06-10}
-
-\begin{document}
+
+\author{\name{\textsuperscript{a} and }
+\affil{\textsuperscript{a}
+\textsuperscript{b}}}
+
 \maketitle
+
 \begin{abstract}
@@
 
+\begin{keywords}
+    Social Isolation, Social Media, Digital Communication, 
+    China
+\end{keywords}
 \newpage{}
@@
 
-\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-social-iso-dist-1.pdf}
+\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-social-iso-dist-1.pdf}
 
@@
 
-\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-var-dist-1.pdf}
+\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-var-dist-1.pdf}
 
@@
 
-\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-sm-use-dist-1.pdf}
+\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-sm-use-dist-1.pdf}
 
@@
 
-\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-urban-dist-1.pdf}
+\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-urban-dist-1.pdf}
 
@@
 
-\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-social-isolation-interactions-1.pdf}
+\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-social-isolation-interactions-1.pdf}
 
@@
 
-\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-resids-human-1.pdf}
+\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-resids-human-1.pdf}
 
@@
 
-\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-resids-online-offline-1.pdf}
+\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-resids-online-offline-1.pdf}
 

### 2024-06-10 tandf/Social-Isolation-in-China-jg-revised.tex
Compiled mac version

--- 2024-03-19 tandf/Social-Isolation-in-China.tex
@@
     China
-\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, breakable, sharp corners, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi
+\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, frame hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, sharp corners, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi
 
@@
 contextual differences of the Chinese internet compared to the Western
-intern do not appear to significantly alter the relationship.
+internet do not appear to significantly alter the relationship.
 
@@
 
-{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-social-iso-dist-1.pdf}
+{\centering \includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-social-iso-dist-1.pdf}
 
@@
 
-{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-var-dist-1.pdf}
+{\centering \includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-var-dist-1.pdf}
 
@@
 
-{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-sm-use-dist-1.pdf}
+{\centering \includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-sm-use-dist-1.pdf}
 
@@
 
-{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-urban-dist-1.pdf}
+{\centering \includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-urban-dist-1.pdf}
 
@@
 
-{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-social-isolation-interactions-1.pdf}
+{\centering \includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-social-isolation-interactions-1.pdf}
 
@@
 
-{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-resids-human-1.pdf}
+{\centering \includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-resids-human-1.pdf}
 
@@
 
-{\centering \includegraphics{Social-Isolation-in-China_files/figure-pdf/fig-resids-online-offline-1.pdf}
+{\centering \includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-resids-online-offline-1.pdf}
 

### 2024-06-10 tandf/Social Isolation in China jg revised.qmd
Final submission files ready

@@
 shift-heading-level-by: -1
+author:
+  - name: Jason Gainous
+    affiliations:
+      - name: University of Sharjah
+        department: Department of Mass Communication
+        city: Sharjah
+        country: United Arab Emirates
+    orcid: 0000-0002-3104-2313
+    email: jgainous@sharjah.ac.ae
+  - name: Andrew W. MacDonald
+    affiliations:
+      - name: Duke Kunshan University
+        department: Division of Social Sciences
+        city: Kunshan
+        country: China
+    orcid: 0000-0002-4695-1560
+    email: andrew.macdonald@dukekunshan.edu.cn
+    attributes:
+      corresponding: true
 ---

### 2024-06-10 tandf/Social-Isolation-in-China-jg-revised.tex
Final submission files ready

@@
   pdftitle={Lonely and online: an investigation of social media use and social isolation in China},
+  pdfauthor={Jason Gainous; Andrew W. MacDonald},
   pdfkeywords={Social Isolation, Social Media, Digital
@@
 
-\author{\name{\textsuperscript{a} and }
-\affil{\textsuperscript{a}
-\textsuperscript{b}}}
+\author{\name{Jason Gainous\textsuperscript{a} and Andrew W.
+MacDonald\textsuperscript{b}\thanks{CONTACT Andrew W.
+MacDonald. Email: andrew.macdonald@dukekunshan.edu.cn}}
+\affil{\textsuperscript{a}Department of Mass Communication, University
+of Sharjah, Sharjah, United Arab Emirates;
+\textsuperscript{b}Division of Social Sciences, Duke Kunshan
+University, Kunshan, China}}
 
@@
     China
-\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, frame hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, sharp corners, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi
+\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, boxrule=0pt, interior hidden, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, enhanced]}{\end{tcolorbox}}\fi
 

### 2024-08-19 tandf/Response to reviewers second revision.qmd
Review 2 update

---
title: "Response to reviewers - second revision"
format: pdf
---

## Reviewer 2

*1. Timeliness of Data: The research is based on data collected in 2015, a time when the prevalence of mobile internet and social media platforms might differ significantly from the present landscape. The authors utilized a survey conducted from November 25 to December 2, 2015, as mentioned in the document: "We employed Qualtrics to collect the data...from November 25 to December 2, 2015." Given the rapid evolution of digital communication, the applicability of findings based on a decade-old dataset should be reconsidered.*

*2. Mismatch Between Literature Review and Data Collection: The literature review incorporates studies from around 2020, such as the reference to "Valkenburg et al., 2022," yet the data used for analysis is from 2015. This discrepancy may affect the validity of conclusions drawn from contemporary theoretical perspectives when applied to outdated data.*

We are happy to revise our literature review section in ways that the reviewer feels would strengthen the paper but we are a bit unsure of how to proceed given two previous comments by reviewers that we add to the literature review section. While we acknowledge that the previous recommendation and this recommendation are not precisely mutually exclusive, it does suggest that if we remove some references here we may be working against the recommendations of the previous reviewers.

Suggestions as to how to move forward would be welcome here.

> Previous reviewer 1 comment: "It is suggested to examine the related theories to answer, why the phenomenon of social media use in Mainland China may be different from others."

> Previous reviewer 2 comment: "Nothing in the literature review about social media addiction. I suggest to see: Social isolation, social support and their relationship with smartphone addiction; examples: The relationship between addiction to smartphone usage and depression among adults: A crosssectional study, Smartphone addiction among university students in the light of some variables, and Examining the effects of motives and gender differences on smartphone addiction."

*3. Rationale for Variable Selection: The inclusion of variables like "Chinese Communist Party membership (CCP)" is noted, as stated: "For those we begin by fitting an additive model of our index of social isolationism as function of each of our primary independent variables...CCP Member." However, the introduction does not discuss the relevance of this variable, leaving unclear its contribution to the study.*

A reasonable point. We have added some discussion of the reason this variable is included in the final paragraph of the Data, Measurement and Description section.

*4. Depth of Discussion: The discussion section lacks depth, particularly in expanding upon the implications of the results. For example, the document mentions: "our results cast some doubt on theories that suggest it is the negative content..." but does not elaborate on how these findings challenge existing theories.*

Fair point. We have substantially increased discussion of the implications and linked it more explicitly back to the literature discussed in the theory section.

### 2024-08-19 tandf/Social Isolation in China second revision.qmd
Review 2 update

--- 2024-06-10 tandf/Social Isolation in China jg revised.qmd
@@
 
--   **H$1_a$**: social media use should have a positive connection to social isolation due to strengthened government control over online content
+-   **H**$1_a$: social media use should have a positive connection to social isolation due to strengthened government control over online content
 
--   **H$1_b$**: social media use should have a negative connection to social isolation due to the dominance of influencer culture in China, moderated by age.
+-   **H**$1_b$: social media use should have a negative connection to social isolation due to the dominance of influencer culture in China, moderated by age.
 
--   **H$2$**: those who are able to use social media to make new friends will have lower social isolation scores than those who do not
+-   **H**$2$: those who are able to use social media to make new friends will have lower social isolation scores than those who do not
 
--   **H$3$:** the urban/rural divide will produce differential impacts in the above hypotheses on the relationship between social media use and social isolation
+-   **H**$3$: the urban/rural divide will produce differential impacts in the above hypotheses on the relationship between social media use and social isolation
 
@@
 Each was recoded so that higher values represented more social media use, rescaled to range from 0 through 1, added together, and then again, rescaled to range from 0 through 1 maintaining all original intervals.The Chronbach's alpha was relatively low for these three items ($\alpha = 0.31$), but we proceeded with the construction of this index because, first, the face validity is high.
-Simply, those who claim to use social media generally more often, claim to read political news more often, and claim to use it more than they did in the past, are certainly likely to be more frequent social media users than those who do not do all these things.Second, we confirmed that these three items were all positively correlated with each other (p < 0.0001 for all pairwise relationships).
+Simply, those who claim to use social media generally more often, claim to read political news more often, and claim to use it more than they did in the past, are certainly likely to be more frequent social media users than those who do not do all these things.Second, we confirmed that these three items were all positively correlated with each other (p \< 0.0001 for all pairwise relationships).
 The distribution of this index is presented in @fig-sm-use-dist.
@@
 
+Finally, while not a key variable of interest, we also include a dummy variable for Chinese Communist Party (CCP) membership.
+Previous research on party members suggest that party members may volunteer for social causes at a higher rate than non party members [@dickson2014].
+This volunteering behavior may contribute to a lower level of feelings of social isolation and therefore it is of interest to estimate any possible effects of party member status.
+Additionally, a long line of research has noted that party members earn more than non-party members [@dickson2000; @yan2019].
+If party membership affects social isolation and also affects earnings, controlling for CCP membership is important to prevent a biased estimate of the relationship between earnings and social isolation.
+
 Our modeling strategy that follows is straightforward.
-We begin by modeling each of our internet communication independent variables as function of socio-economic status (SES), gender, Chinese Communist Party membership (CCP), and age to create an individual profile of each type of digital user (see the Online Appendix for the operationalization of these variables).
+We begin by modeling each of our internet communication independent variables as function of socio-economic status (SES), gender, CCP membership status, and age to create an individual profile of each type of digital user (see the Online Appendix for the operationalization of these variables).
 This provides some context for the models that follow which are intended to test our primary hypotheses, that is that internet communication can deter social isolation and that this is particularly true for those who do not have the convenience of the high social interaction opportunity provided by urban living.
@@
 However, this does not seem to extend to those that use the internet to facilitate offline meetups.
-Finally, we find that the impact of the internet and social media vary significantly according to the level of urbanicity (**H3**) - this matches with previous findings that suggest that there is significant heterogeneity in the impact of social media on social isloation.
+Finally, we find that the impact of the internet and social media vary significantly according to the level of urbanicity (**H3**) - this matches with previous findings that suggest that there is significant heterogeneity in the impact of social media on social isolation.
 
@@
 This finding lends support to the FOMO channel - viewing lots of content from influencers in a rural area compounds feelings of isolation.
+The finding by @henning-smith2018 and others that rural respondents are more socially isolated seems, at least in China, to be exacerbated by social media.
 
 Additionally, given the robustly negative relationship between social media use and social isolation even in the context of China's highly policed internet, our results cast some doubt on theories that suggest it is the negative content, such as cyberbullying or violent/graphic posts, that drives the relationship.
-Finally, our results also further suggest more work needs to be done in identifying important hetergeneous effects - in our results, those living in a big city experienced almost no change in social isolation as social media use increased while the relationship becomes increasingly negative by ruralness.
+While @ademiluyi2022 finds that cyberbulling and has a negative short term relationship with social exclusion our finding that there is a negative relationship between social media use and social isolation even in places like China that actively attempt to limit this type of online behavior suggest that the relationship we observe has deeper causes.
+More generally, China's internet governance strategy of limiting negative online experience does not seem to have dampened the relationship between social media use and social isolation, indicating to us that other proposed mechanisms are likely driving the observed relationship.
+
+Finally, our results also further suggest more work needs to be done in identifying important heterogeneous effects - in our results, those living in a big city experienced almost no change in social isolation as social media use increased while the relationship becomes increasingly negative by ruralness.
 This specific heterogeneous effect may be unique to China but the strength of it suggests that important inter-personal factors may be relevant in other contexts.
+Importantly, given our survey results are from 2015, our finding of important heterogeneous effects suggest that these effects did not begin around the time of recent scholarly interest in the topic [@beyens2020; @ostic2021] but rather have been an important feature of the relationship between social media and social isolation since the beginning of social media use.
 

### 2024-08-19 tandf/Social-Isolation-in-China-second-revision.tex
Review 2 update

--- 2024-06-10 tandf/Social Isolation in China jg revised.tex
@@
 
+\begin{document}
 \title{Lonely and online: an investigation of social media use and
 social isolation in China}
-\author{}
-\date{2024-06-10}
-
-\begin{document}
+
+\author{\name{Jason Gainous\textsuperscript{a} and Andrew W.
+MacDonald\textsuperscript{b}\thanks{CONTACT Andrew W.
+MacDonald. Email: andrew.macdonald@dukekunshan.edu.cn}}
+\affil{\textsuperscript{a}Department of Mass Communication, University
+of Sharjah, Sharjah, United Arab Emirates;
+\textsuperscript{b}Division of Social Sciences, Duke Kunshan
+University, Kunshan, China}}
+
 \maketitle
+
 \begin{abstract}
@@
 \item
-  \textbf{H\(1_a\)}: social media use should have a positive connection
+  \textbf{H}\(1_a\): social media use should have a positive connection
   to social isolation due to strengthened government control over online
@@
 \item
-  \textbf{H\(1_b\)}: social media use should have a negative connection
+  \textbf{H}\(1_b\): social media use should have a negative connection
   to social isolation due to the dominance of influencer culture in
@@
 \item
-  \textbf{H\(2\)}: those who are able to use social media to make new
+  \textbf{H}\(2\): those who are able to use social media to make new
   friends will have lower social isolation scores than those who do not
 \item
-  \textbf{H\(3\):} the urban/rural divide will produce differential
+  \textbf{H}\(3\): the urban/rural divide will produce differential
   impacts in the above hypotheses on the relationship between social
@@
 
-\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-social-iso-dist-1.pdf}
+\includegraphics{Social-Isolation-in-China-second-revision_files/figure-pdf/fig-social-iso-dist-1.pdf}
 
@@
 
-\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-var-dist-1.pdf}
+\includegraphics{Social-Isolation-in-China-second-revision_files/figure-pdf/fig-var-dist-1.pdf}
 
@@
 
-\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-sm-use-dist-1.pdf}
+\includegraphics{Social-Isolation-in-China-second-revision_files/figure-pdf/fig-sm-use-dist-1.pdf}
 
@@
 
-\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-urban-dist-1.pdf}
+\includegraphics{Social-Isolation-in-China-second-revision_files/figure-pdf/fig-urban-dist-1.pdf}
 
@@
 \end{figure}%
+
+Finally, while not a key variable of interest, we also include a dummy
+variable for Chinese Communist Party (CCP) membership. Previous research
+on party members suggest that party members may volunteer for social
+causes at a higher rate than non party members (Dickson, 2014). This
+volunteering behavior may contribute to a lower level of feelings of
+social isolation and therefore it is of interest to estimate any
+possible effects of party member status. Additionally, a long line of
+research has noted that party members earn more than non-party members
+(Dickson \& Rublee, 2000; Yan, 2019). If party membership affects social
+isolation and also affects earnings, controlling for CCP membership is
+important to prevent a biased estimate of the relationship between
+earnings and social isolation.
 
@@
 modeling each of our internet communication independent variables as
-function of socio-economic status (SES), gender, Chinese Communist Party
-membership (CCP), and age to create an individual profile of each type
-of digital user (see the Online Appendix for the operationalization of
-these variables). This provides some context for the models that follow
-which are intended to test our primary hypotheses, that is that internet
-communication can deter social isolation and that this is particularly
-true for those who do not have the convenience of the high social
-interaction opportunity provided by urban living. For those we begin by
-fitting an additive model of our index of social isolationism as
-function of each of our primary independent variables while also
-controlling for the same variables included in our profile models.
-Finally, we refit three models with the same specification but introduce
-an interactive term between each of our internet communication
-indicators, respectively, with our measure of urbanicity. This allows us
-to test whether the observed additive effects are stronger for those
-living outside cities.
+function of socio-economic status (SES), gender, CCP membership status,
+and age to create an individual profile of each type of digital user
+(see the Online Appendix for the operationalization of these variables).
+This provides some context for the models that follow which are intended
+to test our primary hypotheses, that is that internet communication can
+deter social isolation and that this is particularly true for those who
+do not have the convenience of the high social interaction opportunity
+provided by urban living. For those we begin by fitting an additive
+model of our index of social isolationism as function of each of our
+primary independent variables while also controlling for the same
+variables included in our profile models. Finally, we refit three models
+with the same specification but introduce an interactive term between
+each of our internet communication indicators, respectively, with our
+measure of urbanicity. This allows us to test whether the observed
+additive effects are stronger for those living outside cities.
 
@@
 
-\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-social-isolation-interactions-1.pdf}
+\includegraphics{Social-Isolation-in-China-second-revision_files/figure-pdf/fig-social-isolation-interactions-1.pdf}
 
@@
 previous findings that suggest that there is significant heterogeneity
-in the impact of social media on social isloation.
+in the impact of social media on social isolation.
 
@@
 channel - viewing lots of content from influencers in a rural area
-compounds feelings of isolation.
+compounds feelings of isolation. The finding by Henning-Smith et al.
+(2018) and others that rural respondents are more socially isolated
+seems, at least in China, to be exacerbated by social media.
 
@@
 it is the negative content, such as cyberbullying or violent/graphic
-posts, that drives the relationship. Finally, our results also further
-suggest more work needs to be done in identifying important hetergeneous
-effects - in our results, those living in a big city experienced almost
-no change in social isolation as social media use increased while the
-relationship becomes increasingly negative by ruralness. This specific
-heterogeneous effect may be unique to China but the strength of it
-suggests that important inter-personal factors may be relevant in other
-contexts.
+posts, that drives the relationship. While Ademiluyi et al. (2022) finds
+that cyberbulling and has a negative short term relationship with social
+exclusion our finding that there is a negative relationship between
+social media use and social isolation even in places like China that
+actively attempt to limit this type of online behavior suggest that the
+relationship we observe has deeper causes. More generally, China's
+internet governance strategy of limiting negative online experience does
+not seem to have dampened the relationship between social media use and
+social isolation, indicating to us that other proposed mechanisms are
+likely driving the observed relationship.
+
+Finally, our results also further suggest more work needs to be done in
+identifying important heterogeneous effects - in our results, those
+living in a big city experienced almost no change in social isolation as
+social media use increased while the relationship becomes increasingly
+negative by ruralness. This specific heterogeneous effect may be unique
+to China but the strength of it suggests that important inter-personal
+factors may be relevant in other contexts. Importantly, given our survey
+results are from 2015, our finding of important heterogeneous effects
+suggest that these effects did not begin around the time of recent
+scholarly interest in the topic (Beyens et al., 2020; Ostic et al.,
+2021) but rather have been an important feature of the relationship
+between social media and social isolation since the beginning of social
+media use.
 
@@
 
+\bibitem[\citeproctext]{ref-dickson2014}
+Dickson, B. J. (2014). Who Wants to Be a Communist? Career Incentives
+and Mobilized Loyalty in China. \emph{The China Quarterly}, \emph{217},
+42--68. \url{https://doi.org/10.1017/S0305741013001434}
+
+\bibitem[\citeproctext]{ref-dickson2000}
+Dickson, B. J., \& Rublee, M. R. (2000). Membership Has Its Privileges.
+\emph{Comparative Political Studies}, \emph{33}(1), 87--112.
+\url{https://doi.org/10.1177/0010414000033001004}
+
 \bibitem[\citeproctext]{ref-duradoni2020}
@@
 
+\bibitem[\citeproctext]{ref-yan2019}
+Yan, S. (2019). The changing faces and roles of communist party
+membership in china: An empirical analysis based on CHIPS 1988, 1995 and
+2002. \emph{Journal of Contemporary East Asia Studies}, \emph{8}(1),
+99--120. \url{https://doi.org/10.1080/24761028.2019.1633987}
+
 \end{CSLReferences}
@@
 
-\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-resids-human-1.pdf}
+\includegraphics{Social-Isolation-in-China-second-revision_files/figure-pdf/fig-resids-human-1.pdf}
 
@@
 
-\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-resids-online-offline-1.pdf}
+\includegraphics{Social-Isolation-in-China-second-revision_files/figure-pdf/fig-resids-online-offline-1.pdf}
 

### 2024-08-27 tandf/Response to reviewers second revision jg edits.qmd
Second response to reviewers

--- 2024-08-19 tandf/Response to reviewers second revision.qmd
@@
 
+We agree that the digital environment changes rapidly, that our data are getting dated, and that we needed to make a case for why we are confident that our theory and results are still relevant today.
+We make the case that our estimates are actually conservative ones because the new developments in the digital environment should increase the strength of the relationship between social media use and social isolationism.
+As such, we added to the manuscript a three-pronged defense of the age of the data: 1) Based on our theoretical framework, the development of new social media technologies should only exacerbate the differences between urban and rural variation in the relationship between social media use and feelings of isolation.
+The new technologies make it even more apparent to rural citizens that they may be missing out - the rise of short video content, improved algorithms that better target users with content and tighten their social networks, better content creation tools, etc.
+The modern digital environment relative to the one at the time our data were collected should heighten the fear of missing out making our estimates conservative ones.
+2) Our questions of digital media consumption are general enough to not be context and time dependent.
+They are not aimed at specific technologies that are no longer in use.
+3) The urbanization of China has increased since the data were collected.
+This makes citizens living in rural areas increasingly separated from many of their family and friends forced to move to cities for jobs.
+As such, here too, we expect the divide is only exacerbating the problem.
+While it is true that more people are moving to cities so they will not have the fear of missing out, those people who are left are less likely to have family and friends nearby.
+
+See footnote 3 for our discussion of this issue.
+
 *2.
@@
 
-> Previous reviewer 1 comment: "It is suggested to examine the related theories to answer, why the phenomenon of social media use in Mainland China may be different from others."
+> Previous reviewer 1 comment: It is suggested to examine the related theories to answer, why the phenomenon of social media use in Mainland China may be different from others.
 
-> Previous reviewer 2 comment: "Nothing in the literature review about social media addiction.
-I suggest to see: Social isolation, social support and their relationship with smartphone addiction; examples: The relationship between addiction to smartphone usage and depression among adults: A crosssectional study, Smartphone addiction among university students in the light of some variables, and Examining the effects of motives and gender differences on smartphone addiction."
+> Previous reviewer 2 comment: Nothing in the literature review about social media addiction.
+I suggest to see: "Social isolation, social support and their relationship with smartphone addiction", "The relationship between addiction to smartphone usage and depression among adults: A crosssectional study", "Smartphone addiction among university students in the light of some variables," and "Examining the effects of motives and gender differences on smartphone addiction."
 

### 2024-08-27 tandf/Social Isolation in China second revision jg edits.qmd
Second response to reviewers

--- 2024-08-19 tandf/Social Isolation in China second revision.qmd
@@
 shift-heading-level-by: -1
-author:
-  - name: Jason Gainous
-    affiliations:
-      - name: University of Sharjah
-        department: Department of Mass Communication
-        city: Sharjah
-        country: United Arab Emirates
-    orcid: 0000-0002-3104-2313
-    email: jgainous@sharjah.ac.ae
-  - name: Andrew W. MacDonald
-    affiliations:
-      - name: Duke Kunshan University
-        department: Division of Social Sciences
-        city: Kunshan
-        country: China
-    orcid: 0000-0002-4695-1560
-    email: andrew.macdonald@dukekunshan.edu.cn
-    attributes:
-      corresponding: true
 ---
@@
 We employed Qualtrics to collect the data.
-They randomly selected 2292 respondents from their existing panel[^2] from November 25 to December 2, 2015.
-This sample size on provides for a roughly $\pm2$ margin of error.[^3] While our sample is selected randomly from Qualtrics' online user panel, it isn't representative of China's entire population due to its internet-based recruitment methods.
+They randomly selected 2292 respondents from their existing panel[^2] from November 25 to December 2, 2015.[^3] This sample size on provides for a roughly $\pm2$ margin of error.[^4] While our sample is selected randomly from Qualtrics' online user panel, it isn't representative of China's entire population due to its internet-based recruitment methods.
 The sample, however, aligns well with Chinese internet users, crucial for our internet effects research.
-Compared to national data, our sample skews younger and more educated but is similar in income and gender.[^4] These demographics reflect the global digital divide and are in line with expectations for internet users in developing regions.
+Compared to national data, our sample skews younger and more educated but is similar in income and gender.[^5] These demographics reflect the global digital divide and are in line with expectations for internet users in developing regions.
 Our findings are particularly relevant for understanding digital media's impact among active internet users in China.
@@
 
-[^3]: We were able to first collect a small sample ($n=286$) to check the reliability and adjust the instrument after before proceeding with the final data collection.
+[^3]: While the data are from 2015, we contend that they still contribute to understanding of social isolation and social media use.
+Based on our theory oulined in this paper, the new developments in the digital environment should, in our view, increase the strength of the relationship found in this paper for three reasons: 1)  The new technologies make it even more apparent to rural citizens that they may be missing out - the rise of short video content, improved algorithms that better target users with content and tighten their social networks, better content creation tools, etc.
+The modern digital environment relative to the one at the time our data were collected should heighten the fear of missing out making our estimates conservative ones.
+2) Our questions of digital media consumption described below are general enough to not be context and time dependent.
+They are not aimed at specific technologies that are no longer in use.
+3) The urbanization of China has increased since the data were collected.
+This makes citizens living in rural areas increasingly separated from many of their family and friends forced to move to cities for jobs.
+As such, here too, we expect the divide is only exacerbating the problem.
+While it is true that more people are moving to cities so they will not have the fear of missing out, those people who are left are less likely to have family and friends nearby.
+
+[^4]: We were able to first collect a small sample ($n=286$) to check the reliability and adjust the instrument after before proceeding with the final data collection.
 We made three adjustments, none of which are related to the measures used in the current study.
 
-[^4]: See https://data.worldbank.org/country/china (go to the Country Profile), and https://www.cnnic.com.cn/AU/Introduction/Introduction/201208/t20120815_33295.htm.
+[^5]: See https://data.worldbank.org/country/china (go to the Country Profile), and https://www.cnnic.com.cn/AU/Introduction/Introduction/201208/t20120815_33295.htm.
 

### 2024-08-27 tandf/Social-Isolation-in-China-second-revision-jg-edits.tex
Second response to reviewers

--- 2024-08-19 tandf/Social-Isolation-in-China-second-revision.tex
@@
 
-\author{\name{Jason Gainous\textsuperscript{a} and Andrew W.
-MacDonald\textsuperscript{b}\thanks{CONTACT Andrew W.
-MacDonald. Email: andrew.macdonald@dukekunshan.edu.cn}}
-\affil{\textsuperscript{a}Department of Mass Communication, University
-of Sharjah, Sharjah, United Arab Emirates;
-\textsuperscript{b}Division of Social Sciences, Duke Kunshan
-University, Kunshan, China}}
+\author{\name{\textsuperscript{a} and }
+\affil{\textsuperscript{a}
+\textsuperscript{b}}}
 
@@
   received a relatively high number of points.} from November 25 to
-December 2, 2015. This sample size on provides for a roughly \(\pm2\)
-margin of error.\footnote{We were able to first collect a small sample
-  (\(n=286\)) to check the reliability and adjust the instrument after
-  before proceeding with the final data collection. We made three
-  adjustments, none of which are related to the measures used in the
-  current study.} While our sample is selected randomly from Qualtrics'
-online user panel, it isn't representative of China's entire population
-due to its internet-based recruitment methods. The sample, however,
-aligns well with Chinese internet users, crucial for our internet
-effects research. Compared to national data, our sample skews younger
-and more educated but is similar in income and gender.\footnote{See
+December 2, 2015.\footnote{While the data are from 2015, we contend that
+  they still contribute to understanding of social isolation and social
+  media use. Based on our theory oulined in this paper, the new
+  developments in the digital environment should, in our view, increase
+  the strength of the relationship found in this paper for three
+  reasons: 1) The new technologies make it even more apparent to rural
+  citizens that they may be missing out - the rise of short video
+  content, improved algorithms that better target users with content and
+  tighten their social networks, better content creation tools, etc. The
+  modern digital environment relative to the one at the time our data
+  were collected should heighten the fear of missing out making our
+  estimates conservative ones. 2) Our questions of digital media
+  consumption described below are general enough to not be context and
+  time dependent. They are not aimed at specific technologies that are
+  no longer in use. 3) The urbanization of China has increased since the
+  data were collected. This makes citizens living in rural areas
+  increasingly separated from many of their family and friends forced to
+  move to cities for jobs. As such, here too, we expect the divide is
+  only exacerbating the problem. While it is true that more people are
+  moving to cities so they will not have the fear of missing out, those
+  people who are left are less likely to have family and friends nearby.}
+This sample size on provides for a roughly \(\pm2\) margin of
+error.\footnote{We were able to first collect a small sample (\(n=286\))
+  to check the reliability and adjust the instrument after before
+  proceeding with the final data collection. We made three adjustments,
+  none of which are related to the measures used in the current study.}
+While our sample is selected randomly from Qualtrics' online user panel,
+it isn't representative of China's entire population due to its
+internet-based recruitment methods. The sample, however, aligns well
+with Chinese internet users, crucial for our internet effects research.
+Compared to national data, our sample skews younger and more educated
+but is similar in income and gender.\footnote{See
   https://data.worldbank.org/country/china (go to the Country Profile),
@@
 
-\includegraphics{Social-Isolation-in-China-second-revision_files/figure-pdf/fig-social-iso-dist-1.pdf}
+\includegraphics{Social-Isolation-in-China-second-revision-jg-edits_files/figure-pdf/fig-social-iso-dist-1.pdf}
 
@@
 
-\includegraphics{Social-Isolation-in-China-second-revision_files/figure-pdf/fig-var-dist-1.pdf}
+\includegraphics{Social-Isolation-in-China-second-revision-jg-edits_files/figure-pdf/fig-var-dist-1.pdf}
 
@@
 
-\includegraphics{Social-Isolation-in-China-second-revision_files/figure-pdf/fig-sm-use-dist-1.pdf}
+\includegraphics{Social-Isolation-in-China-second-revision-jg-edits_files/figure-pdf/fig-sm-use-dist-1.pdf}
 
@@
 
-\includegraphics{Social-Isolation-in-China-second-revision_files/figure-pdf/fig-urban-dist-1.pdf}
+\includegraphics{Social-Isolation-in-China-second-revision-jg-edits_files/figure-pdf/fig-urban-dist-1.pdf}
 
@@
 
-\includegraphics{Social-Isolation-in-China-second-revision_files/figure-pdf/fig-social-isolation-interactions-1.pdf}
+\includegraphics{Social-Isolation-in-China-second-revision-jg-edits_files/figure-pdf/fig-social-isolation-interactions-1.pdf}
 
@@
 
-\includegraphics{Social-Isolation-in-China-second-revision_files/figure-pdf/fig-resids-human-1.pdf}
+\includegraphics{Social-Isolation-in-China-second-revision-jg-edits_files/figure-pdf/fig-resids-human-1.pdf}
 
@@
 
-\includegraphics{Social-Isolation-in-China-second-revision_files/figure-pdf/fig-resids-online-offline-1.pdf}
+\includegraphics{Social-Isolation-in-China-second-revision-jg-edits_files/figure-pdf/fig-resids-online-offline-1.pdf}
 

### 2025-01-21 firstmonday/Social Isolation in China fm.qmd
First monday submission

--- 2024-08-19 tandf/Social Isolation in China second revision.qmd
@@
 keywords: [Social Isolation, Social Media, Digital Communication, China]
-format:
-  tandf-pdf:
-    keep-tex: true 
+format: docx
 execute: 
@@
   warning: false
-keep-tex: true
 bibliography: references.bib
-csl: taylor-and-francis-apa.csl
+csl: first-monday.csl
 shift-heading-level-by: -1
@@
 library(ggResidpanel)
+library(flextable)
 
@@
              stars=c("*" = 0.05),
-             output="kableExtra",
-             gof_map = gof.included) %>% 
-  footnote(general = n, threeparttable = TRUE)
+             output="flextable",
+             gof_map = gof.included)
 
@@
              stars=c("*" = 0.05),
-             output="kableExtra",
-             gof_map = gof.included) %>% 
-  footnote(general = n, threeparttable = TRUE)
+             output="flextable",
+             gof_map = gof.included)
 ```
@@
 {{< pagebreak >}}
+
+## About the Authors
+
+Jason Gainous is a Professor at the University of Sharjah.
+He has published three books, two with Oxford University Press (Directed Digital Dissidence in Autocracies: How China Wins Online and Tweeting to Power: The Social Media Revolution in American Politics, ) and one with Rowman and Littlefield (Rebooting American Politics: The Internet Revolution).
+He has also published various articles in journals including American Politics Research, Democratization, Information, Communication and Society, International Journal of Press/Politics, International Journal of Communication, Journal of Information Technology & Politics, Political Behavior, Political Research Quarterly, Political Communication, Social Science Quarterly, and Statistical Science among others.
+
+His research has won awards from the American Political Science Association, the Kentucky Political Science Association, the Southwestern Social Science Association, and the Florida Political Science Association.
+The University of Louisville has also honored him with their most prestigious award for research as well as their most prestigious award for teaching.
+
+Dr. Gainous is also the Co-Editor in Chief of the Journal of Information Technology & Politics.
+
+Andrew W.
+MacDonald is an Assistant Professor of Social Science at Duke Kunshan University.
+He primarily works in the area of Chinese public opinion research, having authored nearly a dozen surveys of Chinese attitudes on politics, technology, and social questions.
+His work on this topic has been published in a wide variety of communication, technology, and experimental design journals.
+
+His latest projects examine how Chinese feel about state versus corporate control of online personal information and how Chinese people read and interpret state propaganda messages.
+Taken as a whole, his work seeks to complexify simple narratives about Chinese public opinion; that either the public passively accepts state narratives or becomes an all-out regime opponent.
+In fact, public opinion is surprisingly nuanced given that China is an authoritarian context.
+
+His other interests lie in data visualization and making data science more approachable using new technological tools.
+He has developed several innovative, web-based approaches for learning statistical concepts and regularly teaches his universities Stats 101 class.
+
+## Acknowledgements
+
+The authors would like to thank the University of Louisville's Center for Asian Democracy for supporting this project.
+Additionally, the authors would like to thank those who offered feedback at the Responsible Citizens conference in Paris.
 

### 2025-03-17 firstmonday/Social Isolation in China fm.qmd
Reviewer responses

@@
 We believe the setting of China gives additional leverage to investigate issues of heterogeneity and the importance of context for several reasons.
-Firstly, the highly controlled nature of China's internet space prevents user exposure to some of the more threatening online content (such as cyberbullying) that is hypothesized to be a factor in creating a negative relationship between social media and feelings of social isolation [@wang2020].
-If this mechanism were the dominant reason for previous findings of a negative relationship between the two, one would expect the relationship to be more positive in China.
-Relatedly, China has a more commercial and robust influencer culture that often dominates user's social media consumption [@tam2019; @wei2023].
+Firstly, China's internet is highly controlled, not only by blocking foreign websites, but also by much more hands-on regulation of what the Chinese government deems unhealthy content [@wang2020].
+While cyberbullying and antisocial behavior is a regular phenomenon on the Chines Internet, the government has been more proactive in trying to regulate it than in the West [@huang2021; @surveyd2023].
+One expectation is therefore that Chinese social media space generates fewer feelings of social isolation - though, if the government's efforts have been not been successful, it is plausible that there is no difference compared to studies in the West.
+On the other hand, an effect that generates a prediction in the opposite direction is that China has a more commercial and robust influencer culture that often dominates user's social media consumption [@tam2019; @wei2023].
 If the main pathway creating a negative relationship is via user's comparisons of their lives with others (FOMO), we expect the relationship between social media use and feelings of social isolation to be greater in China.
@@
 
-Finally, our results also further suggest more work needs to be done in identifying important heterogeneous effects - in our results, those living in a big city experienced almost no change in social isolation as social media use increased while the relationship becomes increasingly negative by ruralness.
+One finding that matches the cyberoptimist theory of social media is that users who use social media to make new connections do report less social isolation.
+As @clark2018 found, the motivation for social media use matters.
+In their study, users who go onto social media sites for activities such as "social snacking" or quick but shallow satisfaction of social needs report higher degrees of social isolation.
+This is opposed to users who explicitly use social media to build communities of like-minded individuals.
+While our dataset does not provide information on intentionality, our findings here are in line with this kind of differential effect.
+
+The interaction effects in our model also further suggests more work needs to be done in identifying important heterogeneous effects - in our results, those living in a big city experienced almost no change in social isolation as social media use increased while the relationship becomes increasingly negative by ruralness.
 This specific heterogeneous effect may be unique to China but the strength of it suggests that important inter-personal factors may be relevant in other contexts.
